---
title: "cgb2010-replication"
author: "mht"
date: "December 2, 2014"
output: html_document
---


Merge data sets for 2 experiments into a single .csv

```{r datamerge, echo=FALSE}
setwd('/Users/mht/Documents/research/generics/cbg2010-replication/data/')
d1<-read.table('cbgR-exp1_anonymized-trials.tsv',header=T)
#d2<-read.table('cbgR-exp2_anonymized-trials.tsv',header=T)
d3<-read.table('cbgR-exp3_anonymized-trials.tsv',header=T)

#d2$workerid<-d2$workerid+length(levels(factor(d1$workerid)))
#d3$workerid<-d3$workerid+length(levels(factor(d2$workerid)))+length(levels(factor(d1$workerid)))
d3$workerid<-d3$workerid+length(levels(factor(d1$workerid)))

all.experiments<-rbind(d1,d3)

#write.csv(all.experiments, file='cbgR-exp1_exp3_anonymized-trials.csv')
#write.csv(td1, file='cbgR-exp3_anonymized-trials.csv')

```

# Experiment 1: CBG (2010) Experiments 1 and 2

### Experimental conditions


+ **truth conditions** = given a prevalence level (XX% of warfles have purple feathers) and a sentence (*generic*, *most*, *some*), answer if the sentence is True or False
+ **implied prevalence** = given a sentence (*generic*, *most*, *some*), answer with the percentage of *warfles that have purple feathers*


```{r exp1}
library(ggplot2)
library(plyr)
library(reshape2)
library(ggthemes)
library(gridExtra)
library(bootstrap)
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}


setwd('/Users/mht/Documents/research/generics/cbg2010-replication/data/')
turk.data<-read.table('cbgR-exp1_anonymized-trials.tsv',header=T)

turk.data$implied_prevalence <- as.numeric(levels(turk.data$response)[turk.data$response])
turk.data$truth_conditions <- factor(as.logical(levels(turk.data$response)[turk.data$response]), levels=c("TRUE","FALSE"))
turk.data$stim_prevalence <- factor(turk.data$stim_prevalence)
```


Number of responses for each prevalence level (for truth conditions task)
```{r resp1Atab, echo=FALSE}
table(turk.data[,c("stim_determiner","stim_prevalence")])
```

Number of responses for implied prevalence task.
```{r resp2Btab, echo=FALSE}
table(subset(turk.data,trial_type=='implied_prevalence')[,c("stim_determiner")])
```


Plot *implied prevalence* (top) and proportion of "true" responses at each stated prevalence level (bottom, replicated figure 3 from CGB 2010)

```{r}
df<-ddply(subset(turk.data,trial_type=='truth_conditions'), 
      .(stim_determiner, stim_prevalence), summarise, 
      true_responses= table(truth_conditions)[["TRUE"]]/length(truth_conditions))

a<-ggplot(subset(turk.data,trial_type=='implied_prevalence'),aes(x=implied_prevalence,fill=stim_determiner))+
  geom_density(alpha=.5)+
  facet_wrap(~stim_determiner)+
  theme_bw()+
  guides(fill=F)

b<-ggplot(df, aes(x=stim_prevalence,y=true_responses,colour=stim_determiner, group=stim_determiner))+
  geom_line(size=1)+
  facet_wrap(~stim_determiner)+
  theme_bw()+
  ylab("proportion of 'true' responses")+
  guides(colour=F)

grid.arrange(a,b)
```

Replicate figure 2 of CGB 2010 *asymmetry of truth_conditions and implied_prevalence*
```{r}

bootstrap.ci <- function(x){
  agr = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=mean)
  agr$CILow = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=ci.low)$subj_prevalence
  agr$CIHigh = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=ci.high)$subj_prevalence
  agr$YMin = agr$subj_prevalence - agr$CILow
  agr$YMax = agr$subj_prevalence + agr$CIHigh
  return(agr)
}

turk.data$stim_prevalence <- as.numeric(levels(turk.data$stim_prevalence)[turk.data$stim_prevalence])

df2<-ddply(subset(turk.data, truth_conditions%in%c("TRUE",NA)), 
       .(trial_type, stim_determiner, workerid), summarise, 
       subj_prevalence = mean(implied_prevalence),
       subj_truth_prevalence = mean(stim_prevalence))

df2$subj_prevalence[is.na(df2$subj_prevalence)] <- df2$subj_truth_prevalence[!is.na(df2$subj_truth_prevalence)]
df2.bs<-bootstrap.ci(df2)
df2.bs$trial_type <- factor(df2.bs$trial_type, levels=c("truth_conditions","implied_prevalence"))

ggplot(df2.bs, aes(x=stim_determiner,y=subj_prevalence,fill=trial_type, group=trial_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_bw()+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=1)

```


# Experiment 2 -- prior elicitation 2 ways

### Experimental conditions

**implied prevalence** only, with no quantifier sentence

+ **catprop** - subjects were given evidence that the category and the property were relevant ("recently discovered"); also the cover story was elaborated (you are a zoologist)
+ **plain** is the CBG paradigm without the quantifier/generic sentence for evidence (bare bones)


```{r exp2}
setwd('/Users/mht/Documents/research/generics/cbg2010-replication/data/')
turk.data<-read.table('cbgR-exp2_anonymized-trials.tsv',header=T)
summary(turk.data)
```


Reaction time histograms

```{r}
ggplot(turk.data,aes(x=rt/60000,fill=trial_prompt))+
  geom_histogram()+
  facet_wrap(~trial_prompt)+
  guides(fill=F)+
  xlab('rt in minutes')+
  theme_bw()
```


Prevalence histograms / densities, broken up by cover story (catprop vs plain)

```{r}
ggplot(turk.data,aes(x=response,fill=trial_prompt))+
  geom_histogram(binwidth=5, aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]))+
  #geom_density()+
  facet_wrap(~trial_prompt)+
  guides(fill=F)+
  theme_bw()
```

Prevalence histograms / densities, collapsed across cover stories

```{r}
ggplot(turk.data,aes(x=response))+
  geom_histogram(binwidth=5, fill='blue', aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]))+
  #geom_density()+
  guides(fill=F)+
  theme_bw()
```

Histograms by subject, for each condition separately

```{r}
ggplot(subset(turk.data, trial_prompt=='catprop'),
       aes(x=response))+
  geom_histogram(binwidth=10,fill='blue')+
  facet_wrap(~workerid)+
  guides(fill=F)+
  scale_x_continuous(limits=c(0,110),breaks=c(0,25,50,75,100))+
  theme_bw()

ggplot(subset(turk.data, trial_prompt=='plain'),
       aes(x=response))+
  geom_histogram(binwidth=10,fill='red')+
  facet_wrap(~workerid)+
  guides(fill=F)+
  scale_x_continuous(limits=c(0,110),breaks=c(0,25,50,75,100))+
  theme_bw()
```

Average prior prevalence

```{r}

bootstrap.ci <- function(x){
  agr = aggregate(value ~ trial_prompt, data=x, FUN=mean)
  agr$CILow = aggregate(value ~ trial_prompt, data=x, FUN=ci.low)$value
  agr$CIHigh = aggregate(value ~ trial_prompt, data=x, FUN=ci.high)$value
  agr$YMin = agr$value - agr$CILow
  agr$YMax = agr$value + agr$CIHigh
  return(agr)
}
df.m<- melt(turk.data[,c("trial_prompt","response")],id.vars='trial_prompt')
df.b<-bootstrap.ci(df.m)

ggplot(df.b,aes(x=trial_prompt,y=value,fill=trial_prompt))+
  geom_bar(stat='identity',position=position_dodge(),width=0.4)+
    geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.1,
                size=1,
                position=position_dodge(0.5),
                colour='white')+
  guides(fill=F)+
  ylim(0,100)+
  theme_bw()
```


# Experiment 3 -- replicate experiment 4 of CBG

The idea now is to see if the generic theta differs across contexts, thus motivating a lifted variable model from a bayesian data analysis standpoint.

+ **truth conditions** = given a prevalence level (XX% of warfles have purple feathers) and a sentence (*generic*, *most*, *some*), answer if the sentence is True or False
+ **implied prevalence** = given a sentence (*generic*, *most*, *some*), answer with the percentage of *warfles that have purple feathers*

The sentence is between subjects (subjects see only generics or mosts or somes).

Within-subject is the context:

+ **dangerous**
+ **distinctive**
+ **extra irrelevant**
+ **bare** (from experiment 1, above)

```{r exp3}

library(ggthemes)


setwd('/Users/mht/Documents/research/generics/cbg2010-replication/data/')
td0<-read.table('cbgR-exp1_anonymized-trials.tsv',header=T)
#write.csv(td0, file='cbgR-exp1_anonymized-trials.csv')
td1<-read.table('cbgR-exp3_anonymized-trials.tsv',header=T)
#write.csv(td1, file='cbgR-exp3_anonymized-trials.csv')


td1$workerid<-td1$workerid+length(levels(factor(td0$workerid)))
td<-rbind(td0,td1)
td$workerid <- factor(td$workerid)
td$rt <- td$rt/1000
td$stim_prevalence <- factor(td$stim_prevalence)


td$implied_prevalence <- to.n(td$response)
td$truth_conditions <- factor(as.logical(levels(td$response)[td$response]), 
                              levels=c("TRUE","FALSE"))

```
Number of responses for each prevalence level (for truth conditions task)
```{r, echo=FALSE}
table(td1[,c("stim_determiner","stim_prevalence")])/6
```

Number of responses for implied prevalence task.
```{r, echo=FALSE}
table(subset(td1,trial_type=='implied_prevalence')[,c("stim_determiner")])/30
```



```{r}
df<-ddply(subset(td,trial_type=='truth_conditions'), 
      .(stim_determiner, stim_prevalence, stim_type), summarise, 
      true_responses= table(truth_conditions)[["TRUE"]]/length(truth_conditions))


ggplot(subset(td,trial_type=='implied_prevalence'),
          aes(x=implied_prevalence,fill=stim_type))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=10)+
  facet_grid(stim_type~stim_determiner)+
  theme_bw()+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'),
        strip.text.y =       element_text(size=14,color='black'))

b<-ggplot(df, aes(x=stim_prevalence,y=true_responses,colour=stim_type, 
                  group=stim_determiner))+
  geom_line(size=1,alpha=0.90)+
  facet_grid(stim_type~stim_determiner)+
  theme_bw()+
  ylab("proportion of 'true' responses")

grid.arrange(a,b)
```

Replicate figure 3 from CGB 2010 (w CIs)

```{r}

bootstrap.ci.tc <- function(x){
  
  agr = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=mean)
  agr$CILow = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.low)$truth_num
  agr$CIHigh = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.high)$truth_num
  agr$YMin = agr$truth_num - agr$CILow
  agr$YMax = agr$truth_num + agr$CIHigh
  return(agr)
}

tc<-subset(td,trial_type=='truth_conditions')
tc$truth_num <- 1*as.logical(tc$truth_conditions)
tc.bs<-bootstrap.ci.tc(tc)

ggplot(tc.bs, aes(x=factor(stim_prevalence),y=truth_num,colour=stim_type, group=stim_type))+
  geom_point(size=3, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=YMin,ymax=YMax,colour=stim_type),
              width=0.3,
              size=0.8,
              position=position_dodge(0.5))+
  facet_wrap(~stim_determiner)+
  theme_bw()+
  ylab("proportion of 'true' responses")+
  scale_colour_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))

```


Replicate figure 2 of CGB 2010
```{r}

bootstrap.ci <- function(x){
  
  agr = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=mean)
  agr$CILow = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=ci.low)$subj_prevalence
  agr$CIHigh = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=ci.high)$subj_prevalence
  agr$YMin = agr$subj_prevalence - agr$CILow
  agr$YMax = agr$subj_prevalence + agr$CIHigh
  return(agr)
}

td$stim_prevalence <- to.n(td$stim_prevalence)

df2<-ddply(subset(td, truth_conditions%in%c("TRUE",NA)), 
       .(trial_type, stim_determiner, stim_type, workerid), summarise, 
       subj_prevalence = mean(implied_prevalence),
       subj_truth_prevalence = mean(stim_prevalence))

df2$subj_prevalence[is.na(df2$subj_prevalence)] <- df2$subj_truth_prevalence[!is.na(df2$subj_truth_prevalence)]

df2.bs<-bootstrap.ci(df2)
df2.bs$trial_type <- factor(df2.bs$trial_type, levels=c("truth_conditions","implied_prevalence"))

ggplot(df2.bs, aes(x=stim_determiner,y=subj_prevalence,fill=trial_type, group=trial_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_bw()+
  facet_wrap(~stim_type,nrow=1)+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))

ggplot(df2.bs, aes(x=trial_type,y=subj_prevalence,fill=stim_type, group=stim_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_bw()+
  facet_wrap(~stim_determiner)+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))
```

# Bayesian data analysis

## Infer thresholds for quantifiers from implied prevalence task

```{r tfbt.ip.1}
setwd('/Users/mht/Documents/research/generics/cbg2010-replication/models/bayesian_analysis')
d0<-read.csv('post_bare_most_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
d0$quantifier<-'most'
d0$context<-'bare'
d1<-read.csv('post_danger_most_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
d1$quantifier<-'most'
d1$context<-'danger'
d2<-read.csv('post_distinct_most_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
d2$quantifier<-'most'
d2$context<-'distinct'
d3<-read.csv('post_irrelevant_most_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
d3$quantifier<-'most'
d3$context<-'irrelevant'

e0<-read.csv('post_bare_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
e0$quantifier<-'some'
e0$context<-'bare'
e1<-read.csv('post_danger_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
e1$quantifier<-'some'
e1$context<-'danger'
e2<-read.csv('post_distinct_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
e2$quantifier<-'some'
e2$context<-'distinct'
e3<-read.csv('post_irrelevant_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
e3$quantifier<-'some'
e3$context<-'irrelevant'

f0<-read.csv('post_bare_generic_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
f0$quantifier<-'generic'
f0$context<-'bare'
f1<-read.csv('post_danger_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
f1$quantifier<-'generic'
f1$context<-'danger'
f2<-read.csv('post_distinct_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
f2$quantifier<-'generic'
f2$context<-'distinct'
f3<-read.csv('post_irrelevant_some_implied_prevalence_mh10000_100L1norm_f3_alpha2.csv',header=F,col.names='value')
f3$quantifier<-'generic'
f3$context<-'irrelevant'

all.data<-rbind(f0,f1,f2,f3,e0,e1,e2,e3,d0,d1,d2,d3)

all.data$quantifier<- factor(all.data$quantifier)
all.data$context<-factor(all.data$context)

ggplot(data=all.data,aes(x=value,fill=context))+
  geom_histogram()+
  facet_grid(context~quantifier)+
  theme_bw()

```


## Infer thresholds for quantifiers from truth conditions task

```{r tfbt.tc.1}
g0<-read.csv('/Users/mht/Documents/research/generics/cbg2010-replication/models/bayesian_analysis/post_bare_generic_truth_conditions_mh1000_10_alpha3.csv',header=F)
qplot(data=g0,x=V1,geom='histogram', fill='blue')+  theme_bw()

```
