---
title: "cgb2010-replication"
author: "mht"
date: "December 2, 2014"
output: html_document
---


```{r exp1}
library(ggplot2)
library(plyr)
library(reshape2)
library(ggthemes)
library(gridExtra)
library(bootstrap)
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}


setwd('/Users/mht/Documents/research/generics/cbg2010-replication/')
turk.data<-read.table('cbg2010_anonymized-trials.tsv',header=T)

turk.data$implied_prevalence <- as.numeric(levels(turk.data$response)[turk.data$response])
turk.data$truth_conditions <- factor(as.logical(levels(turk.data$response)[turk.data$response]), levels=c("TRUE","FALSE"))

turk.data$stim_prevalence <- factor(turk.data$stim_prevalence)

```


Number of responses for each prevalence level (for truth conditions task)
```{r resp1Atab}
table(turk.data[,c("stim_determiner","stim_prevalence")])
```

Number of responses for implied prevalence task.
```{r resp2Btab}
table(subset(turk.data,trial_type=='implied_prevalence')[,c("stim_determiner")])
```



```{r}
df0= ddply(turk.data, 
           .(stim_determiner, trial_type, stim_prevalence), summarise,
          truth_endorsements = sum(truth_conditions==TRUE))

df<-ddply(subset(turk.data,trial_type=='truth_conditions'), 
      .(stim_determiner, stim_prevalence), summarise, 
      true_responses= table(truth_conditions)[["TRUE"]]/length(truth_conditions))


a<-ggplot(subset(turk.data,trial_type=='implied_prevalence'),aes(x=implied_prevalence,fill=stim_determiner))+
 # geom_line(stat='histogram')+
  geom_density(alpha=.5)+
  #geom_histogram(binwidth=10)+
  facet_wrap(~stim_determiner)+
  theme_bw()+
  guides(fill=F)

b<-ggplot(df, aes(x=stim_prevalence,y=true_responses,colour=stim_determiner, group=stim_determiner))+
  geom_line(size=1)+
  facet_wrap(~stim_determiner)+
  theme_bw()+
  ylab("proportion of 'true' responses")+
  guides(colour=F)


grid.arrange(a,b)
```

Replicate figure 3 from CGB 2010

```{r}
df<-ddply(subset(turk.data,trial_type=='truth_conditions'), 
      .(stim_determiner, stim_prevalence), summarise, 
      true_responses= table(truth_conditions)[["TRUE"]]/length(truth_conditions))

ggplot(df, aes(x=stim_prevalence,y=true_responses,colour=stim_determiner, group=stim_determiner))+
  geom_line(size=1)+
  facet_wrap(~stim_determiner,nrow=3)+
  theme_solarized()+
  ylab("proportion of 'true' responses")+
  guides(colour=F)

```


Replicate figure 2 of CGB 2010
```{r}

bootstrap.ci <- function(x){
  
  agr = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=mean)
  agr$CILow = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=ci.low)$subj_prevalence
  agr$CIHigh = aggregate(subj_prevalence ~ trial_type + stim_determiner, data=x, FUN=ci.high)$subj_prevalence
  agr$YMin = agr$subj_prevalence - agr$CILow
  agr$YMax = agr$subj_prevalence + agr$CIHigh
  return(agr)
}

turk.data$stim_prevalence <- as.numeric(levels(turk.data$stim_prevalence)[turk.data$stim_prevalence])

df2<-ddply(subset(turk.data, truth_conditions%in%c("TRUE",NA)), 
       .(trial_type, stim_determiner, workerid), summarise, 
       subj_prevalence = mean(implied_prevalence),
       subj_truth_prevalence = mean(stim_prevalence))

df2$subj_prevalence[is.na(df2$subj_prevalence)] <- df2$subj_truth_prevalence[!is.na(df2$subj_truth_prevalence)]

df2.bs<-bootstrap.ci(df2)
df2.bs$trial_type <- factor(df2.bs$trial_type, levels=c("truth_conditions","implied_prevalence"))

ggplot(df2.bs, aes(x=stim_determiner,y=subj_prevalence,fill=trial_type, group=trial_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_bw()+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=1)

```


# Experiment 2 -- prior elicitation 2 ways

trial_prompt == catprop is where subjects were given evidence that the category and the property were relevant ("recently discovered"); also the cover story was elaborated (you are a zoologist)

trial_prompt == plain is the cbg paradigm without the quantifier/generic sentence for evidence (bare bones)


```{r exp2}
setwd('/Users/mht/Documents/research/generics/cbg2010-replication/')
turk.data<-read.table('cbg2010prior_anonymized-trials.tsv',header=T)
summary(turk.data)
```


Reaction time histograms

```{r}
ggplot(turk.data,aes(x=rt/60000,fill=trial_prompt))+
  geom_histogram()+
  facet_wrap(~trial_prompt)+
  guides(fill=F)+
  xlab('rt in minutes')

ggplot(turk.data,aes(x=rt/60000,fill=trial_prompt))+
  geom_histogram()+
  facet_wrap(~trial_prompt)+
  guides(fill=F)+
  xlab('rt in minutes')+
  xlim(0,1)

```


Prevalence histograms / densities
```{r}
ggplot(turk.data,aes(x=response,fill=trial_prompt))+
  geom_histogram(binwidth=10)+
  #geom_density()+
  facet_wrap(~trial_prompt)+
  guides(fill=F)

ggplot(turk.data,aes(x=response))+
  geom_histogram(binwidth=10)+
  #geom_density()+
  guides(fill=F)

```

Density plots by subject, for each condition

```{r}
ggplot(subset(turk.data, trial_prompt=='catprop'),
       aes(x=response))+
  geom_histogram(binwidth=10,fill='blue')+
  #geom_density(fill='white')+
  facet_wrap(~workerid)+
  guides(fill=F)+
  scale_x_continuous(limits=c(0,110),breaks=c(0,25,50,75,100))

ggplot(subset(turk.data, trial_prompt=='plain'),
       aes(x=response))+
  geom_histogram(binwidth=10,fill='lightyellow')+
  #geom_density(fill='white')+
  facet_wrap(~workerid)+
  guides(fill=F)+
  scale_x_continuous(limits=c(0,110),breaks=c(0,25,50,75,100))
```

Average prior prevalence

```{r}

bootstrap.ci <- function(x){
  agr = aggregate(value ~ trial_prompt, data=x, FUN=mean)
  agr$CILow = aggregate(value ~ trial_prompt, data=x, FUN=ci.low)$value
  agr$CIHigh = aggregate(value ~ trial_prompt, data=x, FUN=ci.high)$value
  agr$YMin = agr$value - agr$CILow
  agr$YMax = agr$value + agr$CIHigh
  return(agr)
}
df.m<- melt(turk.data[,c("trial_prompt","response")],id.vars='trial_prompt')
df.b<-bootstrap.ci(df.m)

ggplot(df.b,aes(x=trial_prompt,y=value,fill=trial_prompt))+
  geom_bar(stat='identity',position=position_dodge(),width=0.4)+
    geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.1,
                size=1,
                position=position_dodge(0.5),
                colour='white')+
  guides(fill=F)+
  ylim(0,100)
```


# Experiment 3 -- replicate experiment 4 of CBG

The idea is to see if the generic theta differs across contexts, thus motivating a lifted variable model from a bayesian data analysis standpoint


```{r exp3}

library(ggthemes)


setwd('/Users/mht/Documents/research/generics/cbg2010-replication/data/')
td0<-read.table('cbgR-exp1_anonymized-trials.tsv',header=T)
#write.csv(td0, file='cbgR-exp1_anonymized-trials.csv')
td1<-read.table('cbgR-exp3_anonymized-trials.tsv',header=T)
#write.csv(td1, file='cbgR-exp3_anonymized-trials.csv')


td1$workerid<-td1$workerid+length(levels(factor(td0$workerid)))
td<-rbind(td0,td1)
td$workerid <- factor(td$workerid)
td$rt <- td$rt/1000
td$stim_prevalence <- factor(td$stim_prevalence)


td$implied_prevalence <- to.n(td$response)
td$truth_conditions <- factor(as.logical(levels(td$response)[td$response]), 
                              levels=c("TRUE","FALSE"))

```
Number of responses for each prevalence level (for truth conditions task)
```{r}
table(td1[,c("stim_determiner","stim_prevalence")])/6
```

Number of responses for implied prevalence task.
```{r}
table(subset(td1,trial_type=='implied_prevalence')[,c("stim_determiner")])/30
```




```{r}
df0= ddply(td, 
           .(stim_determiner, trial_type, stim_prevalence), summarise,
          truth_endorsements = sum(truth_conditions==TRUE))

df<-ddply(subset(td,trial_type=='truth_conditions'), 
      .(stim_determiner, stim_prevalence, stim_type), summarise, 
      true_responses= table(truth_conditions)[["TRUE"]]/length(truth_conditions))


  ggplot(subset(td,trial_type=='implied_prevalence'),
          aes(x=implied_prevalence,fill=stim_type))+
 # geom_line(stat='histogram')+
  #geom_density(alpha=.8)+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=10)+
  facet_grid(stim_type~stim_determiner)+
  theme_solarized()+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'),
        strip.text.y =       element_text(size=14,color='black'))

b<-ggplot(df, aes(x=stim_prevalence,y=true_responses,colour=stim_type, 
                  group=stim_determiner))+
  geom_line(size=1,alpha=0.90)+
  facet_wrap(stim_type~stim_determiner)+
  #theme_bw()+
  theme_solarized()+
  ylab("proportion of 'true' responses")


grid.arrange(a,b)
```

Replicate figure 3 from CGB 2010 (w CIs)

```{r}

bootstrap.ci.tc <- function(x){
  
  agr = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=mean)
  agr$CILow = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.low)$truth_num
  agr$CIHigh = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.high)$truth_num
  agr$YMin = agr$truth_num - agr$CILow
  agr$YMax = agr$truth_num + agr$CIHigh
  return(agr)
}

tc<-subset(td,trial_type=='truth_conditions')
tc$truth_num <- 1*as.logical(tc$truth_conditions)
tc.bs<-bootstrap.ci.tc(tc)


ggplot(tc.bs, aes(x=factor(stim_prevalence),y=truth_num, fill=stim_type))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
              width=0.2,
          #    size=1,
              position=position_dodge(0.9),
              colour='black')+
  facet_wrap(~stim_determiner)+
  theme_solarized()+
  ylab("proportion of 'true' responses")

ggplot(tc.bs, aes(x=factor(stim_prevalence),y=truth_num,colour=stim_type, group=stim_type))+
  geom_point(size=3, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=YMin,ymax=YMax,colour=stim_type),
              width=0.3,
              size=0.8,
              position=position_dodge(0.5))+
  facet_wrap(~stim_determiner)+
  theme_solarized()+
  ylab("proportion of 'true' responses")+
  scale_colour_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))






```


Replicate figure 2 of CGB 2010
```{r}

bootstrap.ci <- function(x){
  
  agr = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=mean)
  agr$CILow = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=ci.low)$subj_prevalence
  agr$CIHigh = aggregate(subj_prevalence ~ trial_type + stim_determiner + stim_type, data=x, FUN=ci.high)$subj_prevalence
  agr$YMin = agr$subj_prevalence - agr$CILow
  agr$YMax = agr$subj_prevalence + agr$CIHigh
  return(agr)
}

td$stim_prevalence <- to.n(td$stim_prevalence)

df2<-ddply(subset(td, truth_conditions%in%c("TRUE",NA)), 
       .(trial_type, stim_determiner, stim_type, workerid), summarise, 
       subj_prevalence = mean(implied_prevalence),
       subj_truth_prevalence = mean(stim_prevalence))

df2$subj_prevalence[is.na(df2$subj_prevalence)] <- df2$subj_truth_prevalence[!is.na(df2$subj_truth_prevalence)]

df2.bs<-bootstrap.ci(df2)
df2.bs$trial_type <- factor(df2.bs$trial_type, levels=c("truth_conditions","implied_prevalence"))

ggplot(df2.bs, aes(x=stim_determiner,y=subj_prevalence,fill=trial_type, group=trial_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_solarized()+
  facet_wrap(~stim_type,nrow=1)+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))

ggplot(df2.bs, aes(x=trial_type,y=subj_prevalence,fill=stim_type, group=stim_type))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=1,
                position=position_dodge(0.5),
                colour='black')+
  theme_solarized()+
  facet_wrap(~stim_determiner)+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x =       element_text(size=14,color='black'))
```

# Bayesian data analysis

## Infer thresholds for quantifiers from implied prevalence task

```{r tfbt1}
setwd('/Users/mht/Documents/research/generics/cbg2010-replication/models/')
posterior<-read.csv('post_bare-most_1000_100_L1f10_impliedPrev.csv',header=F)
qplot(data=posterior,x=V1,geom='histogram')


```


