---
title: "cbg-priors"
author: "mht"
date: "February 25, 2015"
output: html_document
---


```{r}
setwd("~/Documents/research/generics/cbg2010-replication/analysis")
d<-read.table('../data/cbgR-exp11-trials.tsv',header=T)
de<-read.table('../data/cbgR-exp11e-trials.tsv',header=T)
de$workerid<-de$workerid+length(unique(d$workerid))
d<-rbind(d,de)

d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d %>%   
  select(workerid,rt,trial_num,
              response0,response1,response2,response3,response4,
              stim_type) %>%
  rename(context=stim_type, trial=trial_num) %>%
  gather(option,value,-workerid,-rt,-context,-trial)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger-distinct')$roundval),
           table(filter(d.tidy,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev)) %>%
  group_by(type) %>%
  mutate(norm_value=value/sum(value))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"),
                     labels=c("dangerous & distinctive",
                              "nondistinctive & nondangerous",
                              "plain"))

ggplot(d.tidy0, aes(x=prev, y=norm_value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  xlab("\nprevalence")+
  ylab("proportion of responses\n")+
  scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(0,20,40,60,80,100),limits=c(-5,105))+
  theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)+
  guides(fill=F)

ggsave('../../talks/frisem_5815//figures/five_priors_dd-nn-p.png',width=20, height=10)


# d.tidy$context<-factor(d.tidy$context,
#                        levels=c("danger-distinct",
#                                 "nondistinctive",
#                                 "bare"), 
#                         labels=c("dangerous & distinctive", 
#                                  "nondistinctive & irrelevant",
#                                  "plain"))
# ggplot(d.tidy,aes(x=value,fill=context))+
#   geom_histogram(binwidth=1)+
#   facet_wrap(~context)+
#   guides(fill=F)+
#   scale_fill_brewer(type='qual',palette=6)+
#   xlab('prevalence')+
#   ggtitle('human elicited prior distribution')



# 
# ddply(d.tidy, .(context), summarise,
#       median = mean(value))
# 
# 
# 
# 
# dip.test(subset(d.tidy,context=='plain')$value)
# dip.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value)
# dip.test(subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# 
# contrasts(d.tidy$context)<-cbind(dd = c(-2,1,1), ni = c(0, 1, -1))
# contrasts(d.tidy$context)<-cbind(dd = c(1,0,-1), ni = c(-1, 2, -1))
# 
# rs<-lmer(value ~ context + (1 | workerid), data=d.tidy)
# summary(rs)
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!="nondistinctive & irrelevant"))
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!='dangerous & distinctive'))
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!='plain'))
# 
# kruskal.test(value ~ context, data = d.tidy) 
# 
# ks.test(subset(d.tidy,context=='plain')$value,
#         subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# ks.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value,
#         subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# ks.test(subset(d.tidy,context=='plain')$value,
#         subset(d.tidy,context=="nondistinctive & irrelevant")$value)


```

# Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo}
d.taboo<-d.tidy %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(value>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > 0 %")

```

# Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy %>%
  group_by(workerid, trial) %>%
  summarise(total = round(sum(value)/5)*5, # rounds to the nearest 5
            max = max(value),
            min = min(value)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("100 subjects x 6 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(1,6,1))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")

d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy<-d.tidy%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=value, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Single response, free response prior

## Dangerous & Distinct, Nondistinct, Plain

```{r prior1}
d<-read.csv('../data/cbg-prior1a-trials.csv',header=T)
d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d%>%select(workerid,rt,response0,stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger-distinct')$roundval),
           table(filter(d.tidy,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev)) %>%
  group_by(type) %>%
  mutate(norm_value=value/sum(value))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"),
                     labels=c("dangerous & distinctive",
                              "nondistinctive & nondangerous",
                              "plain"))


ggplot(d.tidy0, aes(x=prev, y=norm_value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  xlab("prevalence")+
  ylab("count")+
#  ggtitle("Single response prior")+
  ylab("proportion of responses\n")+
  scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(0,20,40,60,80,100),limits=c(-5,105))+
  theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)+
  guides(fill=F)+
  ylim(0,0.6)

ggsave('../../talks/frisem_5815//figures/one_priors_dd-nn-p.png',width=20, height=10)



```

## Danger, Distinct, Plain

```{r prior1b}
d<-read.csv('../data/cbg-prior1b-trials.csv',header=T)
d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d%>%select(workerid,rt,response0,stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger')$roundval),
           table(filter(d.tidy,context=='distinct')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         danger = Freq.1,
         distinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))




d.tidy0<-d.tidy0 %>% group_by(type) %>%
  mutate(value = value/sum(value))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  #scale_fill_brewer(type='qual',palette='Dark2')+
  xlab("\n prevalence")+
  ylab("proportion of responses \n")+
 # ggtitle("Single response prior")+
    theme_blackDisplay()+
  scale_fill_brewer(type='qual',palette='Set3')+
  guides(fill=F)+
  ylim(0,0.6)

ggsave('../../talks/frisem_5815/figures/ddp_1priors.png',width=16, height=6)



```



Binned histograms (garbage?)

```{r prior2}
d<-read.csv('../data/cbg-prior2a-trials.csv',header=T)
d$item <- paste(d$color,d$part,sep="_")
table(d$context,d$item)
table(d$context,d$part)


#maybe?
## yes: the experiment allowed you to advance if you had clicked the last slider, but not any of the other ones
d[is.na(d)]<-0

d<-d %>% filter(context=='bare')

d.tidy<-d %>% 
  select(workerid,rt,context,item,starts_with("bin"),-binOrder) %>%
  gather(bin,value,-workerid,-rt,-context, -item) %>%
  group_by(workerid,item) %>%
  mutate(val_normed = value/sum(value)) %>%
  separate(bin, into=c("thing","bin"), by="_") 

d.tidy$context<-factor(d.tidy$context,
                       levels=c("danger-distinct",
                                "nondistinctive",
                                "bare"), 
                        labels=c("dangerous & distinctive", 
                                 "nondistinctive & irrelevant",
                                 "plain"))

ggplot(d.tidy, aes(x=bin,y=value))+
  geom_bar(stat='identity')+
  facet_wrap(~workerid)+
  xlab('prevalence')


d.stats <- d.tidy %>% 
  group_by(context,bin) %>%
  summarise(mn = mean(value,na.rm=T),
            sterr = sem(value),
            mn_n = mean(val_normed, na.rm=T),
            sterr_n = sem(val_normed))

ggplot(d.stats,aes(x=bin,y=mn_n,fill=context))+
  geom_bar(stat='identity')+
  geom_errorbar(aes(ymin=mn_n-1.96*sterr_n,ymax=mn_n+1.96*sterr_n))+
  facet_wrap(~context)+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  xlab('prevalence')+
  ggtitle('human elicited prior distribution')
```


# 10 numbers

## Dangerous & Distinct, Nondistinct, Plain

```{r prior3.10numbers}
d<-read.csv(file = '../data/cbg-prior3-trials.csv')
#head(d)
d.tidy3<- d%>%
  select(stim_type, starts_with("response"), workerid, trial_num) %>%
  rename(context = stim_type,
         trial = trial_num) %>%
  gather(key, value, -context, -workerid, -trial) %>%
    mutate(roundval=round(value/10)*10)

## add counts to certain bins to fill out responses
d.tidy3<-bind_rows(d.tidy3,
data.frame(workerid=1000, context='danger-distinct',item='blank',
           key='hand',value=c(70,90), roundval=c(70,90))
)

d.tidy0<-data.frame(table(filter(d.tidy3,context=='bare')$roundval),
           table(filter(d.tidy3,context=='danger-distinct')$roundval),
           table(filter(d.tidy3,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev)) %>% group_by(type) %>%
  mutate(norm_value=value/sum(value))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"), 
                        labels=c("dangerous & distinctive", 
                                 "nondistinctive & irrelevant",
                                 "plain"))

ggplot(d.tidy0, aes(x=prev, y=norm_value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
 # scale_fill_brewer(type='qual',palette='Set1')+
  xlab("\n prevalence")+
  ylab("proportion of responses\n")+
  scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(0,20,40,60,80,100),limits=c(-5,105))+
  theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)+
  guides(fill=F)+
  ylim(0,0.7)

ggsave('../../talks/frisem_5815//figures/ten_priors_dd-nn-p.png',width=20, height=10)




```



### Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo1}
d.taboo<-d.tidy3 %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(value>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > 0 %")+
  scale_x_continuous(breaks = 0:10)

```

### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy3 %>%
  group_by(workerid, trial) %>%
  summarise(total = round(sum(value)/5)*5, # rounds to the nearest 5
            max = max(value),
            min = min(value)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("40 subjects x 3 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy3<-d.tidy3%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy3 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=value, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```
# Prior 6: 10 state, separate danger / distinct

```{r prior6}
d<-read.csv(file = '../data/cbg-prior6-trials.csv')

d$item<-paste(d$stim_color,d$stim_part,sep='_')
#head(d)
d.tidy6<- d%>%
  select(workerid,stim_type, item, starts_with("response"),trial_num) %>%
  rename(context = stim_type, trial=trial_num) %>%
  gather(key, value, -context, -item, -workerid, -trial) %>%
  #mutate(roundval=round(value/5)*5)
  mutate(roundval=round(value/10)*10)


d.tidy6<-bind_rows(d.tidy6,
data.frame(workerid=1000, context='danger',item='blank',key='hand',value=90, roundval=90)
)

d.tidy<-data.frame(table(filter(d.tidy6,context=='bare')$roundval),
           table(filter(d.tidy6,context=='danger')$roundval),
           table(filter(d.tidy6,context=='distinct')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         danger = Freq.1,
         distinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))

ggplot(d.tidy, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
    scale_fill_brewer(type='qual',palette='Dark2')+
  xlab("prevalence")+
  ylab("count")
  
```

### Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo2}
d.taboo<-d.tidy6 %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(value>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > 0 %")+
  ylab("number of trials")+
  scale_x_continuous(breaks = 0:10)

```

### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy6 %>%
  group_by(workerid, trial) %>%
  summarise(total = round(sum(value)/5)*5, # rounds to the nearest 5
            max = max(value),
            min = min(value)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("100 subjects x 3 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy6<-d.tidy6%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy6 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=value, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


## Danger, distinct, plain

Removing the noncompliant subjects

```{r danger.distinct.plain.minusBad}
d.good<-d.subj %>% filter(!((total==100)&(onedone==F))) %>%
  mutate(workeridtrial = paste(workerid,trial))

d$workeridtrial = paste(d$workerid,d$trial_num)

d.filtered <- d[d$workeridtrial%in%d.good$workeridtrial,]

d.tidy6<- d.filtered %>%
  select(workerid,stim_type, item, starts_with("response"),trial_num) %>%
  rename(context = stim_type, trial=trial_num) %>%
  gather(key, value, -context, -item, -workerid, -trial) %>%
  #mutate(roundval=round(value/5)*5)
  mutate(roundval=round(value/10)*10)

qplot(data=d.tidy6,x=value,fill=context,geom='histogram')+
  facet_wrap(~context)

d.tidy6<-bind_rows(d.tidy6,
data.frame(workerid=1000, context='danger',item='blank',key='hand',value=90, roundval=90)
)

d.tidy<-data.frame(table(filter(d.tidy6,context=='bare')$roundval),
           table(filter(d.tidy6,context=='danger')$roundval),
           table(filter(d.tidy6,context=='distinct')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         danger = Freq.1,
         distinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))

ggplot(d.tidy, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
    scale_fill_brewer(type='qual',palette='Dark2')+
  xlab("prevalence")+
  ylab("count")
  


dip.test(subset(d.tidy6,context=='bare')$value)
dip.test(subset(d.tidy6,context=="distinct")$value)
dip.test(subset(d.tidy6,context=='danger')$value)


contrasts(d.tidy$context)<-cbind(dd = c(-2,1,1), ni = c(0, 1, -1))
contrasts(d.tidy$context)<-cbind(dd = c(1,0,-1), ni = c(-1, 2, -1))
contrasts(d.tidy$context)

rs<-lmer(value ~ context + (1 | workerid), data=d.tidy)
summary(rs)

wilcox.test(value ~ context, 
            data = subset(d.tidy6, context!="distinct"))

wilcox.test(value ~ context, 
            data = subset(d.tidy6, context!='danger'))

wilcox.test(value ~ context, 
            data = subset(d.tidy6, context!='bare'))

kruskal.test(value ~ context, data = d.tidy6) 

ks.test(subset(d.tidy6,context=='bare')$value,
        subset(d.tidy6,context=='danger')$value)

ks.test(subset(d.tidy6,context=="distinct")$value,
        subset(d.tidy6,context=='danger')$value)

ks.test(subset(d.tidy6,context=='bare')$value,
        subset(d.tidy6,context=="distinct")$value)

```


# Prior 4: 5 sliders

```{r prior4}
d<-read.csv(file = '../data/cbg-prior4-trials.csv')
#head(d)
d.tidy4<- d%>%
  select(stim_type, starts_with("slider"), workerid, trial_num) %>%
  rename(context = stim_type,
          trial = trial_num) %>%
  gather(key, value, -context, -workerid, -trial)%>%
    mutate(roundval=round(value*10)*10)



d.tidy0<-data.frame(table(filter(d.tidy4,context=='bare')$roundval),
           table(filter(d.tidy4,context=='danger-distinct')$roundval),
           table(filter(d.tidy4,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev)) %>% 
  group_by(type) %>%
  mutate(norm_value=value/sum(value))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"), 
                        labels=c("dangerous & distinctive", 
                                 "nondistinctive & irrelevant",
                                 "plain"))

ggplot(d.tidy0, aes(x=prev, y=norm_value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
 # scale_fill_brewer(type='qual',palette='Set1')+
  xlab("\n prevalence")+
  ylab("proportion of responses\n")+
  scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(0,20,40,60,80,100),limits=c(-5,105))+
  theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)+
  guides(fill=F)+
  ylim(0,0.6)

ggsave('../../talks/frisem_5815//figures/fiveSliders_priors_dd-nn-p.png',
       width=20, height=10)



```



### Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo3}
d.taboo<-d.tidy4 %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(roundval>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > round(0) %")+
  scale_x_continuous(breaks = 0:5)

```

### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy4 %>%
  group_by(workerid, trial) %>%
  summarise(total = sum(roundval), # rounds to the nearest 5
            max = max(roundval),
            min = min(roundval)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("40 subjects x 6 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy4<-d.tidy4%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy4 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=roundval, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Prior 5: Accidental with 5 sliders

```{r prior5}
d<-read.csv(file = '../data//cbg-prior5-trials.csv')
#head(d)
d.tidy5<- d%>%
  select(workerid, stim_type, starts_with("slider"), trial_num) %>%
  rename(context = stim_type,
         trial=trial_num) %>%
  gather(key, value, -context, -workerid, -trial)%>%
    mutate(roundval=round(value*10)*10)


d.sum<-data.frame(table(d.tidy5$roundval)) %>%
  mutate(Var1 = to.n(Var1))

ggplot(data=d.sum, aes(x=Var1,y=Freq))+
  geom_bar(stat='identity',position=position_dodge())+
  ylab('frequency')+
  xlab('prevalence')+
  scale_x_continuous(breaks=seq(0,100,20))


```


### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy5 %>%
  group_by(workerid, trial) %>%
  summarise(total = sum(roundval), # rounds to the nearest 5
            max = max(roundval),
            min = min(roundval)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("40 subjects x 6 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy5<-d.tidy5%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy5 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=roundval, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Prior 7: Two stage with instructions

```{r prior7}
setwd("~/Documents/research/generics/cbg2010-replication/analysis")
d<-read.csv(file = '../turk/prior7/cbg-prior7-trials.csv')

d.tidy <- d %>%
    select(workerid, prevalence, nKinds, stimtype) %>%
    gather(key, response, prevalence, nKinds)

qplot(data=d.tidy, x=response, geom='histogram', fill=stimtype,
      position=position_dodge())+
  facet_wrap(~key,scales='free')


d.summ<- d%>%
  select(workerid, prevalence, nKinds, stimtype) %>%
  rename(type = stimtype) %>%
  group_by(workerid) %>%
  mutate(prevalence = prevalence / max(prevalence)) %>%
  ungroup() %>%
  group_by(type,workerid) %>%
  summarise(ave_prev = mean(prevalence),
            ave_kinds = mean(nKinds))

qplot(x=ave_prev,y=ave_kinds, color=type,geom='point',data=d.summ)+
  facet_wrap(~type)


d.hist <- d.summ<- d%>%
  select(workerid, prevalence, nKinds, stimtype) %>%
  rename(type = stimtype) %>%
  mutate(ave_prev = round(prevalence/10)*10,
         ave_kinds = round(nKinds/5)*5) %>%
  group_by(type, ave_prev) %>%
  summarise(heat = sum(nKinds))


ggplot(d.hist, aes(x=ave_prev,y=heat,fill=type))+
  geom_bar(stat='identity',position=position_dodge())+
  facet_wrap(~type)


d.tile <- d.summ<- d%>%
  select(workerid, prevalence, nKinds, stimtype) %>%
  rename(type = stimtype) %>%
  mutate(ave_prev = round(prevalence/10)*10,
         ave_kinds = round(nKinds/5)*5) %>%
  group_by(type, ave_prev, ave_kinds) %>%
  summarise(heat = length(ave_prev))

ggplot(d.tile, aes(x=ave_prev, y=ave_kinds, fill=heat))+
  geom_tile()+
  facet_wrap(~type)


```
Add ghost 0s

```{r}
a<- d %>%
  mutate(prevalence = 0,
         nKinds = 1000-nKinds)

d.tidy<- #bind_rows(d,a) %>%
  d %>%
  select(workerid, prevalence, nKinds, stimtype) %>%
  rename(type = stimtype) %>%
  group_by(workerid) %>%
  mutate(prevalence = prevalence / max(prevalence)) %>%
  ungroup() %>%
  mutate(ave_prev = round(prevalence*10)/10,
         ave_kinds = round(nKinds/5)*5,
         absent_prev = 0) %>%
  group_by(type, ave_prev) %>%
  summarise(heat = sum(nKinds))


ggplot(d.tidy, aes(x=ave_prev,y=heat,fill=type))+
  geom_bar(stat='identity',position=position_dodge())+
  facet_wrap(~type)

```
