---
title: "cbg-priors"
author: "mht"
date: "February 25, 2015"
output: html_document
---


```{r}
setwd("~/Documents/research/generics/cbg2010-replication/analysis")
d<-read.table('../data/cbgR-exp11-trials.tsv',header=T)
de<-read.table('../data/cbgR-exp11e-trials.tsv',header=T)
de$workerid<-de$workerid+length(unique(d$workerid))
d<-rbind(d,de)

d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d %>%   
  select(workerid,rt,trial_num,
              response0,response1,response2,response3,response4,
              stim_type) %>%
  rename(context=stim_type, trial=trial_num) %>%
  gather(option,value,-workerid,-rt,-context,-trial)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger-distinct')$roundval),
           table(filter(d.tidy,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  scale_fill_brewer(type='qual',palette='Set1')+
  xlab("prevalence")+
  ylab("count")



# d.tidy$context<-factor(d.tidy$context,
#                        levels=c("danger-distinct",
#                                 "nondistinctive",
#                                 "bare"), 
#                         labels=c("dangerous & distinctive", 
#                                  "nondistinctive & irrelevant",
#                                  "plain"))
# ggplot(d.tidy,aes(x=value,fill=context))+
#   geom_histogram(binwidth=1)+
#   facet_wrap(~context)+
#   guides(fill=F)+
#   scale_fill_brewer(type='qual',palette=6)+
#   xlab('prevalence')+
#   ggtitle('human elicited prior distribution')



# 
# ddply(d.tidy, .(context), summarise,
#       median = mean(value))
# 
# 
# 
# 
# dip.test(subset(d.tidy,context=='plain')$value)
# dip.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value)
# dip.test(subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# 
# contrasts(d.tidy$context)<-cbind(dd = c(-2,1,1), ni = c(0, 1, -1))
# contrasts(d.tidy$context)<-cbind(dd = c(1,0,-1), ni = c(-1, 2, -1))
# 
# rs<-lmer(value ~ context + (1 | workerid), data=d.tidy)
# summary(rs)
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!="nondistinctive & irrelevant"))
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!='dangerous & distinctive'))
# 
# wilcox.test(value ~ context, 
#             data = subset(d.tidy, context!='plain'))
# 
# kruskal.test(value ~ context, data = d.tidy) 
# 
# ks.test(subset(d.tidy,context=='plain')$value,
#         subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# ks.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value,
#         subset(d.tidy,context=='dangerous & distinctive')$value)
# 
# ks.test(subset(d.tidy,context=='plain')$value,
#         subset(d.tidy,context=="nondistinctive & irrelevant")$value)


```

# Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo}
d.taboo<-d.tidy %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(value>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > 0 %")

```

# Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy %>%
  group_by(workerid, trial) %>%
  summarise(total = round(sum(value)/5)*5, # rounds to the nearest 5
            max = max(value),
            min = min(value)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("100 subjects x 6 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(1,6,1))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")

d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy<-d.tidy%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=value, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Single response, free response prior

## Dangerous & Distinct, Nondistinct, Plain

```{r prior1}
d<-read.csv('../data/cbg-prior1a-trials.csv',header=T)
d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d%>%select(workerid,rt,response0,stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger-distinct')$roundval),
           table(filter(d.tidy,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  scale_fill_brewer(type='qual',palette='Set1')+
  xlab("prevalence")+
  ylab("count")+
  ggtitle("Single response prior")
```

## Danger, Distinct, Plain

```{r prior1b}
d<-read.csv('../data/cbg-prior1b-trials.csv',header=T)
d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d%>%select(workerid,rt,response0,stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)%>%
  mutate(roundval=round(value/10)*10)


d.tidy0<-data.frame(table(filter(d.tidy,context=='bare')$roundval),
           table(filter(d.tidy,context=='danger')$roundval),
           table(filter(d.tidy,context=='distinct')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         danger = Freq.1,
         distinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("danger",
                                "distinct",
                                "plain"))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  scale_fill_brewer(type='qual',palette='Dark2')+
  xlab("prevalence")+
  ylab("count")+
  ggtitle("Single response prior")
```



Binned histograms (garbage?)

```{r prior1}
d<-read.csv('../data/cbg-prior2a-trials.csv',header=T)
d$item <- paste(d$color,d$part,sep="_")
table(d$context,d$item)
table(d$context,d$part)


#maybe?
## yes: the experiment allowed you to advance if you had clicked the last slider, but not any of the other ones
d[is.na(d)]<-0

d.tidy<-d %>% 
  select(workerid,rt,context,item,starts_with("bin"),-binOrder) %>%
  gather(bin,value,-workerid,-rt,-context, -item) %>%
  group_by(workerid,item) %>%
  mutate(val_normed = value/sum(value)) %>%
  separate(bin, into=c("thing","bin"), by="_") 

d.tidy$context<-factor(d.tidy$context,
                       levels=c("danger-distinct",
                                "nondistinctive",
                                "bare"), 
                        labels=c("dangerous & distinctive", 
                                 "nondistinctive & irrelevant",
                                 "plain"))
d.stats <- d.tidy %>% 
  group_by(context,bin) %>%
  summarise(mn = mean(value,na.rm=T),
            sterr = sem(value),
            mn_n = mean(val_normed, na.rm=T),
            sterr_n = sem(val_normed))

ggplot(d.stats,aes(x=bin,y=mn_n,fill=context))+
  geom_bar(stat='identity')+
  geom_errorbar(aes(ymin=mn_n-1.96*sterr_n,ymax=mn_n+1.96*sterr_n))+
  facet_wrap(~context)+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  xlab('prevalence')+
  ggtitle('human elicited prior distribution')
```


# 10 numbers

## Dangerous & Distinct, Nondistinct, Plain

```{r prior3}
d<-read.csv(file = '../data/cbg-prior3-trials.csv')
#head(d)
d.tidy3<- d%>%
  select(stim_type, starts_with("response"), workerid, trial_num) %>%
  rename(context = stim_type,
         trial = trial_num) %>%
  gather(key, value, -context, -workerid, -trial) %>%
    mutate(roundval=round(value/10)*10)

## add counts to certain bins to fill out responses
d.tidy3<-bind_rows(d.tidy3,
data.frame(workerid=1000, context='danger-distinct',item='blank',
           key='hand',value=c(70,90), roundval=c(70,90))
)

d.tidy0<-data.frame(table(filter(d.tidy3,context=='bare')$roundval),
           table(filter(d.tidy3,context=='danger-distinct')$roundval),
           table(filter(d.tidy3,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  scale_fill_brewer(type='qual',palette='Set1')+
  xlab("prevalence")+
  ylab("count")
```



### Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo}
d.taboo<-d.tidy3 %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(value>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > 0 %")+
  scale_x_continuous(breaks = 0:10)

```

### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy3 %>%
  group_by(workerid, trial) %>%
  summarise(total = round(sum(value)/5)*5, # rounds to the nearest 5
            max = max(value),
            min = min(value)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("40 subjects x 3 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy3<-d.tidy3%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy3 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=value, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Prior 4: 5 sliders

```{r prior4}
d<-read.csv(file = '../data/cbg-prior4-trials.csv')
#head(d)
d.tidy4<- d%>%
  select(stim_type, starts_with("slider"), workerid, trial_num) %>%
  rename(context = stim_type,
          trial = trial_num) %>%
  gather(key, value, -context, -workerid, -trial)%>%
    mutate(roundval=round(value*10)*10)



d.tidy0<-data.frame(table(filter(d.tidy4,context=='bare')$roundval),
           table(filter(d.tidy4,context=='danger-distinct')$roundval),
           table(filter(d.tidy4,context=='nondistinctive')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         dangerdistinct = Freq.1,
         nondistinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))


d.tidy0$type<-factor(d.tidy0$type,
                       levels=c("dangerdistinct",
                                "nondistinct",
                                "plain"))

ggplot(d.tidy0, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
  scale_fill_brewer(type='qual',palette='Set1')+
  xlab("prevalence")+
  ylab("count")

```



### Distinctive manipulation check

Does distinctive imply taboo? That is, if you rate one animal as having it, do you set all the others to 0? (compare with other types)

```{r distinctive.taboo}
d.taboo<-d.tidy4 %>%
  group_by(workerid,trial, context) %>%
  summarise(n.positive = sum(roundval>0))

qplot(data=d.taboo,x=n.positive,geom='histogram')+
  facet_wrap(~context)+
  xlab("number of animal kinds with > round(0) %")+
  scale_x_continuous(breaks = 0:5)

```

### Compliance

How much do subjects put for each trial? (What do their numbers sum to?)

"onedone" here means subject puts 100 for one of the animals, and all 0s otherwise
```{r}

d.subj <- d.tidy4 %>%
  group_by(workerid, trial) %>%
  summarise(total = sum(roundval), # rounds to the nearest 5
            max = max(roundval),
            min = min(roundval)) %>%
  mutate(onedone=((total==100)&(max==100)))

d.subj0<-data.frame(table(d.subj$total,d.subj$onedone)) %>%
  mutate(total = to.n(Var1)) %>%
  rename(onedone = Var2)

ggplot(data=d.subj0,aes(x=total,y=Freq, fill=onedone))+
  geom_bar(stat='identity',position=position_dodge())+
  xlab("total for one trial")+
  ylab("number of trials")+
  ggtitle("40 subjects x 6 trials/subject")
```


How many people make their responses add to 100?


```{r}

d.bad<-d.subj %>% filter((total==100)&(onedone==F))

print("number of subjects who do this 100 behavior at least once")

length(levels(factor(d.bad$workerid)))

print("total number of trials with this 100 behavior")
length(d.bad$workerid)

qplot(data=data.frame(table(d.bad$workerid)), x=Freq, geom='histogram')+
  scale_x_continuous(breaks=seq(0:4))+
  ggtitle("number of noncompliant trials / subject")+
  xlab("number of noncompliant trials")+
  ylab("number of subjects")


d.bad<-d.bad %>% mutate(id = paste(workerid,trial))
d.tidy4<-d.tidy4%>% mutate(id = paste(workerid,trial))

d.culprits<-d.tidy4 %>% filter(id%in%d.bad$id)

qplot(data=d.culprits, x=roundval, geom='histogram')+
  scale_x_continuous(breaks=seq(0,100,10), limits=c(0,100))+
  ggtitle("distribution of responses")+
  xlab("response in a noncompliant trial")+
  ylab("number of responses")

```


# Prior 5: Accidental with 5 sliders

```{r prior5}
setwd(dir = '../prior5')
d<-read.csv(file = 'cbg-prior5-trials.csv')
#head(d)
d.tidy5<- d%>%
  select(workerid, stim_type, starts_with("slider")) %>%
  rename(context = stim_type) %>%
  gather(key, value, -context, -workerid)

ggplot(d.tidy5,aes(x=value))+
  geom_density(adjust=0.25)+
  #geom_histogram(binwidth=0.01)+
  facet_wrap(~context)+
  xlim(0,1)

d.tidy5$roundval<-round(d.tidy5$value*10)*10

d.sum<-data.frame(table(d.tidy5$roundval)) %>%
  mutate(Var1 = to.n(Var1))

ggplot(data=d.sum, aes(x=Var1,y=Freq))+
  geom_bar(stat='identity',position=position_dodge())+
  ylab('frequency')+
  xlab('prevalence')+
  scale_x_continuous(breaks=seq(0,100,20))



d.tidy5 %>%
  group_by(context) %>%
  summarise(mean(value))


n.subj<-length(levels(factor(d.tidy5$workerid)))

db.total=data.frame()
for (i in 1:1000){
  samp.subj<-sample.int(n.subj,replace=T) 
  samp.tidy<-d.tidy5[d.tidy5$workerid%in%samp.subj,]
  df.temp<-data.frame(matrix(table(samp.tidy$roundval)+1,nrow=1))
  db.total<-bind_rows(db.total,df.temp)
}

db.total<-db.total[complete.cases(db.total),]
file.path<-'../../models/'
write.csv(db.total, file=paste(file.path,'bootstrap_acc_priors.csv',sep=''))



```




# Prior 6: 10 state, separate danger / distinct

```{r prior6}
setwd(dir = '~/Documents/research/generics/cbg2010-replication/turk/prior6')
d<-read.csv(file = 'cbg-prior6-trials.csv')

d$item<-paste(d$stim_color,d$stim_part,sep='_')
#head(d)
d.tidy6<- d%>%
  select(workerid,stim_type, item, starts_with("response")) %>%
  rename(context = stim_type) %>%
  gather(key, value, -context, -item, -workerid) %>%
  #mutate(roundval=round(value/5)*5)
  mutate(roundval=round(value/10)*10)



d.tidy<-d.tidy6

d.tidy %>%
  group_by(context) %>%
  summarise(mn = mean(value),
            hi = mean(value)+1.96*sem(value),
            lo = mean(value) - 1.96*sem(value))

ggplot(d.tidy,aes(x=value))+
  geom_histogram(binwidth=1)+
  #facet_wrap(~item,scales='free')+
  facet_wrap(~context)+
  xlim(0,100)

## add counts to certain bins to fill out responses
d.tidy6<-bind_rows(d.tidy6,
data.frame(workerid=1000, context='danger',item='blank',key='hand',value=85, roundval=85),
data.frame(workerid=1000, context='distinct',item='blank',key='hand',value=55, roundval=55)
)

d.tidy<-data.frame(table(filter(d.tidy6,context=='bare')$roundval),
           table(filter(d.tidy6,context=='danger')$roundval),
           table(filter(d.tidy6,context=='distinct')$roundval)) %>%
  select(Var1,Freq,Freq.1,Freq.2) %>%
  rename(prev=Var1,
         plain = Freq,
         danger = Freq.1,
         distinct = Freq.2) %>%
  gather(type, value, -prev) %>%
  mutate(prev = to.n(prev))

ggplot(d.tidy, aes(x=prev, y=value, fill=type))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~type)+
    scale_fill_brewer(type='qual',palette='Dark2')+
  xlab("prevalence")+
  ylab("count")


  
```



```{r sep.dang.dist.priorstats}
setwd("~/Documents/research/generics/cbg2010-replication/data")
d<- read.csv('cbg-prior0b-trials.csv')
#d0<- read.csv('cbg-prior1b-trials.csv')
#d<-d0

d.tidy<-d%>%   select(workerid,rt,
              response0,response1,response2,response3,response4,
              stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)
#d.tidy<-d%>%   select(workerid,rt,
#              response0,
#              stim_type) %>%
#  rename(context=stim_type) %>%
#  gather(option,value,-workerid,-rt,-context)

d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)

d.tidy %>%
  group_by(context) %>%
  #summarise(median(value))
  summarise(mean(value))




d.tidy$context<-factor(d.tidy$context,
                       levels=c("bare",
                                "danger",
                                "distinct"))


ggplot(d.tidy,aes(x=value,fill=context))+
  geom_histogram(binwidth=0.5)+
  facet_wrap(~context)+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  xlab('prevalence')+
  ggtitle('human elicited prior distribution')




d.tidy$roundval<-round(d.tidy$value/10)*10
out<-data.frame(table(d.tidy$context, d.tidy$roundval))
out$Var2<-to.n(out$Var2)


ggplot(out,aes(x=Var2,y=Freq, fill=Var1))+
  geom_bar(stat='identity')+
  facet_grid(.~Var1)+
  scale_fill_brewer(type='qual',palette='Dark2')+
  xlab('\n % of kind with feature')+
  #  theme_blackDisplay()+
    theme(strip.background = element_blank(),
       strip.text.y = element_text(angle=0),
        legend.position='bottom',
        legend.direction='horizontal')+
  guides(fill=F)+
  scale_x_continuous(breaks=seq(0,100,20))

#ggsave('../../semfest-2015/figures/exp2.png',width=20, height=10)



plotpath = "~/Documents/research/generics/cogsci-2015//paper/figures/"

# 
# ggsave(filename=paste(plotpath,'elicited_priors.png',sep=''),
#        plot=exp2,
#        width=12,
#        height=4.5)



dip.test(subset(d.tidy,context=='bare')$value)
dip.test(subset(d.tidy,context=="distinct")$value)
dip.test(subset(d.tidy,context=='danger')$value)


contrasts(d.tidy$context)<-cbind(dd = c(-2,1,1), ni = c(0, 1, -1))
contrasts(d.tidy$context)<-cbind(dd = c(1,0,-1), ni = c(-1, 2, -1))
contrasts(d.tidy$context)

rs<-lmer(value ~ context + (1 | workerid), data=d.tidy)
summary(rs)

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!="distinct"))

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!='danger'))

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!='bare'))

kruskal.test(value ~ context, data = d.tidy) 

ks.test(subset(d.tidy,context=='bare')$value,
        subset(d.tidy,context=='danger')$value)

ks.test(subset(d.tidy,context=="distinct")$value,
        subset(d.tidy,context=='danger')$value)

ks.test(subset(d.tidy,context=='bare')$value,
        subset(d.tidy,context=="distinct")$value)
```


