---
title: "asymmetry"
author: "mht"
date: "August 12, 2015"
output: html_document
---


```{r helpers, echo=F}
library(coda)
library(ggthemes)
sem.2AFC <- function(p, n){return(sqrt((p*(1-p))/n))}
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
avePrevScore <- function(responses,prevalences){
  avePrev<-if (sum(responses)>0){
    sum(responses*prevalences)/sum(responses)
  } else {
    100
  }
  return(avePrev)
}

theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}

ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) -quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}

ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,
           .975,na.rm=na.rm) - mean(x,na.rm=na.rm)}

bootstrap.ci.byItem <- function(x){
  agr = aggregate(response ~ stim_property + type, data=x, FUN=mean)
  agr$CILow = aggregate(response ~ stim_property +type, data=x, FUN=ci.low)$response
  agr$CIHigh = aggregate(response ~ stim_property+ type, data=x, FUN=ci.high)$response
  agr$YMin = agr$response - agr$CILow
  agr$YMax = agr$response + agr$CIHigh
  return(agr)
}


bootstrap.ci.ByType <- function(x){
  agr = aggregate(response ~ type, data=x, FUN=mean)
  agr$CILow = aggregate(response ~ type, data=x, FUN=ci.low)$response
  agr$CIHigh = aggregate(response ~ type, data=x, FUN=ci.high)$response
  agr$YMin = agr$response - agr$CILow
  agr$YMax = agr$response + agr$CIHigh
  return(agr)
}



```


# Interpretation (L1) by Item



### human data

```{r data.byItem}
d<-read.csv('~/Documents/research/generics/models/data/asymmetry-2-trials-medSplitAccidental.csv')

d.implied<- d %>% filter(trial_type=='implied_prevalence')

d.impItem<-bootstrap.ci.byItem(d.implied)


d.impItem$stim_property<-with(d.impItem, 
                         reorder(stim_property, response, function(x) x))



ggplot(data=d.impItem, aes(x=stim_property, y=response, fill= type))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=0.5, size = 1.5,
                color='black')+
  xlab("")+
  ylab("\n implied prevalence")+
  scale_y_continuous(breaks=c(-0.5,0,0.5),labels=c("0","0.5","1"))+
  coord_flip()+
  scale_fill_solarized()

```



### model results

```{r load.byItem}
d<-read.csv('~/Documents/research/generics/models/data/asymmetry-2-trials-medSplitAccidental.csv')
d.implied<- d %>% filter(trial_type=='implied_prevalence')


m1<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-implied-byItem-phi-priord50iter20000_mh100000a.csv")
m2<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-implied-byItem-phi-priord50iter20000_mh100000b.csv")


samples = 50000
d<-bind_rows(m1,m2)

d.params<-data.frame(Parameter = rep(d$Parameter, 
                               1+samples*d$Probability),
                     Item = rep(d$Item, 
                               1+samples*d$Probability),
                    Prevalence = rep(d$Prevalence, 
                                   1+samples*d$Probability),
                    Response = rep(d$Value, 
                                   1+samples*d$Probability)
                    )
```


## Posterior over parameters
```{r posterior.parameters.byItem}
d.opt <- d.params %>% filter((Item%in%c('speakerOptimality','phi')))

d.opt %>% group_by(Item) %>%
  summarize(MAP = estimate_mode(Response),
            credHigh = HPDhi(Response),
            credLow = HPDlo(Response))


a<-ggplot(d.opt %>% filter(Item =='speakerOptimality'), aes(x=Response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=0.3)+
  #facet_grid(Item~Parameter, scales='free')+
  xlim(0,20)+
  ylab("Posterior probability")+
  xlab(expression(lambda))#+
  #theme_black()

b<-ggplot(d.opt %>% filter(Item =='phi'), aes(x=Response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=0.018)+
  facet_wrap(~Item)+
  #facet_grid(Item~Parameter, scales='free')+
  xlim(0,1)+
  ylab("Posterior probability")+
  xlab(expression(phi))#+
  #theme_black()

plt1<-arrangeGrob(a,b,nrow=1)
plt1
#ggsave(plt1,file='~/Documents/research/generics/manuscript/figures/asymmetry-byItem-params-2x50k.pdf', height = 4)

```

## Posterior predictives

```{r posterior.predictives.byItem}


d.pp <- d.params %>% filter((Parameter%in%c('truth_conditions',
                                            'implied_prevalence')) & 
                (!(Item%in%c('speakerOptimality','phi')))) %>%
  group_by(Item) %>%
  summarize(MAP = estimate_mode(Response),
            credHigh = HPDhi(Response),
            credLow = HPDlo(Response))




dm.items<- left_join(d.impItem %>% rename(Item=stim_property), d.pp)

dm.items$type<-factor(dm.items$type, 
                        levels=c("part","vague", 
                                 "color", "accidental_high", "accidental_low"),
                         labels = c("body parts", "vague parts",
                                    "color parts", "common accidental",
                                    "rare accidental"))


ggplot(dm.items, aes(x=MAP, y = response, color=type))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, linetype=2, alpha=0.6)+
  geom_errorbar(aes(ymin = YMin, ymax=YMax))+
  geom_errorbarh(aes(xmin = credLow, xmax = credHigh))+
  xlim(0,1.05)+
  ylim(0,1.05)+
  xlab("Model posterior predictive")+
  ylab("Human interpretation of prevalence")+
  scale_color_brewer(palette='Set1')+
  coord_fixed()+
  guides(color=guide_legend(title="Property type"))

#ggsave(file='~/Documents/research/generics/manuscript/figures/implied-byItem-mh100kX2.pdf', width = 9, height = 5)


with(dm.items, cor(MAP, response))^2
with(dm.items, mse(MAP, response))
```


### Does a priori mean prevalence when present (Gamma) predict implied prevalence?


```{r prior.prevalence.byItem}
d1<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000a.csv")
d2<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000b.csv")
d3<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000c.csv")

samples = 50000
d.tidy<-bind_rows(d1,d2,d3)


#d.tidy <- d


d.params<-data.frame(Parameter = rep(d.tidy$Parameter, 
                               1+samples*d.tidy$Probability),
                     Item = rep(d.tidy$Item, 
                               1+samples*d.tidy$Probability),
                Prevalence = rep(d.tidy$Prevalence, 
                               1+samples*d.tidy$Probability),
                Response = rep(d.tidy$Value, 
                               1+samples*d.tidy$Probability))
  


d.summary<-d.params %>% 
  group_by(Parameter,Item, Prevalence) %>%
  summarise(expectation = mean(Response),
              MAP = estimate_mode(Response),
            credHi = HPDhi(Response),
            credLo = HPDlo(Response))



d.impWPrev<-left_join(d.implied,
          d.summary %>% filter(Item=='response1' & Prevalence=='gamma') %>%
            select(Parameter, MAP) %>%
            rename(stim_property=Parameter))


rs<-lmer(data=d.impWPrev,
     response~MAP+ (1+MAP|workerid))
summary(rs)

 
d.mcp<-d.summary %>% filter(Item=='response1' & Prevalence =='gamma') %>%
  rename(priorMAP = MAP, 
         priorHigh = credHi,
         priorLow = credLo) %>%
  ungroup() %>%
  select(-Item, -Prevalence) %>%
  rename(Item = Parameter)

dmp.items<-left_join(dm.items, d.mcp)

with(dmp.items, cor(priorMAP, response))^2
with(dmp.items, mse(priorMAP, response))

ggplot(dmp.items, aes(x=priorMAP, y = response, color = type))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, linetype=2)+
  geom_errorbar(aes(ymin = YMin, ymax=YMax))+
  geom_errorbarh(aes(xmin = priorLow, xmax = priorMAP))+
  xlim(0,1)+
  ylim(0,1)+
  xlab("Mean conditional prevalence")+
  ylab("Human judgment")+
  scale_color_brewer(palette='Set1')+
  coord_fixed()+
  guides(color=guide_legend(title="Property type"))

#ggsave(file='~/Documents/research/generics/manuscript/figures/implied-mcp-byItem-mh100kX2.pdf')

```






# Asymmetry between truth conditions and implied prevalence

Load and process human data

```{r data.byType}
d<-read.csv('~/Documents/research/generics/models/data/asymmetry-2-trials-medSplitAccidental.csv')

d.accept<- d %>% filter(trial_type=='truth_conditions')
d.implied<- d %>% filter(trial_type=='implied_prevalence')

d.aveImpPrev <- bootstrap.ci.ByType(d.implied 
                                    %>% mutate(response=response*100)) %>%
  mutate(src = "implied")

# calculate average acceptable prevalence for each workerid and type
d.aveAccPrev <- d.accept %>%
  mutate(response = as.numeric(response==1)) %>%
  group_by(workerid, type) %>%
  summarise(response = avePrevScore(response,stim_prevalence))

d.aveAccPrev.summary <- bootstrap.ci.ByType(d.aveAccPrev) %>%
  mutate(src='accept')


d.asymSummary<-bind_rows(d.aveImpPrev, d.aveAccPrev.summary)
d.asymSummary$type<-with(d.asymSummary %>% filter(src=='implied'), 
                             reorder(type, response, function(x) x))

d.asymSummary<-d.asymSummary %>%
  rename(task = src,
         avePrev = response) %>%
  mutate(src = 'data')

ggplot(d.asymSummary,
       aes(x=type, y = avePrev, fill = task))+
  geom_bar(position = position_dodge(0.7), stat='identity', width = 0.7)+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                position=position_dodge(0.7), width=0.3)

```


### model

Load model results
```{r load.byType}

d1<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asymmetry-2so-2phi-incrmh100000_burn50000-incrmh50ka.csv")
d2<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asymmetry-2so-2phi-incrmh100000_burn50000-incrmh50kb.csv")
d3<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asymmetry-2so-2phi-incrmh100000_burn50000-incrmh50kc.csv")


samples = 50000
d<-bind_rows(d1,d2,d3)

d.params<-data.frame(Parameter = rep(d$Parameter, 
                               1+samples*d$Probability),
                     Item = rep(d$Item, 
                               1+samples*d$Probability),
                    Prevalence = rep(d$Prevalence, 
                                   1+samples*d$Probability),
                    Response = rep(d$Value, 
                                   1+samples*d$Probability)
                    )

```


## Posteriors over parameters


```{r posterior.parameters.byType}

d.opt <- d.params %>% filter((Parameter%in%c('speakerOptimality','phi')))


d.opt <- mutate(d.opt, Item = factor(Item, label=c("Implied prevalence task", "Truth judgments task")))

ggplot(d.opt %>% filter(Parameter =='speakerOptimality'), aes(x=Response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=0.4)+
  facet_wrap(~Item)+
  #facet_grid(Item~Parameter, scales='free')+
  xlim(0,20)+
  ylab("Posterior probability")+
  xlab(expression(lambda))#+
  #theme_black()

#ggsave(file='~/Documents/research/generics/manuscript/figures/asymmetry-speakeropts-3x50k.pdf', height = 4)



ggplot(d.opt %>% filter(Parameter =='phi'), aes(x=Response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),binwidth=0.02)+
  facet_wrap(~Item)+
  #facet_grid(Item~Parameter, scales='free')+
  xlim(0,1)+
  ylab("Posterior probability")+
  xlab(expression(phi))#+
  #theme_black()

#ggsave(file='~/Documents/research/generics/manuscript/figures/asymmetry-phi-3x50k.pdf', height = 4)

d.opt %>%
  group_by(Item, Parameter) %>%
  summarise(MAP = estimate_mode(Response),
            credLo = HPDlo(Response),
            credHi = HPDhi(Response))

```


## Posterior predictives for asymmetry


```{r posterior.predictives.byType}
# processed data already saved

load("~/Documents/research/generics/manuscript/model-results/asymmetry.Rdata")

## could substitute in the bootstrapped version of the human data

d.modeldatawPrev
d.asymSummary %>%
  rename(credHi = YMax,
         credLo = YMin) %>%
  mutate(task = factor(task, 
                       labels = c("Implied prevalence", 
                                  "Truth conditions")),
        src= 'Data',
        type = factor(type, labels = c("body parts", "vague parts",
                                    "color parts", "common accidental",
                                    "rare accidental"))) %>%
  rename(Task = task) %>%
  select(-CILow, -CIHigh)


ggplot(d.modeldatawPrev, 
       aes(x=MAPwithin, y = avePrev, color=type,group=Task, linetype=Task))+
  geom_point(position=position_dodge(.05), size=4)+
  geom_line(color='black',
            position=position_dodge(.05), alpha=1)+
  geom_errorbar(aes(ymin = credLow, ymax=credHigh), 
                width=0.03, size = 1,linetype=1,
                position=position_dodge(.05))+
  geom_abline(intercept = 0, slope = 100, linetype = 3)+
  #scale_alpha_manual(values= c(0.5, 1))+
  scale_linetype_manual(values=c(2,1))+
  scale_color_brewer(palette='Set1')+
  xlim(0.2,1)+
  ylim(20,100)+
  #xlab(expression(paste(italic("A priori"), " Mean conditional prevalence")))+
  xlab("Mean prevalence when present   ")+
  ylab("Assenting / Implied prevalence")+
  coord_fixed(0.01)+
  facet_wrap(~src)+
  guides(color=guide_legend(title="Property type"))



```


Barplot versions (earlier version)

```{r posterior.predictive.byType.barplot}
ggplot(d.modeldatawPrev, aes(x=type, y=avePrev, fill = type, alpha=Task))+
  geom_bar(position=position_dodge(0.9),width=0.9,
           color='black',stat='identity')+
  geom_errorbar(position=position_dodge(0.9),
                aes(ymin=credLow, ymax = credHigh),
                width=0.7,
                color='black',
                size = 0.8)+
  scale_alpha_manual(values=c(0.6,1))+
  #theme_black()+
  scale_fill_brewer(palette='Set1')+
  #scale_fill_brewer(palette='Set3')+
  facet_wrap(~src)+
  ylab("Average prevalence")+
  xlab("")+
  guides(fill=F, alpha=guide_legend("Task"))+
    theme(axis.text.x = element_text(angle = 45, hjust = 1,
                                   vjust=1))+
  theme(legend.position='bottom',
        legend.direction='horizontal')

```


### To recreate and reload saved data
Simulate subject-data from model predictions for truth conditions task
 
```{r posterior.predictive.simulateSubjects}

d.pp <- d.params %>% filter((Parameter%in%c('truth_conditions',
                                            'implied_prevalence')) & 
                (!(Item%in%c('speakerOptimality','phi'))))

d.tc <- d.pp %>% filter(Parameter=='truth_conditions')

d.bootstrap <- data.frame()

for (i in 1:1000){
  d.simulsamp <- data.frame()
  for (j in 1:40){
    d.subj<- d.tc %>% 
      group_by(Item, Prevalence) %>%
      sample_n(1) %>%
      mutate(Outcome = rbinom(1,1,Response)) %>%
      group_by(Item) %>%
      summarise(avePrev = avePrevScore(Outcome, Prevalence))
    d.simulsamp <- bind_rows(d.simulsamp, d.subj)
  }
  d.groupmean<-d.simulsamp %>% group_by(Item) %>%
    summarise(group_mean = mean(avePrev))
  
  d.bootstrap<- bind_rows(d.bootstrap, d.groupmean)
  if ((i %% 10)==0) { print(i) }
  #print(i) 
}
```



# Figure 5: Implied prevalence X truth conditions vs. Prior prevalence (model and data)

```{r}
d1<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-prior-incrmh100000a.csv")
d2<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-prior-incrmh100000b.csv")
d3<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-prior-incrmh100000c.csv")

samples = 50000
d.tidy<-bind_rows(d1,d2,d3)


d.params<-data.frame(Parameter = rep(d.tidy$Parameter, 
                               1+samples*d.tidy$Probability),
                     Item = rep(d.tidy$Item, 
                               1+samples*d.tidy$Probability),
                Prevalence = rep(d.tidy$Prevalence, 
                               1+samples*d.tidy$Probability),
                Response = rep(d.tidy$Value, 
                               1+samples*d.tidy$Probability))



d.summary<-d.params %>% group_by(Parameter,Item, Prevalence) %>%
  summarise(MAP = estimate_mode(Response),
            credHi = HPDhi(Response),
            credLo = HPDlo(Response))


d.sums<- d.summary %>% filter(Prevalence=='gamma')

d.between<-d.sums %>% filter(Item=='response0') %>% 
    ungroup() %>%
                     select(-Prevalence, -Item) %>%
                               rename(MAPbetween = MAP,
                                      credLoBetween = credLo,
                                      credHiBetween = credHi)
d.within<- d.sums %>% filter(Item=='response1') %>% 
  ungroup() %>%
                                          select(-Prevalence, -Item) %>%
                               rename(MAPwithin = MAP,
                                      credLoWithin = credLo,
                                      credHiWithin = credHi)

m.join<-left_join(d.between, d.within)

m.join$Property<-factor(m.join$Parameter, 
                        levels=c("part","vague", "color", "accidental_high", "accidental_low"),
                         labels = c("body parts", "vague parts",
                                    "color parts", "common accidental",
                                    "rare accidental"))

d.modeldatawPrev<-left_join(d.modeldata, 
                            m.join %>% select(Property, MAPwithin) %>% rename(type = Property) )
d.modeldatawPrev <- d.modeldatawPrev %>%
  rename(Task = task)

d.modeldatawPrev$src<-factor(d.modeldatawPrev$src, 
                             labels=c("Human data", "Model posterior predictive"))
#save(d.modeldatawPrev, file="~/Documents/research/generics/manuscript/model-results/asymmetry.Rdata")


load("~/Documents/research/generics/manuscript/model-results/asymmetry.Rdata")


ggplot(d.modeldatawPrev, 
       aes(x=MAPwithin, y = avePrev, color=type,group=Task, linetype=Task))+
  geom_point(position=position_dodge(.05), size=4)+
  geom_line(color='black',
            position=position_dodge(.05), alpha=1)+
  geom_errorbar(aes(ymin = credLow, ymax=credHigh), 
                width=0.03, size = 1,linetype=1,
                position=position_dodge(.05))+
  geom_abline(intercept = 0, slope = 100, linetype = 3)+
  #scale_alpha_manual(values= c(0.5, 1))+
  scale_linetype_manual(values=c(2,1))+
  scale_color_brewer(palette='Set1')+
  xlim(0.2,1)+
  ylim(20,100)+
  #xlab(expression(paste(italic("A priori"), " Mean conditional prevalence")))+
  xlab("Mean prevalence when present   ")+
  ylab("Assenting / Implied prevalence")+
  coord_fixed(0.01)+
  facet_wrap(~src)+
  guides(color=guide_legend(title="Property type"))

#ggsave(file=paste('~/Documents/research/generics/manuscript/figures/asym-lines-data-model-',paramsetups,'-',samples/1000,'kx3.pdf',sep=''), width=11, height = 6)


```



Money plot

```{r}

d.simulsubj.stats <- d.bootstrap %>%
  group_by(Item) %>%
  summarise(MAP = estimate_mode(group_mean),
            credLow = HPDlo(group_mean),
            credHigh = HPDhi(group_mean)) %>%
  rename(avePrev = MAP) %>%
  mutate(task = 'accept',
         src = 'model',
         type = Item) %>%
  select(-Item)


d.modelprev <- d.pp %>%  
                    filter(Parameter=='implied_prevalence') %>%
                    select(-Prevalence) %>%
              group_by(Item) %>%
              summarise(MAP = 100*estimate_mode(Response),
                      credLow = 100*HPDlo(Response),
                      credHigh = 100*HPDhi(Response)) %>%
              rename(type = Item,
                     avePrev = MAP)%>%
              mutate(src='model',
                     task='implied')


d.aveprev<-bind_rows(d.modelprev, d.simulsubj.stats)
d.modeldata<-bind_rows(d.aveprev, d.asymSummary)

d.modeldata$type<- with(d.modeldata%>% filter(task=='implied' & src=='data'),
                        reorder(type, avePrev, function(x) -x))


d.modeldata$type<-factor(d.modeldata$type, 
                         labels = c("body parts", "vague parts",
                                    "color parts", "common accidental",
                                    "rare accidental"))

d.modeldata$src<-factor(d.modeldata$src,labels =c("Data", "Model"))

d.modeldata$task<-factor(d.modeldata$task, labels=c("Truth conditions",
                                                    "Implied prevalence"))
load("~/Documents/research/generics/manuscript/model-results/asymmetry.Rdata")

ggplot(d.modeldatawPrev, aes(x=type, y=avePrev, fill = type, alpha=Task))+
  geom_bar(position=position_dodge(0.9),width=0.9,
           color='black',stat='identity')+
  geom_errorbar(position=position_dodge(0.9),
                aes(ymin=credLow, ymax = credHigh),
                width=0.7,
                color='black',
                size = 0.8)+
  scale_alpha_manual(values=c(0.6,1))+
  #theme_black()+
  scale_fill_brewer(palette='Set1')+
  #scale_fill_brewer(palette='Set3')+
  facet_wrap(~src)+
  ylab("Average prevalence")+
  xlab("")+
  guides(fill=F, alpha=guide_legend("Task"))+
    theme(axis.text.x = element_text(angle = 45, hjust = 1,
                                   vjust=1))+
  theme(legend.position='bottom',
        legend.direction='horizontal')

paramsetups<-'2phi-2so'
#ggsave(file=paste('~/Documents/research/generics/manuscript/figures/asym-data-model-',paramsetups,'-',samples/1000,'kx3.pdf',sep=''), width=11, height = 6)

#ggsave(file=paste('~/Box Sync/talks/esslli-2015-generics/figures/asym-data-model-',paramsetups,'-',samples/1000,'k.pdf',sep=''), width=11, height = 6)

d.modeldata<-d.modeldatawPrev
  
(with(d.modeldata %>% select(type, task, src, avePrev) %>% spread(src, avePrev),cor(Data, Model)))^2
(with(d.modeldata %>% select(type, Task, src, avePrev) %>% spread(src, avePrev),mse(Data/100, Model/100)))

(with(d.modeldata %>% filter(task=='Implied prevalence') %>% select(type, task, src, avePrev) %>% spread(src, avePrev),cor(Data, Model)))^2

```


Linear regression: Implied prevalence vs. A priori Within-prevalence
```{r}

d.reg<-left_join(d.implied, d.within %>% rename(type=Parameter))

rs<-lmer(response ~ MAPwithin + (1 + MAPwithin | workerid), d.reg)
summary(rs)
```
Linear regression: Implied prevalence > A priori Within-prevalence

```{r}
d.reg1<-d.reg %>%
  select(MAPwithin, response, stim_property, workerid)  %>%
  gather(key, val, -stim_property, -workerid)

rs1<-lmer(val ~  key + (1 | workerid) + (1 + key | stim_property), data=d.reg1)  

summary(rs1)

priorSD<-d.reg1 %>% filter(key=="MAPwithin") %>% summarise(sd(val))
posteriorSD<-d.reg1 %>% filter(key=="response") %>% summarise(sd(val))
pooled.sd <- sqrt((39*(priorSD^2) + 39*(posteriorSD^2))/78)

cohen.d <- 0.1725 / pooled.sd

```


```{r}
dmp.test<-dmp.items %>%
  select(Item, response, priorMAP)

summary(rs1)

```

```{r}


d.aveAccPrev <- d.accept %>%
  mutate(response = as.numeric(response==1)) %>%
  group_by(workerid, type) %>%
  summarise(prev = avePrevScore(response,stim_prevalence)) %>%
  mutate(src = "accept") 

d.reg.tc<-left_join(d.aveAccPrev, d.within %>% rename(type=Parameter))



rs.tc<-lmer(prev ~ MAPwithin+ (1 + MAPwithin | workerid), d.reg.tc)

summary(rs.tc)



d.reg.tc$workerid<- max(to.n(levels(factor(d.reg$workerid)))) + d.reg.tc$workerid

d.reg <- d.reg %>% select(workerid, type, response, MAPwithin, credHiWithin, credLoWithin) %>%
  rename(prev = response) %>%
  mutate(src = 'implied')

d.reg.joint<- bind_rows(d.reg, d.reg.tc)

rs.tc<-lmer(prev ~ MAPwithin*src - src + (1 + MAPwithin | workerid), d.reg.joint)

summary(rs.tc)
```


FBT on prior elicitation and asymmetry data. Posterior over parameters and posterior predictive.


```{r tfbt.2}
samples = 100000
paramsetups = "2opts-2phi"

d<-read.csv(paste("~/Documents/research/generics/manuscript/model-results/generics-asymmetry-prioriter10000_mh10000a.csv",sep=''))

d.params <- d %>% filter(!(Parameter%in%c("truth_conditions", 
                                          "implied_prevalence")))
# 
# d.params<-d.params %>% select(Parameter,Item, Prevalence) %>%
#   rename(Value = Item,
#          Probability = Prevalence) %>%
#   mutate(Value = to.n(Value))
# 

d.params <- data.frame(Parameter = rep(d.params$Parameter, 
                                       1+samples*d.params$Probability),
                       Response = rep(d.params$Value, 
                                      1+samples*d.params$Probability))

ggplot(d.params %>%filter(Parameter=='phi'), aes(x=Response))+
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01,
                 fill='grey89')+
  xlim(0,1)+
  xlab(expression(phi))+
  ylab("Posterior probability")+
  theme_black()



#ggsave(file=paste('~/Documents/research/generics/manuscript/figures/asym-lambdas-',paramsetups,'-',samples/1000,'k.pdf',sep=''))
#ggsave(file=paste('~/Box Sync/talks/esslli-2015-generics/figures/asym-lambdas-',paramsetups,'-',samples/1000,'k.pdf',sep=''))

#ggsave(file=paste('~/Documents/research/generics/manuscript/figures/asym-params-',paramsetups,'-',samples/1000,'k.pdf',sep=''))


quantile((d.params %>% filter(Parameter=='truthOptimality1'))$Response, 
         probs = c(0.025,0.975))

quantile((d.params %>% filter(Parameter=='impliedOptimality1'))$Response, 
         probs = c(0.025,0.975))

quantile((d.params %>% filter(Parameter=='truthOptimality2'))$Response, 
         probs = c(0.025,0.975))

quantile((d.params %>% filter(Parameter=='impliedOptimality2'))$Response, 
         probs = c(0.025,0.975))

quantile((d.params %>% filter(Parameter=='phi'))$Response, 
         probs = c(0.025,0.975))


d.tasks <- d %>% 
  filter(Parameter%in%c("truth_conditions", 
                                    "implied_prevalence"))

d.tasks <-  data.frame(Parameter = rep(d.tasks$Parameter, 
                                       1+samples*d.tasks$Probability),
                       Item = rep(d.tasks$Item, 
                                       1+samples*d.tasks$Probability),
                       Prevalence = rep(d.tasks$Prevalence, 
                                       1+samples*d.tasks$Probability),
                       Response = rep(d.tasks$Value, 
                                      1+samples*d.tasks$Probability))




d.pp <- d.tasks %>%
  group_by(Parameter,Item, Prevalence) %>%
  summarise(expectation = mean(Response),
            credLow = quantile(Response, probs=0.025),
            credHigh = quantile(Response, probs=0.975))

# truth conditions plot
ggplot(d.pp %>% filter(Parameter=='truth_conditions'),
       aes(x=Prevalence, y = expectation, color=Item))+
  geom_point(position=position_dodge())+
  geom_line(position=position_dodge())





# d.modeldata<-bind_rows(d.aveprev, d.asymSummary)
# 
# ggplot(d.modeldata, aes(x=type, y=avePrev, fill = task))+
#   geom_bar(position=position_dodge(), stat='identity')+
#   geom_errorbar(position=position_dodge(),
#                 aes(ymin=credLow, ymax = credHigh))+
#   facet_wrap(~src)
# 
# ggplot(d.modeldata %>% filter(type=='implied' & src=='model'),
#        aes(x=stim_type, y=avePrev, fill = stim_type))+
#   geom_bar(position=position_dodge(), stat='identity')+
#   geom_errorbar(position=position_dodge(),
#                 aes(ymin=credLow, ymax = credHigh))

```



Exploratory analysis for differences based on across-category prevalence

```{r}

# from asymmetry-priors.Rmd

d.accept<-left_join(d.accept, d.across %>% select(Parameter, splitHalf) %>% rename(stim_property = Parameter))


accept.summary <- d.accept %>%
  group_by(splitHalf, stim_prevalence) %>%
  summarise(prop = mean(response),
            n = length(response)) %>%
  mutate(sterr = sem.2AFC(prop,n))


ggplot(accept.summary,aes(x=factor(stim_prevalence), y= prop, 
                      group=splitHalf, color=splitHalf))+
  geom_point(position=position_dodge(0.3))+
  geom_line(position=position_dodge(0.3),size=1.5,linetype=2)+
  geom_errorbar(aes(ymin=prop-2*sterr,
                    ymax=prop+2*sterr),
                width=0.1, size=1.5,
                position=position_dodge(0.3))



```


Exploratory analysis of truth judgments vs. prevalence (and S2 model)

```{r truthJudge.byPrev}

# calculate proportion of "accepts" for each type and prevalence
accept.summary <- d.accept %>%
  group_by(stim_type, stim_prevalence) %>%
  summarise(prop = mean(response),
            n = length(response)) %>%
  mutate(sterr = sem.2AFC(prop,n))

ggplot(accept.summary,aes(x=factor(stim_prevalence), y= prop, 
                      group=stim_type, color=stim_type))+
  geom_point(position=position_dodge(0.3))+
  geom_line(position=position_dodge(0.3),size=1,linetype=2)+
  geom_errorbar(aes(ymin=prop-2*sterr,
                    ymax=prop+2*sterr),
                width=0.1, size=1,
                position=position_dodge(0.3))+
  ylim(0,1)



d.tj <- d.params %>% filter((Parameter%in%c('truth_conditions')) & 
                (!(Item%in%c('speakerOptimality','phi')))) %>%
  group_by(Item, Prevalence) %>%
  summarize(MAP = estimate_mode(Response),
            credHigh = HPDhi(Response),
            credLow = HPDlo(Response))


ggplot(d.tj, aes(x=Prevalence, y = MAP, group=Item, color=Item))+
    geom_point(position=position_dodge(0.3))+
  geom_line(position=position_dodge(0.3),size=1,linetype=2)+
  geom_errorbar(aes(ymin=credLow,
                    ymax=credHigh),
                width=0.1, size=1,
                position=position_dodge(0.3))+
  ylim(0,1)


```

Exploratory analysis of truth judgments by Item x Prevalence

```{r truthJudge.byItem.byPrev}

# calculate proportion of "accepts" for each type and prevalence
accept.summary <- d.accept %>%
  group_by(stim_property, stim_prevalence) %>%
  summarise(prop = mean(response),
            n = length(response)) %>%
  mutate(sterr = sem.2AFC(prop,n)) %>%
  rename(Item = stim_property, 
         Prevalence = stim_prevalence)


qplot(data=accept.summary,x=n, geom='histogram')+
  scale_x_continuous(breaks=seq(0,13,2))



d<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-truth-byItem-phi-priord50iter20000_mh20000b.csv")
samples = 1000
d.tidy <- d

d.params<-data.frame(Parameter = rep(d.tidy$Parameter, 
                               1+samples*d.tidy$Probability),
                     Item = rep(d.tidy$Item, 
                               1+samples*d.tidy$Probability),
                Prevalence = rep(d.tidy$Prevalence, 
                               1+samples*d.tidy$Probability),
                Response = rep(d.tidy$Value, 
                               1+samples*d.tidy$Probability))


d.summary<-d.params %>% group_by(Parameter,Item, Prevalence) %>%
  summarise(expectation = mean(Response),
              MAP = estimate_mode(Response),
            credHi = HPDhi(Response),
            credLo = HPDlo(Response)) %>%
  select(-Parameter)


tj.item.md<-left_join(accept.summary, d.summary)


ggplot(data=tj.item.md, aes(x=expectation, y=prop))+
  geom_point()+
  geom_errorbar(aes(ymin = prop-1.96*sterr, ymax = prop + 1.96*sterr), position=position_dodge())+
  geom_errorbarh(aes(xmin = credLo, xmax = credHi), position=position_dodge())



with(tj.item.md, cor(expectation, prop))


```

