---
title: "natural-judgments"
author: "mht"
date: "August 16, 2015"
output: html_document
---

Load prevalence estimates

```{r prev}
```{r}
m.path<-"~/Documents/research/generics/manuscript/model-results/"

samples = 50000
prefix<-'generics-naturalPrevalence-incrMH100000_burn50000' 
m1<-read.csv(paste(m.path, prefix, 'a.csv', sep=''))
m2<-read.csv(paste(m.path, prefix, 'b.csv', sep=''))
m3<-read.csv(paste(m.path, prefix, 'c.csv', sep=''))

m<-bind_rows(m1,m2,m3)

str(m)

m <- data.frame(Parameter =  rep(m$Parameter, 
                                   1+samples*m$Probability),
                Property =  rep(m$Property, 
                                   1+samples*m$Probability),
                Category =  rep(m$Category, 
                                   1+samples*m$Probability),
                Negation =  rep(m$Negation, 
                                   1+samples*m$Probability),
                Value = rep(m$Value, 
                                   1+samples*m$Probability))


m.summary<- m %>% filter(Negation == 'gamma') %>%
  group_by(Property, Category) %>%
  summarise(#expectation = mean(Value),
            #med = median(Value),
            map = estimate_mode(Value),
            credLow =HPDlo(Value),
            credHigh= HPDhi(Value)) %>%
  unite(sentence, Category, Property, sep =' ') %>%
  mutate(sentence = paste(sentence, '.', sep=''))


```



```{r tj1}

d.path <- "~/Documents/research/generics/data/real-kinds/"
tj <-read.csv(file = paste(d.path,'real-kinds-truth-1-trials.csv',sep=''))
c <- read.csv(file = paste(d.path,'real-kinds-truth-1-catch_trials.csv', sep=''))
s<- read.csv(file = paste(d.path,'real-kinds-truth-1-subject_information.csv', sep=''))
nonenglish<-c(1,4,19,38,39)
catch<-c[c$pass==0,]$workerid

tj <- tj %>% filter(!(workerid %in% c(nonenglish, catch)))

### bootstrap CI
bootstrap.ci <- function(x){
  agr = aggregate(response ~ sentence, data=x, FUN=mean)
  agr$CILow = aggregate(response ~ sentence, data=x, FUN=ci.low)$response
  agr$CIHigh = aggregate(response ~ sentence, data=x, FUN=ci.high)$response
  agr$YMin = agr$response - agr$CILow
  agr$YMax = agr$response + agr$CIHigh
  return(agr)
}


tj.bs<-bootstrap.ci(tj %>% mutate(response = as.numeric(response=='agree-key')))



tj.bs$sentence <- gsub('&quotechar','', tj.bs$sentence)
tj.bs$sentence <- gsub('lyme','Lyme', tj.bs$sentence)


tj.wPrev<-left_join(tj.bs %>% select(-CILow, -CIHigh), 
                    m.summary %>% rename(prev = map, 
                                         prevHigh = credHigh,
                                         prevLow = credLow), by = "sentence")

with(tj.wPrev, cor(response,prev))^2

write.csv(tj.wPrev, 
          file='~/Documents/research/generics/manuscript/model-results/natural-judgments-means.csv')

```

Bayesian model evaluation results

```{r fullBayesian.postparams}


estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}



m.path<-"~/Documents/research/generics/manuscript/model-results/"
samples =50000
previter = 50000
prioriter = 50000


m1<-read.csv(paste(m.path,"generics-truthJudgment-previter50000_prevprioriter50000-priord50Zero_mh100000_burn50000a.csv",sep=''))
m2<-read.csv(paste(m.path,"generics-truthJudgment-previter50000_prevprioriter50000-priord50Zero_mh100000_burn50000b.csv",sep=''))
m3<-read.csv(paste(m.path,"generics-truthJudgment-previter50000_prevprioriter50000-priord50Zero_mh100000_burn50000c.csv",sep=''))

m<- bind_rows(m1,m2,m3)

#m<-read.csv(paste(m.path,"generics-truthJudgment-previter50000_prevprioriter50000-priord50Zero_mh100000_burn50000a.csv",sep=''))

#m<-bind_rows(m1,m2)

m <- data.frame(Parameter =  rep(m$Parameter, 
                                   1+samples*m$Probability),
                Property =  rep(m$Property, 
                                   1+samples*m$Probability),
                Category =  rep(m$Category, 
                                   1+samples*m$Probability),
                Negation =  rep(m$Negation, 
                                   1+samples*m$Probability),
                Value = rep(m$Value, 
                                   1+samples*m$Probability))






m.prev <- m %>% 
  filter(Parameter == 'prevalence') %>%
  mutate(Negation = gsub(1," dont ", Negation),
         Negation = gsub(0," ", Negation)) %>%
  unite(Property1, Category, Negation, Property,sep='') %>%
  rename(Item = Property1)

ggplot(m.prev, aes(x=Value))+
  geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  facet_wrap(~Item, scales='free')+
  xlim(0,1)+
  xlab("Prevalence")+
  ylab("Posterior probability")
  





m.params<- m %>% filter(Parameter 
                        %in% c("speakerOptimality", "cost", "softmax","phi")
                        )

ggplot(m.params, aes(x=Value))+
  geom_histogram(aes(y=..count../sum(..count..)))+
  #geom_density(adjust=2)+
  facet_wrap(~Parameter, scales='free')+
  #xlim(0,10)+
  xlab("Speaker Optimality")+
  ylab("Posterior probability")


m.params %>% 
  group_by(Parameter) %>%
  summarise(postMode = estimate_mode(Value),
            credHi = HPDhi(Value),
            credLo = HPDlo(Value))

#ggsave(file='~/Box Sync/talks/esslli-2015-generics/posterior-rationality-truthJudge.pdf')


```

Scatter plot

```{r fullBayesian.pp}
  
m.pp<- m %>% filter(!((Parameter %in% 
                         c("speakerOptimality", "cost", "softmax", 'gamma',
                           'delta', "phi")) |
                        (substring(Parameter,1,10) == 'prevalence'))) %>%
    mutate(Negation = gsub(1," dont ", Negation),
         Negation = gsub(0," ", Negation)) %>%
    unite(sentence, Category, Negation, Property,sep='') %>%
  filter(Parameter == 'generic_linked')




m.pp.exp<- m.pp %>%
  group_by(sentence) %>%
  summarise(expectation = mean(Value),
            posMode = estimate_mode(Value),
            credHi = HPDhi(Value),
            credLo = HPDlo(Value)) %>%
  mutate(sentence = paste(sentence, '.', sep=''))


combined.model.data<- left_join(m.pp.exp, tj.wPrev, by='sentence')
combined.model.data$sentence<-with(combined.model.data, 
                                   reorder(sentence, response, function(x) -x))



qplot(data=combined.model.data,
      x=posMode,y=response,
      color=sentence)+
  geom_point(size=4)+
  geom_errorbar(aes(ymin=YMin, ymax=YMax),
                position=position_dodge(), size =1)+
  geom_errorbarh(aes(xmin = credLo, xmax=credHi),
                 position=position_dodge(), size = 1)+
  geom_abline(intercept=0,slope=1,linetype=2, size=1,color='black')+
  xlab("\n model posterior predictive")+
  ylab("proportion of agree's \n")+
  guides(color=F)+
  xlim(-0.05,1.05)+
  ylim(-0.05,1.05)+
  coord_fixed()

ggsave(file='~/Documents/research/generics/manuscript/figures/tj_n100_tjVsPostpred_95hdi.pdf', width=10, height=5)


with(combined.model.data, cor(posMode, response))^2

with(filter(combined.model.data,
            (prev > quantile(combined.model.data$prev)["25%"] & 
            prev < quantile(combined.model.data$prev)["75%"])), 
     cor(posMode,response))^2


with(combined.model.data, cor(posMode, response, method='spearman'))


# 
# qplot(data=combined.model.data,
#       x=prev,y=response,
#       color=sentence)+
#   geom_point(size=4)+
#   geom_errorbar(aes(ymin=YMin, ymax=YMax),
#                 position=position_dodge(), size =1)+
#   geom_errorbarh(aes(xmin = prevLow, xmax=prevHigh),
#                  position=position_dodge(), size = 1)+
#   geom_abline(intercept=0,slope=1,linetype=2, size=1,color='black')+
#   xlab("\n prevalence")+
#   ylab("proportion of agree's \n")+
#   guides(color=F)+
#   xlim(-0.05,1.05)+
#   ylim(-0.05,1.05)+
#   coord_fixed()
# 
# ggsave(file='~/Documents/research/generics/manuscript/figures/tj_n100_tjVsprev_95hdi.pdf', width=10, height=5)

with(combined.model.data, cor(prev, response))^2
with(filter(combined.model.data,
            (prev > quantile(combined.model.data$prev)["25%"] & 
            prev < quantile(combined.model.data$prev)["75%"])), 
     cor(prev,response))^2

with(combined.model.data, cor(prev, response, method='spearman'))


combined.model.data<- combined.model.data %>%
  mutate(dev = abs(expectation-response))


```

Bar plots


```{r}
cmd.tidy <- 
  bind_rows(
    combined.model.data %>% gather(src, value, posMode, response) %>%
          filter(src=='posMode') %>%
          select(sentence, credHi, credLo, src, value),
    combined.model.data %>% gather(src, value, posMode, response) %>%
          filter(src=='response') %>%
          select(sentence, YMin, YMax, src, value) %>%
          rename(credHi = YMax,
                 credLo = YMin))

cmd.tidy$sentence<-with(cmd.tidy %>% filter(src=='posMode'), 
                        reorder(sentence, value, function(x) x))

cmd.tidy<- cmd.tidy %>% rename(
  Source = src
  ) %>%
  mutate(Source = factor(Source, levels = c("response", 
                                            "posMode"),
                         labels = c("Human judgments",
                                    "Model predictions")))

ggplot(data=cmd.tidy, aes(x=sentence, y=value-0.5, 
                          fill = Source))+
  geom_bar(stat='identity',
           aes(x=sentence),
           position=position_dodge(1), width=1,
           color='black')+
  geom_errorbar(aes(x=sentence, fill = Source,
                    ymin=credLo-0.5,ymax=credHi-0.5), width=0.5, size = 1,
                color='black',
                position=position_dodge(1))+
  scale_fill_brewer(palette=3, type='qual')+
  #theme_blackDisplay()+
  #theme(axis.text.x = element_text(angle = 45, hjust = 1,
   #                                vjust=1))+
 # ylim(-.5,0.5)+
  xlab("")+
  ylab(" proportion endorsement")+
  scale_y_continuous(breaks=c(-0.5,0,0.5),labels=c("0","0.5","1"))+
  coord_flip()

ggsave(file="~/Documents/research/generics/manuscript/figures/tj_n100-postPred-byItem.pdf", width = 11, height = 7)


  ```


