---
title: "Prevalence priors for common features"
author: "Michael Henry Tessler"
date: "August 12, 2015"
output: html_document
---


```{r helpers}
library(coda)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}


roundToMixture <- function(x){
  return (if (x==0) {
    0
  } else if (x<=5) {
    0.01
  } else if (x>=95) {
    0.99
  } else {
    round(x/10)/10
  } )
}

```

# Check posterior predictive of prior (mixture) model

There are different ways of formualting the prior BDA model that correspond to:

1. 2 factors (first: Is present? second: What %?) vs. 1 factor (just mixture)
2. Treating the data as continuous (from a Beta) or discretized (discretized Beta)


All three produce the same results (R2 = 0.95)

```{r posteriorPredictiveCheck}
m.path<-"~/Documents/research/generics/manuscript/model-results/"

samples = 50000

# single factor, continuous factor
prefix<-'generics-naturalPriors-singleFactor-postPred-n57-continuous-incrMH100000_burn50000a.csv' 
# two factors, discretized factor
prefix<-"generics-naturalPriors-postPred-n57-incrMH50000_burn25000c.csv"
# single factor, discretized factor
prefix<-"generics-naturalPriors-singleFactor-postPred-n57-incrMH50000_burn25000c.csv"

m<-read.csv(paste(m.path, prefix, sep=''))

str(m)

m <- data.frame(Parameter =  rep(m$Parameter, 
                                   1+samples*m$Probability),
                Bin =  rep(m$Category, 
                                   1+samples*m$Probability),                
                Property =  rep(m$Property, 
                                   1+samples*m$Probability),
                Negation =  rep(m$Negation, 
                                   1+samples*m$Probability),
                Value = rep(m$Value, 
                                   1+samples*m$Probability))

m.params <- m %>% filter(Negation!='posteriorPredictive') %>%
  group_by(Property,Negation) %>%
  summarise(MAP = estimate_mode(Value),
            credHigh = HPDhi(Value),
            credLow = HPDlo(Value),
            expectation = mean(Value)) 

m.pp <- m %>% filter(Negation=='posteriorPredictive') %>%
  group_by(Bin, Property) %>%
  summarise(MAP = estimate_mode(Value),
            credHigh = HPDhi(Value),
            credLow = HPDlo(Value),
            expectation = mean(Value)) %>%
  ungroup() %>%
  mutate(Bin = to.n(Bin))


# read human data
d<- read.csv("~/Documents/research/generics/manuscript/data/naturalGenerics-prior-trials-n57.csv")


d.properties <- d %>%
  rowwise() %>%
  mutate(Bin = roundToMixture(prevalence)) %>%
  ungroup() %>%
  group_by(Property, Bin) %>%
  summarize(count = length(trial_type)) %>%
  ungroup() %>%
  group_by(Property) %>%
  mutate(norm_count = count / sum(count))

prior.md<-left_join(m.pp, d.properties)
prior.md[is.na(prior.md$norm_count),]$norm_count <- 0

prior.md <- prior.md %>%
  mutate(Bin = factor(Bin))


ggplot(prior.md, aes(x=MAP, y = norm_count, color=Bin))+
  geom_point()+
  geom_abline(intercept =0, slope=1,linetype=2)+
  geom_errorbarh(aes(xmin=credLow, xmax=credHigh), position=position_dodge())+
  xlab("Posterior predictive of prior model")+
  ylab("Normalized counts of human responses")+
  coord_fixed()

#ggsave(file='~/Documents/research/generics/manuscript/figures/postPred-priorModel.pdf')

with(prior.md, cor(MAP, norm_count))^2

# Check outliers
View(prior.md %>% filter(norm_count < .2 & MAP > .18))
```




# Load BDA results

These use 2 factors, discretized (see above)

```{r load.model}
m.path<-"~/Documents/research/generics/manuscript/model-results/"

samples = 50000
prefix<-'generics-naturalPriors-n57-incrMH100000_burn50000' 
m1<-read.csv(paste(m.path, prefix, 'a.csv', sep=''))
m2<-read.csv(paste(m.path, prefix, 'b.csv', sep=''))
m3<-read.csv(paste(m.path, prefix, 'c.csv', sep=''))

m<-bind_rows(m1,m2,m3)
#m<-read.csv(paste(m.path, prefix, 'c.csv', sep=''))

str(m)

# Reconstruct samples from webppl histogram

m <- data.frame(Parameter =  rep(m$Parameter, 
                                   1+samples*m$Probability),
                Property =  rep(m$Property, 
                                   1+samples*m$Probability),
                Negation =  rep(m$Negation, 
                                   1+samples*m$Probability),
                Value = rep(m$Value, 
                                   1+samples*m$Probability))

```


## Posteriors on parameters

The BDA model assumes participants' responses are sampled from a mixture of categories that don't have the property (prevalence = 0%) and categories that do. The mean of the distribution governing those that do have the property is gamma. The concentration of that distribution is delta.

The parameter prob_hasF is the mixture parameter governing the property's potential to be present in a kind.

```{r posterior.parameters}
m.prev <- filter(m, Negation=='gamma')

plt1<-ggplot(m.prev, aes(x=Value))+
  #geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  geom_histogram(aes(y=..count../sum(..count..)))+
  facet_wrap(~Property, scales='free')+
  xlim(0,1)+
  xlab("Gamma")+
  ylab("Posterior probability")

#ggsave(plt1,file='~/Documents/research/generics/manuscript/figures/diagnostics/naturalPriors-gammas-allChains.pdf', width = 15, height=15)


m.prev <- filter(m, Negation=='delta')

plt2<-ggplot(m.prev, aes(x=Value))+
  #geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  geom_histogram(aes(y=..count../sum(..count..)))+
  facet_wrap(~Property, scales='free')+
  #xlim(0,50)+
  xlab("Delta")+
  ylab("Posterior probability")

# delta.summary<-m.prev %>% 
#   group_by(Property) %>%
#   summarise(map = estimate_mode(Value), 
#             credHi = HPDhi(Value),
#             credLo = HPDlo(Value))

#ggsave(plt2,file='~/Documents/research/generics/manuscript/figures/diagnostics/naturalPriors-deltas-allChains.pdf', width = 15, height=15)


m.prev <- filter(m, Negation=='prob_hasF')

plt3<-ggplot(m.prev, aes(x=Value))+
  #geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  geom_histogram(aes(y=..count../sum(..count..)))+
  facet_wrap(~Property, scales='free')+
  xlim(0,1)+
  xlab("Thetas")+
  ylab("Posterior probability")

#ggsave(plt3,file='~/Documents/research/generics/manuscript/figures/diagnostics/naturalPriors-thetas-allChains.pdf', width = 15, height=15)


```


## Posterior predictive (the cheap way)

Reconstruct prevalence prior by forward sampling

```{r posterior.predictive.forwardSample}


shape1 = function(gamma,delta){return (gamma * delta)}
shape2= function(gamma,delta){return ((1-gamma) * delta)}

d.params <- m %>% filter(!(Negation=='phi')) %>%
  select(-Parameter) %>%
  rename(Parameter=Negation)


d.samples<-data.frame()


for (i in 1:100){

  d.samp<-d.params %>%
    group_by(Property, Parameter) %>%
    sample_n(1) %>%
    ungroup() %>%
    spread(Parameter, Value) %>%
    mutate(alpha = shape1(gamma,delta),
           beta = shape2(gamma, delta)) %>%
    group_by(Property) %>%
    mutate(doesHaveF = rbinom(1,1,prob_hasF)) %>%
    select(-gamma, -delta)

  
  for (k in 1:length(d.samp$Property)){
    d.iter<-data.frame(
               Pairing = d.samp[k,1],
               
               Prevalence = if (d.samp[[k,"doesHaveF"]]==1){
                                rbeta(50, d.samp[[k, "alpha"]], 
                                          d.samp[[k, "beta"]]
                                    )
                                } else {rep(0,50)}
               )
    d.samples<-bind_rows(d.samples, d.iter)
  }
  
  if ((i %% 10)==0) { print(i) }
}

```



# Figure 1: Scatterplot -- Theta vs. Gamma

```{r fig1.scatter}

m.stats<- m %>% 
#  filter(Negation != 'delta') %>%
  group_by(Property, Negation) %>%
  summarise(MAP = estimate_mode(Value),
            credHigh = HPDhi(Value),
            credLow = HPDlo(Value))


m.spread<- m.stats %>%
  gather(key, val, MAP, credHigh, credLow) %>%
  spread(Negation, val)

m.join<- left_join(left_join(m.spread %>% 
                               filter(key=='MAP') %>% 
                               select(-key),
                   m.spread %>% 
                     filter(key=='credHigh') %>% 
                     select(-key) %>%
                     rename(credHigh_within = gamma,
                            credHigh_varianceWithin = delta,
                            credHigh_across = prob_hasF)),
                   m.spread %>% filter(key=='credLow') %>% select(-key) %>%
                     rename(credLow_within = gamma,
                            credLow_varianceWithin = delta,
                            credLow_across = prob_hasF))


# Distribution over concentration parameters
qplot(x=delta, geom='histogram',data= m.join, binwidth =0.5)



# Scatterplot
ggplot(m.join, aes(x = gamma, y = prob_hasF, label=Property))+
   geom_point(size =2.5, color='black')+
   geom_errorbar(aes(ymin = credLow_across, ymax = credHigh_across),
                                 position=position_dodge(), size =1,
                 color='black')+
   geom_errorbarh(aes(xmin = credLow_within, xmax = credHigh_within),                 
                  position=position_dodge(), size =1,
                  color='black')+
  xlim(-0.05,1.05)+
  ylim(-0.05,1.05)+
  coord_fixed()+
  xlab(expression(gamma))+
  ylab(expression(theta))
#  xlab("Mean prevalence when present")+
#  ylab("Property's potential to be present in a kind")


#ggsave(file='~/Documents/research/generics/manuscript/figures/prevalences-scatter-2.pdf', width=12, height=6)
```


## Figure 1: Insets


### Add L_1 posteriors to prevalene prior plots

```{r fig1.insets}

prefix<-'generics-truthJudgment-wState-previter10000_prevprioriter10000-priord50Zero-n57_mh10000_burn5000'
#prefix<-'generics-truthJudgment-wTheta-previter50000_prevprioriter50000-priord50Zero-n57_mh100000_burn50000'

t<-as.data.frame(fread(paste(m.path, prefix, 'c.csv', sep='')))


t.tidy <- t %>%
  filter(Parameter=='statePosterior') %>%
  #filter(Parameter=='thetaPosterior') %>%
  select(-Negation, -Parameter) %>%
  rename(bin = Category)


t.dy <- data.frame(
                Property =  rep(t.tidy$Property, 
                                   1+samples*t.tidy$Probability),
                bin =  rep(t.tidy$bin,
                                   1+samples*t.tidy$Probability),
                Value = rep(t.tidy$Value, 
                                   1+samples*t.tidy$Probability))

t.stats<- t.dy %>%
  group_by(Property, bin) %>%
  summarize(MAP = estimate_mode(Value),
            credLow = HPDlo(Value),
            credHigh = HPDhi(Value)) %>%
    mutate(bin = to.n(bin)) %>%
  group_by(Property) %>%
  mutate(cdf = cumsum(MAP)) %>%
  mutate(cdfLow = cdf - (MAP-credLow),
         cdfHigh = cdf + (credHigh - MAP)) 
  

t.interp<- data.frame()
for (p in levels(t.stats$Property)){
  mh = data.frame(with(t.stats 
                       %>% filter(Property==p), 
                       approx(x=bin, y = MAP, n = 100)))
  mh$Property  = p
  t.interp<- bind_rows(t.interp, mh)  
}


t.dy <- data.frame(
                Property =  rep(t.interp$Property, 
                                   1+samples*t.interp$y),
                Prevalence = rep(t.interp$x,
                                   1+samples*t.interp$y))


t.dy$src= "Posterior prevalence"
d.samples$src<- "Prior prevalence"

d.sty <- bind_rows(t.dy, d.samples)

target<- c("are female", "lay eggs", 
           "carry malaria", "have wings",
           "dont attack swimmers")

d.sty$src<-factor(d.sty$src, 
                  levels=c("Prior prevalence", 
                           "Posterior prevalence"))

load(file='~/Documents/research/generics/manuscript/data/naturalkinds-withinK-prevalence.Rdata')

m.prevTargets <- m.summary %>%
  filter(Category%in%c("Robins", "Mosquitos", 
                       "Ducks", "Sharks") )

m.prevTargets <- m.prevTargets[c(1,5,7, 10,11),]

for (ti in target){
#  ggplot(d.samples %>% filter(Property == t), 
#          aes(x=Prevalence))+
#    ggplot(d.sty%>% filter(Property == ti), 
#           aes(x=Prevalence, linetype=src, color=src, alpha=src))+
#       geom_density(aes(y=..scaled..), size=1, color ='black',fill='black')+
#        scale_color_manual(values=c("#bdbdbd","#f0f0f0"))+
#   scale_alpha_manual(values=c(0.6,0.1))+
#     #geom_density(size=1, alpha=0.7)+
#      geom_errorbarh(data = m.prevTargets %>% filter(Property==ti),
#                     aes(x= map, xmin = credLow, xmax = credHigh,
#                     y = 1.05), color='#2ca25f', size = 1.1,
#                     height = 0.1, inherit.aes=F)+
#   scale_linetype_manual(values=c(1,2))+
#   xlab("Prevalence")+
#   guides(fill=F, color=F, alpha=F, linetype=F)+
#   facet_wrap(~Property, scales='free')+
#   scale_x_continuous(limits=c(0,1), breaks=c(0,0.5,1))+
#   scale_y_continuous(limits=c(0,1.1), breaks=c(0,0.5,1))+
#   ylab("Scaled density")+
#   theme(strip.text.x=element_text(size=16))+
#   coord_fixed()
#     

#ggsave(file=paste('~/Documents/research/generics/manuscript/figures/truthjudge-prevalences-priors-posteriors-wTarget-',t,'.pdf',sep=''), 
#       width=5, height=3.5)

  
# black theme

ggplot(d.sty%>% filter(Property == ti), 
          aes(x=Prevalence, linetype=src, color=src, alpha=src, fill=src))+
  geom_density(aes(y=..scaled..), size=1, color ='white')+
  #scale_color_manual(values=c("#bdbdbd","#f0f0f0"))+
  scale_fill_manual(values = c("#ffffb3","#8dd3c7"))+
  scale_alpha_manual(values=c(0.9,0.6))+
  geom_errorbarh(data = m.prevTargets %>% filter(Property==ti),
                    aes(x= map, xmin = credLow, xmax = credHigh,
                    y = 1.05), color='#bebada', size = 1.1,
                    height = 0.1, inherit.aes=F)+
  scale_linetype_manual(values=c(1,2))+
  xlab("Prevalence")+
  guides(alpha=F, color=F)+
  facet_wrap(~Property, scales='free')+
  scale_x_continuous(limits=c(0,1), breaks=c(0,0.5,1))+
  scale_y_continuous(limits=c(0,1.1), breaks=c(0,0.5,1))+
  ylab("Scaled density")+
  theme_black()+
  theme(strip.text.x=element_text(size=16))+
  coord_fixed()
    
  
  
  
  
  
ggsave(file=paste('~/Documents/research/habituals/talks/frisem-2016-generics/figures/truthjudge-prevalences-priors-posterior-wTarget-',ti,'.pdf',sep=''), 
       width=5, height=3.5)
  
print(ti)

}
```