---
title: "Prevalence of common features for familiar categories"
author: "Michael Henry Tessler"
date: "August 11, 2015"
output: html_document
---


```{r helpers}
library(coda)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```


# Load BDA results

```{r}
m.path<-"~/Documents/research/generics/manuscript/model-results/"

samples = 150000
prefix<-'generics-naturalPrevalence-n57-incrMH100000_burn50000' 
m1<-read.csv(paste(m.path, prefix, 'a.csv', sep=''))
m2<-read.csv(paste(m.path, prefix, 'b.csv', sep=''))
m3<-read.csv(paste(m.path, prefix, 'c.csv', sep=''))

m<-read.csv(paste(m.path,'generics-naturalPrevalence-continuousFactoring-n57-incrMH10000_burn5000.csv', sep=''))

m<-read.csv(paste(m.path,'generics-naturalPrevalence-continuousFactoring-n57-HMC100_burn50_step5stepSize0.0015.csv', sep=''))

m<-bind_rows(m1,m2,m3)

str(m)

# Reconstruct samples from webppl histogram

m <- data.frame(Parameter =  rep(m$Parameter, 
                                   1+samples*m$Probability),
                Property =  rep(m$Property, 
                                   1+samples*m$Probability),
                Category =  rep(m$Category, 
                                   1+samples*m$Probability),
                Negation =  rep(m$Negation, 
                                   1+samples*m$Probability),
                Value = rep(m$Value, 
                                   1+samples*m$Probability))


# Get credible intervals for prevalence, for each property and category
# e.g. (% of birds, lions that lay eggs, have manes)

m.summary<- m %>% 
  filter(Negation == 'gamma') %>%
  group_by(Property, Category) %>%
  summarise(#expectation = mean(Value),
            #med = median(Value),
            map = estimate_mode(Value),
            credLow =HPDlo(Value),
            credHigh= HPDhi(Value))

#save(m.summary, file='~/Documents/research/generics/manuscript/data/naturalkinds-withinK-prevalence.Rdata')

# write.csv(m.summary, 
#            file='~/Documents/research/generics/manuscript/model-results/natural-prevalence-intervals-n57.csv')
```


Check correspondence with BDA results using n = 60 (3 subjects did the experiment twice)

```{r}
# check correspondence with n=60 measures
m.sum<- read.csv('~/Documents/research/generics/manuscript/model-results/natural-prevalence-intervals.csv')


m.sum <- m.sum %>% 
  select(-credLow, -credHigh) %>%
  rename(map2 = map)

m.sum2<- left_join(m.summary, m.sum)

with(m.sum2, cor(map2, map))
```


## Posteriors on parameters


The BDA model assumes participants judgments for the % of K that have F are sampled from a Beta distribution, with unknown mean and concentration.

We take the posterior over the mean (gamma) to be the distribution of participants beliefs about the prevalence of F within K. 

### Gamma, mean of Beta distribution

This is the mean of participants' beliefs about the prevalence of F within K (e.g. % of birds that lay eggs)

```{r posterior.params.gamma}
# ggplot(m.phi, aes(x=Value))+
#   geom_histogram()+
#   xlim(0,1)

m.prev <- filter(m, Negation=='gamma') %>%
  unite(Pairing, Property, Category) 

ggplot(m.prev, aes(x=Value))+
  #geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  geom_histogram(aes(y=..count../sum(..count..)))+
  facet_wrap(~Pairing, scales='free')+
  #xlim(0,1)+
  xlab("Prevalence")+
  ylab("Posterior probability")+
  ggtitle("Distribution on gamma")+
  theme_bw()

#ggsave(plt1,file='~/Documents/research/generics/manuscript/figures/diagnostics/naturalPrevalence-gammas-allChains.pdf', width = 15, height=15)

```

### Delta, concentration of Beta distribution

This is corresponds to the concentration (or roughly precision, inverse variance) of participants' beliefs about the prevalence of F within K (e.g. % of birds that lay eggs)



```{r posterior.params.delta}
delta.summary<- m %>% filter(Negation == 'delta') %>%
  group_by(Property, Category) %>%
  summarise(#expectation = mean(Value),
            #med = median(Value),
            map = estimate_mode(Value),
            credLow =HPDlo(Value),
            credHigh= HPDhi(Value))

m.prev <- filter(m, Negation=='delta') %>%
  unite(Pairing, Property, Category) 



ggplot(m.prev, aes(x=Value))+
  #geom_histogram(binwidth=0.01,aes(y=..count../sum(..count..)))+
  geom_histogram(aes(y=..count../sum(..count..)), binwidth = 0.3)+
  facet_wrap(~Property, scales='free')+
  xlim(0,50)+
  xlab("Delta")+
  ylab("Posterior probability")+
  ggitlte("Distributions on delta"_)

# delta.summary<-m.prev %>% 
#   group_by(Property) %>%
#   summarise(map = estimate_mode(Value), 
#             credHi = HPDhi(Value),
#             credLo = HPDlo(Value))

#ggsave(plt2,file='~/Documents/research/generics/manuscript/figures/diagnostics/naturalPrevalence-deltas-chain1.pdf', width = 15, height=15)

```


## Posterior predictive (the cheap way)

Reconstruct prevalence prior by forward sampling

```{r}

d.samples<-data.frame()

shape1 = function(gamma,delta){return (gamma * delta)}
shape2= function(gamma,delta){return ((1-gamma) * delta)}


m.params<-m1 %>% unite(Pairing, Category, Property)

for (i in 1:100){

  d.samp<-m.params %>%
    group_by(Pairing,Negation) %>%
    sample_n(1) %>%
    ungroup() %>%
    spread(Negation, Value) %>%
    mutate(alpha = shape1(gamma,delta),
           beta = shape2(gamma, delta))
  
  for (k in 1:length(d.samp$Pairing)){
    d.iter<-data.frame(
               Pairing = d.samp[k,1],
               Prevalence = rbeta(100, d.samp[[k, "alpha"]], 
                                       d.samp[[k, "beta"]]
                                  )
               )
    d.samples<-bind_rows(d.samples, d.iter)
  }
  
  if ((i %% 10)==0) { print(i) }

}

ggplot(d.samples, aes(x=Prevalence))+
  geom_histogram()+
  facet_wrap(~Pairing, scales='free')+
  xlim(0,1)

```
