---
title: "cogsci15-generics"
author: "mht"
date: "February 3, 2015"
output: html_document
---

```{r helpers}
library(diptest)
discretize_beta<- function(gamma,delta,bins = c(0.01,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,0.99)) {
  s_alpha<- gamma*delta
  s_beta <- (1 - gamma) * delta
  beta_pdf<- function(x){
    return((x^(s_alpha-1))*((1-x)^(s_beta-1)))
  }
  return(sapply(bins,beta_pdf))
}



bool.tonum<-function(bool){abs(as.numeric(bool)*1-2)}

bootstrap.ci.ip <- function(x){
  agr = aggregate(imp_subj ~ context, data=x, FUN=mean)
  agr$CILow = aggregate(imp_subj ~ context, data=x, FUN=ci.low)$imp_subj
  agr$CIHigh = aggregate(imp_subj ~ context, data=x, FUN=ci.high)$imp_subj
  agr$YMin = agr$imp_subj - agr$CILow
  agr$YMax = agr$imp_subj + agr$CIHigh
  return(agr)
}

bootstrap.ci.tc <- function(x){
  
  agr = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=mean)
  agr$CILow = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.low)$truth_num
  agr$CIHigh = aggregate(truth_num ~ stim_prevalence + stim_determiner + stim_type, data=x, FUN=ci.high)$truth_num
  agr$YMin = agr$truth_num - agr$CILow
  agr$YMax = agr$truth_num + agr$CIHigh
  return(agr)
}

bootstrap.ci.prior <- function(x){
  agr = aggregate(value ~ context, data=x, FUN=mean)
  agr$CILow = aggregate(value ~ context, data=x, FUN=ci.low)$value
  agr$CIHigh = aggregate(value ~ context, data=x, FUN=ci.high)$value
  agr$YMin = agr$value - agr$CILow
  agr$YMax = agr$value + agr$CIHigh
  return(agr)
}


g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}


simulate_subject<- function(dstats){
  prevlev<-c(10,10,30,30,50,50,70,70,90,90)
  dd.resp = c(rbinom(2,1,dstats[1,"mean"]),
             rbinom(2,1,dstats[2,"mean"]),
              rbinom(2,1,dstats[3,"mean"]),
              rbinom(2,1,dstats[4,"mean"]),
              rbinom(2,1,dstats[5,"mean"]))
  dd.ave <- sum(dd.resp*prevlev)/sum(dd.resp)
  
  ni.resp = c(rbinom(2,1,dstats[6,"mean"]),
             rbinom(2,1,dstats[7,"mean"]),
              rbinom(2,1,dstats[8,"mean"]),
              rbinom(2,1,dstats[9,"mean"]),
              rbinom(2,1,dstats[10,"mean"]))
  ni.ave <- sum(ni.resp*prevlev)/sum(ni.resp)
  
  pl.resp = c(rbinom(2,1,dstats[11,"mean"]),
             rbinom(2,1,dstats[12,"mean"]),
              rbinom(2,1,dstats[13,"mean"]),
              rbinom(2,1,dstats[14,"mean"]),
              rbinom(2,1,dstats[15,"mean"]))
  pl.ave <- sum(pl.resp*prevlev)/sum(pl.resp)
  return(c(dd.ave,ni.ave,pl.ave))
}

# for truth_conditions --> average_prevalence transform
# if subject says "False" to everything, her average prevalence = 100
# else, it is the mean of the the things she said "True" to
check.zero <- function(prev,val){
  if (sum(val)==0){
    v = 100
  } else {
    v = sum(prev*val)/sum(val)
  }
  return(v)
}

```

# Experiment 1: CBG Replication


## 1a stats

```{r 1a.stats}
setwd("~/Documents/research/generics/cbg2010-replication/data")
d<-read.table('cbgR-exp9-trials.tsv',header=T)

d$item <- paste(d$stim_color,d$stim_part,sep="_")
d$rt <- d$rt/1000
d$truth_conditions <- factor(as.logical(levels(d$response)[d$response]), 
                              levels=c("TRUE","FALSE"))
d$truth_num <- bool.tonum(d$truth_conditions)
d$prev_centered <- scale(d$stim_prevalence, scale=F)

#contrasts(d$stim_type) = cbind(quad = c(-1,2,-1), lin = c(-1, 0, 1))
#contrasts(d$stim_type) = cbind(dd = c(0,1,0), ni = c(0, 0, 1))

rs<-glmer(truth_num ~ prev_centered*stim_type + 
            (1 | workerid) + 
            (1 | item), 
          data=d, family = 'binomial')

summary(rs)
```

## 1b stats

```{r 1b.stats}
setwd("~/Documents/research/generics/cbg2010-replication/data/")
f<-read.table('cbgR-exp12-trials.tsv',header=T)
f$item <- paste(f$stim_color,f$stim_part,sep="_")
table(f$stim_type,f$item)
table(f$stim_type,f$stim_part)

f.tidy <- f %>%
  select(workerid,rt,stim_type,response)%>%
  rename(context=stim_type)

f.stats<-ddply(f.tidy, 
       .(workerid,context), summarise, 
       imp_subj = mean(response),
       context=context[1])
f.stats$task<-'implied'


d.tidy <- d %>%
  select(workerid,rt,stim_type,stim_prevalence,truth_num)%>%
  rename(context=stim_type,
         prevalence=stim_prevalence,
         response=truth_num)

d.stats<-ddply(d.tidy,
      .(workerid,context), summarise,
      imp_subj = sum(prevalence*response)/sum(response),
      context=context[1])
d.stats$workerid <- d.stats$workerid+30
d.stats$task<-'truth'


both.stats<-rbind(f.stats,d.stats)
contrasts(both.stats$context)
both.stats$task<-factor(both.stats$task)
contrasts(both.stats$task)
rs<-lmer(imp_subj ~ context * task + (1 | workerid), data=both.stats)
summary(rs)

```

## Figure 1a

```{r fig1a}
tc.bs<-bootstrap.ci.tc(d)

tc.bs$context<-factor(tc.bs$stim_type,
                        levels=c('danger-distinct','nondistinctive','bare'),
                        labels=c("distinctive & dangerous", 
                                 "nondistinctive & nondangerous",
                                 "plain"))

ggplot(tc.bs, aes(x=stim_prevalence,y=truth_num,
                  colour=context, group=context))+
  geom_point(size=3, position=position_dodge(5))+
  geom_line(size=2,position=position_dodge(5))+
  geom_errorbar(aes(ymin=YMin,ymax=YMax,colour=context),
              width=5,
              size=2,
              position=position_dodge(5))+
  scale_colour_brewer(type='qual',palette='Pastel1')+
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(10,30,50,70,90),limits=c(0,100))+
  theme_blackDisplay()+ 
  guides(color=guide_legend(title="Context"))+
  xlab("\n % of kind with feature")+
  ylab('proportion "true"\n')+
  coord_fixed(100)+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)

ggsave('../../semfest-2015/figures/exp1_cbg-replication.png',width=15, height=10)
```

## Figure 1b

```{r fig1b}
f.bs<-bootstrap.ci.ip(f.stats)
f.bs$task<-'impliedprevalence'
d.bs<-bootstrap.ci.ip(d.stats)
d.bs$task<-'truthconditions'

m<-rbind(f.bs,d.bs)

# m$context<-factor(m$context,
#                   levels=c('danger-distinct','nondistinctive','bare'),
#                   labels=c("dangerous \n& distinctive", 
#                            "nondistinctive \n& irrelevant",
#                            "plain"))
m$task <- factor(m$task,
                 levels=c("truthconditions","impliedprevalence"),
                 labels=c("truth conditions", "implied prevalence"))

m$context<-factor(m$context,
                  levels=c('danger-distinct','nondistinctive','bare'),
                  labels=c("distinctive & dangerous", 
                                 "nondistinctive & nondangerous",
                                 "plain"))


fig1b<-ggplot(m, aes(x=context,y=imp_subj,fill=context,alpha=task, group=task))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5,color='black')+
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=0.2,
                size=2,
                color='white',
                position=position_dodge(0.5))+
  theme_blackDisplay()+
  ylab("average prevalence")+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  scale_alpha_manual(values=c(0.4,1))+
  xlab("")+
  theme(#legend.position='bottom',
        #legend.direction='horizontal',
        #legend.box = 'horizontal',
        #axis.text.x=element_blank()
        )+
  guides(fill = F,#guide_legend(order = 1), 
          alpha = guide_legend(order = 2))


ggsave(plot=fig1b,'../../semfest-2015/figures/exp1b_cbg-replication.png',width=25, height=10)



mylegend<-g_legend(fig1b)

p3 <- arrangeGrob(arrangeGrob(fig1a + theme(legend.position="none"),
                         fig1b + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))

#p3

# ggsave(filename=paste(plotpath,'Xexp1data.png',sep=''),
#        plot=p3,
#        width=14,
#        height=6,
#        dpi=150)

```


# Figure 2: Fixed threshold semantics


```{r fig2.ft}

setwd("~/Documents/research/generics/cbg2010-replication/models/bayesian_analysis")

d<-read.csv('ft_conditionTC_cnts_expts9_12_generic_mh1000_10_alpha1.csv',header=F)
f<-read.csv('ft_conditionIP_cnts_expts9_12_generic_mh1000_10_alpha1.csv',header=F)


ft.phi <- d %>% select(V1) %>% rename(phi_tc=V1)
ft.phi2 <- f %>% select(V2) %>% rename(phi_ip=V2)
ft.phi<-cbind(ft.phi,ft.phi2)

phi.tidy <- ft.phi %>%
  gather(variable,value) %>%
  separate(variable, into=c('parameter','task'), by='_')

phi.tidy$task<-factor(phi.tidy$task,
                    levels=c('tc','ip'),
                    labels=c("truth conditions","implied prevalence"))

a<-ggplot(phi.tidy,aes(x=value,alpha=task))+
  geom_density(fill='black')+
  theme_paper()+
  scale_alpha_manual(values=c(0.4,1))+
  scale_x_continuous(breaks=c(0,0.25,.5,0.75,1),limits=c(0,1))+
  scale_fill_brewer(type='qual',palette=1)+
  theme(strip.text.x = element_text(size=14,color='black'),
        legend.position='bottom',
        legend.direction='horizontal',
        axis.title.x =element_text(vjust = -0.5,size=30))+
  guides(fill=guide_legend(title="Context"))+
  xlab(expression(phi))+
  ylab("posterior density")

d.tidy <- d %>%
  select(V3,V4,V5) %>%
  rename(dd_tc = V3,
         ni_tc = V4,
         pl_tc = V5) %>%
  gather(variable,value)

f.tidy <- f %>%
  select(V3,V4,V5) %>%
  rename(dd_ip = V3,
         ni_ip = V4,
         pl_ip = V5) %>%
  gather(variable,value)

theta.tidy<-rbind(d.tidy,f.tidy)

theta.tidy<- theta.tidy %>% 
  separate(variable, into=c("context","task"), by="_")

theta.tidy$task<-factor(theta.tidy$task,
                    levels=c('tc','ip'),
                    labels=c("truth conditions","implied prevalence"))

theta.tidy$context<-factor(theta.tidy$context,
                        levels=c('dd','ni','pl'), 
                        labels=c("dangerous & distinctive", 
                                 "nondistinctive & irrelevant",
                                 "plain"))

b<-ggplot(theta.tidy,aes(x=value,fill=context,alpha=task))+
  geom_density()+
  theme_paper()+
  scale_alpha_manual(values=c(0.4,1))+
  scale_x_continuous(breaks=c(10,30,50,70,90),limits=c(0,100))+
  scale_fill_brewer(type='qual',palette=6)+
  theme(strip.text.x = element_text(size=14,color='black'),
        legend.position='bottom',
        legend.direction='horizontal',
        axis.title.x =element_text(vjust = -0.5,size=30))+
  xlab(expression(theta))+
  ylab("posterior density")+
  guides(alpha=F)


p3 <- arrangeGrob(b ,a, nrow=1)
p3

# ggsave(filename=paste(plotpath,'fixed_phis_thetas.png',sep=''),
#        plot=p3,
#        width=16,
#        height=4.5,
#        dpi=100)


```

# Figure 3: lvRSA Hyperparameters

```{r fig3.lvRSAhyperparameters}

setwd("~/Documents/research/generics/cbg2010-replication/models/bayesian_analysis")

d<-read.csv('lvRSA_cnts_c1_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
f<-read.csv('lvRSA_cnts_c2_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
g<-read.csv('lvRSA_cnts_c3_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
d<-rbind(d,f,g)


ft.phi <- d %>% select(V1,V2) %>% 
  rename(phi_tc=V1,phi_ip=V2) %>%
  gather(variable,value) %>% 
  separate(variable,into=c("parameter","task"), by="_")

ddply(ft.phi, .(parameter, task), summarise,
      mean=mean(value),
      CIlow=quantile(value,probs=0.025),
      CIhigh=quantile(value,probs=0.975))

qplot(data=ft.phi,x=value,geom='histogram',fill=task)+xlim(0,1)+facet_wrap(~task)



lv.alpha<-d %>% select(V36) %>% rename(alpha=V36)
qplot(data=lv.alpha,x=alpha,geom='histogram')

d.tidy <- d %>%
  select(V3,V4, V6, V7, V9, V10) %>%
  rename(dd_gamma = V3,
         dd_delta = V4,
         ni_gamma = V6,
         ni_delta = V7,
         pl_gamma = V9,
         pl_delta = V10) %>%
  gather(variable,value) %>%
  separate(variable, into=c("context","parameter"), by="_")

params.stats<-ddply(d.tidy, .(context,parameter), summarise,
      mean = mean(value),
      CIlow=quantile(value,probs=0.025),
      CIhigh=quantile(value,probs=0.975))

d.tidy$context<-factor(d.tidy$context,
                        levels=c('dd','ni','pl'), 
                        labels=c("distinctive & dangerous", 
                                 "nondistinctive & nondangerous",
                                 "plain"))

d.tidy$parameter<-factor(d.tidy$parameter, levels=c("gamma",
                                                    "delta"))
                      #   labels(expression(gamma),expression(delta)))

plotpath = "~/Documents/research/generics/cogsci-2015//paper/figures/"


c<-ggplot(d.tidy,aes(x=value,fill=context,color=context))+
  geom_density(alpha=0.5, size=2)+
  scale_color_brewer(palette='Pastel1',type='qual')+
  theme_blackDisplay()+
   scale_x_continuous(limits=c(0,0.5))+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  facet_grid(.~parameter,scales='free',labeller= label_parsed)+
  theme(strip.text.x = element_text(),
      #  legend.position='bottom',
      #  legend.direction='horizontal',
        strip.text.y = element_text(size=60,angle=0))+
  guides(fill=guide_legend(title="Context"),color=F)+
  xlab("\n value")+
  ylab("posterior density \n")



ggsave(plot=c,'../../../semfest-2015/figures/lvRSA_hyperparams_cbg-replication.png',width=22, height=10)
# ggsave(filename=paste(plotpath,'inferred_hyperpriors.png',sep=''),
#        plot=c,
#        width=8,
#        height=6,
#        dpi=100)
```

# Figure 4: Posterior predictives of lvRSA

```{r fig4.lvRSApostpreds}
setwd("~/Documents/research/generics/cbg2010-replication/models/bayesian_analysis")
d<-read.csv('lvRSA_cnts_c1_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
f<-read.csv('lvRSA_cnts_c2_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
g<-read.csv('lvRSA_cnts_c3_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
d<-rbind(d,f,g)


d.tidy <- d %>%
  select(V13, V14, V15, V16, V17,
         V19, V20, V21, V22, V23,
         V25, V26, V27, V28, V29) %>%
  rename(dd_10 = V13,
         dd_30 = V14,
         dd_50 = V15,
         dd_70 = V16,
         dd_90 = V17,
         ni_10 = V19,
         ni_30 = V20,
         ni_50 = V21,
         ni_70 = V22,
         ni_90 = V23,
         pl_10 = V25,
         pl_30 = V26,
         pl_50 = V27,
         pl_70 = V28,
         pl_90 = V29) %>% 
  gather(evidence, response)%>%
  separate(evidence, into = c("context","prevalence"), sep="_")


d.stats<-ddply(d.tidy, .(context,prevalence), summarise,
      mean = mean(response),
      CIlow=quantile(response,probs=0.025),
      CIhigh=quantile(response,probs=0.975))



d.stats$context<-factor(d.stats$context,
                        levels=c('dd','ni','pl'), 
                        labels=c("distinctive & dangerous", 
                                 "nondistinctive & nondangerous",
                                 "plain"))
d.stats$prevalence<-as.numeric(d.stats$prevalence)

## append mosquitos
mosquitos<- data.frame(prevalence=c(10,30,50,70,90),
                       response = c(0.5961676991787926,0.7974369474622407,
                                    0.898555969744128,0.9593832867224066,1))
mosquitos<-rename(mosquitos, mean=response)
mosquitos$context <- 'mosquitos'
mosquitos$CIlow<-mosquitos$mean
mosquitos$CIhigh<-mosquitos$mean

#d.stats<-rbind(d.stats,mosquitos)

a<-ggplot(data=d.stats,aes(x=prevalence,y=mean,color=context,group=context))+
    geom_point(size=3, position=position_dodge(4))+
  geom_line(size=2,position=position_dodge(4))+
  geom_errorbar(aes(ymin=CIlow,ymax=CIhigh,colour=context),
              width=3,
              size=2,
              position=position_dodge(4))+
  scale_colour_brewer(type='qual',palette='Pastel1')+
  #theme(strip.text.x = element_text(size=14,color='black'))+
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(10,30,50,70,90),limits=c(0,100))+
  theme_blackDisplay()+ 
  #guides(color=guide_legend(title="Context"))+
  #guides(color=F)+
  xlab("\n % of kind with feature")+
  ylab('P("true" | generic) \n')+
  coord_fixed(100)+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)

ggsave(plot=a,'../../../semfest-2015/figures/lvRSA_postpredA.png',width=15, height=10)




d.tidy <- d %>%
  select(V13, V14, V15, V16, V17,
         V19, V20, V21, V22, V23,
         V25, V26, V27, V28, V29) %>%
  rename(dd_10 = V13,
         dd_30 = V14,
         dd_50 = V15,
         dd_70 = V16,
         dd_90 = V17,
         ni_10 = V19,
         ni_30 = V20,
         ni_50 = V21,
         ni_70 = V22,
         ni_90 = V23,
         pl_10 = V25,
         pl_30 = V26,
         pl_50 = V27,
         pl_70 = V28,
         pl_90 = V29) 

d.tidy$no<-row.names(d.tidy)

d.tidy <- d.tidy %>%
  gather(variable,value, -no) %>%
  separate(variable,into=c('context','prevalence') ,sep="_") 


pp.stats<-ddply(d.tidy, .(no,context), summarise,
                value.tc = check.zero(as.numeric(prevalence),value))
                  

tc.stats<-ddply(pp.stats, .(context), summarise,
      mean = mean(value.tc),
      CIlow = quantile(value.tc,probs=0.025),
      CIhigh = quantile(value.tc,probs=0.975))

tc.stats$task<-'truth'


pp.ip <- d %>%
  select(V32,V33,V34) %>%
  rename(dd_implied = V32,
         ni_implied=V33,
         pl_implied=V34 )%>%
  gather(variable,value) %>%
  separate(variable,into=c('context','task') ,sep="_")

ip.stats<-ddply(pp.ip, .(context,task), summarise,
      mean = mean(value),
      CIlow = quantile(value,probs=0.025),
      CIhigh = quantile(value,probs=0.975))

c.tidy<-rbind(tc.stats,ip.stats)

c.tidy$context<-factor(c.tidy$context,
                        levels=c('dd','ni','pl'),
                        labels=c("distinctive & dangerous", 
                                 "   nondistinctive & irrelevant ",
                                 "plain"))
c.tidy$task <- factor(c.tidy$task,
                 levels=c("truth","implied"),
                 labels=c("truth conditions", "implied prevalence"))







simulated.subjs<-data.frame(dd=NA,ni=NA,pl=NA)
for (i in 1:5000){
  simulated.subjs[i,]<-simulate_subject(d.stats)
}

s.tidy<- simulated.subjs %>%
  gather(key,value)

s.stats<-ddply(s.tidy, .(key), summarise,
               mean = mean(value, na.rm=T),
               CILow = quantile(value,probs=0.025, na.rm=T),
               CIHigh = quantile(value,probs=0.975, na.rm=T))       


### replace with "simulated subjects".. no CIs
c.tidy[1:3,2:4]<-s.stats["mean"]
# 
### append accidental simluation

accidental<-data.frame(tasks = c('tc','ip'),
          prevalence = c(63.41008611540007,50.05101669894225))


accidental$tasks<-factor(accidental$tasks, levels=c('tc','ip'),
                         labels=c('truth conditions','implied prevalence'))

accidental<-rename(accidental, task=tasks, mean=prevalence)
accidental$CIlow<-accidental$mean
accidental$CIhigh<-accidental$mean
accidental$context<-'accidental'

# c.tidy<-rbind(c.tidy,accidental)
# c.tidy$context<-factor(c.tidy$context, 
#                        levels=c(" dangerous \n& distinctive",
#                                 '    irrelevant \n& nondistinctive',
#                                 'plain','mosquito','accidental'),
#                        labels=c("dangerous & distinctive",
#                                 'nondistinctive & irrelevant',
#                                 'plain','mosquito','accidental'))


b<-ggplot(c.tidy, aes(x=context,y=mean,fill=context,alpha=task, group=task))+
  geom_bar(stat='identity',position=position_dodge(0.5), width=0.5,color='white')+
  geom_errorbar(aes(ymin=CIlow,ymax=CIhigh),
                width=0.2,
                size=2,
                color='white',
                position=position_dodge(0.5))+
  theme_blackDisplay()+
  ylab("average prevalence \n")+
  ylim(0,100)+
  scale_fill_brewer(type='qual',palette='Pastel1', drop=F)+
  scale_alpha_manual(values=c(0.4,1))+
  xlab("")+
  guides(fill=F,#guide_legend(order=1),
         alpha=guide_legend(order=2))#+
#  theme(legend.position='bottom',
#         legend.direction='horizontal',
#         legend.box= 'horizontal',
#         axis.text.x=element_blank())

ggsave(plot=b,'../../../semfest-2015/figures/lvRSA_postpredB.png',width=25, height=10)



mylegend<-g_legend(b)

p3 <- arrangeGrob(arrangeGrob(a + theme(legend.position="none"),
                         b + theme(legend.position='none'),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))




#p3
# ggsave(filename=paste(plotpath,'lvRSA_postpreds_wSims.png',sep=''),
#        plot=p3,
#        width=14,
#        height=6,
#        dpi=100)
```

# Figure 5: Priors

## 5a: reconstructed priors

```{r fig5a.marginalizedPriors}

setwd("~/Documents/research/generics/cbg2010-replication/models/bayesian_analysis")
d<-read.csv('lvRSA_cnts_c1_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
f<-read.csv('lvRSA_cnts_c2_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
g<-read.csv('lvRSA_cnts_c3_expts9_12_generic_mh1000_50_alpha1.csv',header=F)
d<-rbind(d,f,g)

bns<-c(0.01,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,0.99)

d.tidy <- d %>%
  select(V3,V4, V6, V7, V9, V10) %>%
  rename(dd_gamma = V3,
         dd_delta = V4,
         ni_gamma = V6,
         ni_delta = V7,
         pl_gamma = V9,
         pl_delta = V10)

d.tidy$s<- row.names(d.tidy)

d.tidy<- d.tidy %>% gather(variable,value,-s) %>% 
  separate(variable, into=c("parameter","context"), by="_") %>% 
  spread(context,value)

x = with(d.tidy, discretize_beta(gamma, delta))
colnames(x) <- bns
d.tidy2 <- cbind(d.tidy, x)

d.tidy3<-d.tidy2 %>% 
  rename(context=parameter) %>%
  gather(bin, prob, -s, -context, -delta, -gamma)

db.stats<- d.tidy3 %>% 
  ddply(.(context, bin),summarise,
        mean=mean(prob),
      CIlow=quantile(prob,probs=0.025),
      CIhigh=quantile(prob,probs=0.975))

db.norm <- data.frame(
  dd_mean = with(subset(db.stats, context=='dd'), mean / sum(mean)),
  ni_mean = with(subset(db.stats, context=='ni'), mean / sum(mean)),
  pl_mean = with(subset(db.stats, context=='pl'), mean / sum(mean)),
  dd_CIlow = with(subset(db.stats, context=='dd'), CIlow / sum(CIlow)),
  ni_CIlow = with(subset(db.stats, context=='ni'), CIlow / sum(CIlow)),
  pl_CIlow = with(subset(db.stats, context=='pl'), CIlow / sum(CIlow)),
  dd_CIhigh = with(subset(db.stats, context=='dd'),  CIhigh / sum(CIhigh)),
  ni_CIhigh = with(subset(db.stats, context=='ni'), CIhigh / sum(CIhigh)),
  pl_CIhigh = with(subset(db.stats, context=='pl'), CIhigh / sum(CIhigh)))

db.norm$bin <- to.n(bns)

db.norm.tidy <- db.norm %>%
  gather(variable,value,-bin) %>%
  separate(variable,into=c('context','statistic'), by ="_")%>%
  spread(statistic, value)

db.norm.tidy$context<-factor(db.norm.tidy$context, 
                             labels =c("distinctive & dangerous",
                                       "nondistinctive & nondangerous",
                                       "plain"))

a<-ggplot(db.norm.tidy,aes(x=100*bin,y=mean,fill=context))+
  geom_bar(stat='identity',position=position_dodge())+
  #xlim(0,100)+
  facet_grid(.~context)+
  guides(fill=F)+
    theme_blackDisplay()+
  scale_x_continuous(breaks=c(0,20,40,60,80,100))+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  xlab("\n % of kind with feature")+
  ylab("inferred prior probability \n")+
  theme(strip.background = element_blank(),
       strip.text.y = element_text(angle=0))


ggsave(plot=a,'../../semfest-2015/figures/lvRSA_posteriorPriors.png',width=20, height=10)

db.norm.stats<-db.norm.tidy %>%
  group_by(context) %>%
  summarise(exp_val = sum(bin*mean),
            CIhigh = sum(bin*CIhigh),
            CIlow = sum(bin*CIlow))

ggplot(db.norm.stats, aes(x = context, y = exp_val*100, fill=context))+
  geom_bar(stat='identity', size=1)+
  geom_errorbar(aes(ymin=CIlow*100, ymax=CIhigh*100), 
                width = 0.3, color='white',size=2)+
  theme_blackDisplay()+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  xlab("")+
  ylab("inferred mean prevalence\n")+
  guides(fill=F)

ggsave('../../semfest-2015/figures/lvRSA_inferredMeanPriors.png',width=20, height=10)
  #      legend.position='bottom',
  #      legend.direction='horizontal')

# ggsave(filename=paste(plotpath,'inferred_marginalized_priors.png',sep=''),
#        plot=a,
#        width=12,
#        height=4.5)


```


## Figure 5b: Exp2 elicited priors


```{r fig5b.exp2elicitedpriors}

setwd("~/Documents/research/generics/cbg2010-replication/data")
d<-read.table('cbgR-exp11-trials.tsv',header=T)
de<-read.table('cbgR-exp11e-trials.tsv',header=T)
de$workerid<-de$workerid+length(unique(d$workerid))
d<-rbind(d,de)

d$item <- paste(d$stim_color,d$stim_part,sep="_")
table(d$stim_type,d$item)
table(d$stim_type,d$stim_part)


d.tidy<-d%>%   select(workerid,rt,
              response0,response1,response2,response3,response4,
              stim_type) %>%
  rename(context=stim_type) %>%
  gather(option,value,-workerid,-rt,-context)


d.tidy$context<-factor(d.tidy$context,
                       levels=c("danger-distinct",
                                "nondistinctive",
                                "bare"), 
                        labels=c("distinctive & dangerous", 
                                 "nondistinctive & nondangerous",
                                 "plain"))


ggplot(d.tidy,aes(x=value,fill=context))+
  geom_histogram(binwidth=0.5)+
  facet_wrap(~context)+
  guides(fill=F)+
  scale_fill_brewer(type='qual',palette=6)+
  xlab('prevalence')+
  ggtitle('human elicited prior distribution')



d.tidy$roundval<-round(d.tidy$value/10)*10
unnormed<-table(d.tidy[,c("context","roundval")])
normedexp2<-data.frame(dd=unnormed[1,]/sum(unnormed[1,]),
           ni=unnormed[2,]/sum(unnormed[2,]),
           pl=unnormed[3,]/sum(unnormed[3,]))
normedexp2$prevalence = row.names(normedexp2)

ggplot(d.tidy,aes(x=roundval,fill=context))+
  geom_histogram(binwidth=10)+
  facet_grid(.~context)+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  xlab('\n % of kind with feature')+
    theme_blackDisplay()+
    theme(strip.background = element_blank(),
       strip.text.y = element_text(angle=0),
        legend.position='bottom',
        legend.direction='horizontal')+
  guides(fill=F)

ggsave('../../semfest-2015/figures/exp2.png',width=20, height=10)



plotpath = "~/Documents/research/generics/cogsci-2015//paper/figures/"

# 
# ggsave(filename=paste(plotpath,'elicited_priors.png',sep=''),
#        plot=exp2,
#        width=12,
#        height=4.5)


```

# Experiment 2 stats

```{r exp2.stats}

bootstrap.ci.prior(d.tidy)



dip.test(subset(d.tidy,context=='plain')$value)
dip.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value)
dip.test(subset(d.tidy,context=='dangerous & distinctive')$value)


contrasts(d.tidy$context)<-cbind(dd = c(-2,1,1), ni = c(0, 1, -1))
contrasts(d.tidy$context)<-cbind(dd = c(1,0,-1), ni = c(-1, 2, -1))

rs<-lmer(value ~ context + (1 | workerid), data=d.tidy)
summary(rs)

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!="nondistinctive & irrelevant"))

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!='dangerous & distinctive'))

wilcox.test(value ~ context, 
            data = subset(d.tidy, context!='plain'))

kruskal.test(value ~ context, data = d.tidy) 

ks.test(subset(d.tidy,context=='plain')$value,
        subset(d.tidy,context=='dangerous & distinctive')$value)

ks.test(subset(d.tidy,context=="nondistinctive & irrelevant")$value,
        subset(d.tidy,context=='dangerous & distinctive')$value)

ks.test(subset(d.tidy,context=='plain')$value,
        subset(d.tidy,context=="nondistinctive & irrelevant")$value)
```

 
# Figure 6: Schematic priors

Schematic density plots for the "mosquito" and "accidental" priors

```{r fig6.schematic_priors}
mosquitos.data<-data.frame(t(rmultinom(10000, 
                                       1, 
                                       c(0.15,0.00001,0.05,
                                         0.00058,0.00058,
                                         0.00032,0.00032,
                                         0.00024,0.00024,
                                         0.00020,0.00020,
                                         0.00018, 0.00018,
                                         0.00018,0.00018,
                                         0.0002,0.0002,
                                         0.0002,0.0002,
                                         0.00032,0.000032))))

acc.data<-data.frame(t(rmultinom(10000, 
                                   1, 
                                  discretize_beta(0.2,10,
                                 c(0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,
                                   0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,
                                   0.9,0.95,0.99)))))


m.tidy<-mosquitos.data %>% 
  rename(x0.01 = X1,
          x05 = X2, 
          x10 = X3, 
          x15 = X4,
          x20 = X5, 
          x25=  X6,
          x30 = X7, 
          x35 = X8, 
          x40 = X9, 
          x45 = X10, 
          x50 = X11,
          x55 = X12, 
          x60 = X13, 
          x65 = X14,
          x70 = X15, 
          x75=  X16,
          x80 = X17, 
          x85 = X18, 
          x90 = X19, 
          x95 = X20,
          x99 = X21) %>%
  gather(key, value)
m.tidy$key<-to.n(substring(m.tidy$key,2))
m.tidy<-subset(m.tidy,value!=0)
m.hist<- data.frame(prev=m.tidy$key*m.tidy$value)


a.tidy<-acc.data %>% 
  rename(x0.01 = X1,
          x05 = X2, 
          x10 = X3, 
          x15 = X4,
          x20 = X5, 
          x25=  X6,
          x30 = X7, 
          x35 = X8, 
          x40 = X9, 
          x45 = X10, 
          x50 = X11,
          x55 = X12, 
          x60 = X13, 
          x65 = X14,
          x70 = X15, 
          x75=  X16,
          x80 = X17, 
          x85 = X18, 
          x90 = X19, 
          x95 = X20,
          x99 = X21) %>%
  gather(key, value)
a.tidy$key<-to.n(substring(a.tidy$key,2))
a.tidy<-subset(a.tidy,value!=0)
a.hist<- data.frame(prev=a.tidy$key*a.tidy$value)
a.hist$context = 'accidental'
m.hist$context = 'mosquito'


m.hist= rbind(a.hist,m.hist)

m.hist$context<-factor(m.hist$context, levels=c("accidental","mosquito"))

a<-ggplot(m.hist, aes(x=prev,fill=context)) +
  geom_density(adjust=1.8, alpha=0.8)+
  scale_x_continuous(breaks=c(0,20,40,60,80,100))+
  scale_fill_manual(values=c('#ff7f00','#984ea3'))+
  theme_blackDisplay()+
  facet_wrap(~context)+
  xlab("\n prevalence level")+
  ylab("schematic prior density \n")+
  theme(strip.background = element_blank(),
       strip.text.x = element_blank(),
        legend.position='bottom',
        legend.direction='horizontal')

ggsave(plot=a,'../../../semfest-2015/schematic_priors.png',width=16, height=8)

a<-ggplot(m.hist, aes(x=prev,fill=context)) +
  geom_density(adjust=1.8, alpha=0.8)+
  scale_x_continuous(breaks=c(0,20,40,60,80,100))+
  scale_fill_manual(values=c('#ff7f00','#984ea3'))+
  xlab("prevalence level")+
  ylab("schematic prior density")+
  theme(strip.background = element_blank(),
       strip.text.x = element_blank(),
        legend.position='bottom',
        legend.direction='horizontal')

a
# plotpath = "~/Documents/research/generics/cogsci-2015//paper/figures/"
# 
# ggsave(filename=paste(plotpath,'schematic_priors.png',sep=''),
#        plot=a,
#        width=5,
#        height=5)
```

# SemFest talk plots


## Schematic priors
```{r}
discretize_beta_shape<- function(s_alpha,s_beta,
                           bins = c(0.01,0.1,0.2,0.3,0.4,0.5,
                                    0.6,0.7,0.8,0.9,0.99)) {
  beta_pdf<- function(x){
    return((x^(s_alpha-1))*((1-x)^(s_beta-1)))
  }
  return(sapply(bins,beta_pdf))
}

xf<- data.frame(bins = c(0.01,0.1,0.2,0.3,0.4,0.5,
                                    0.6,0.7,0.8,0.9,0.99),
               probs = discretize_beta_shape(5,5)/sum(discretize_beta_shape(5,5))+
                      discretize_beta_shape(1,10)/sum(discretize_beta_shape(1,10)))

qplot(data =xf, x=bins, y=probs,geom='bar',stat='identity')

```

```{r schematic.priors}


s<-data.frame(nzhikes=rbeta(10000,3,3),
             # acc=rbeta(10000,5,15),
            #  bio=rbeta(10000,0.01,0.2),
               bio=rbeta(10000,0.01,0.032),
             # rare = c(rbeta(3000,20,150),rbeta(7000,10,1000)))
             # rare = c(rbeta(3000,10,100),rbeta(7000,10,1000)))
              gendered = c(rbeta(3000,50,50),rbeta(7000,100,10000)),
              rare = c(rbeta(3000,100,900),rbeta(7000,100,10000)))

s.tidy<- s %>%
  gather(key,value)

s.tidy$key<-factor(s.tidy$key,
                   labels=c("typical","biological","gendered","rare"))


ggplot(s.tidy, aes(x=value*100,color=key,fill=key)) +
  geom_density(size=2,adjust=1.5,alpha=0.5)+
  scale_color_brewer(palette='Set3',type='qual')+
  scale_fill_brewer(palette="Set3",type='qual')+
  facet_grid(key~.,scales='free')+
  xlim(0,100)+
  theme_blackDisplay()+
  xlab("\n % of category C with feature F")+
  ylab("schematic prior probability \n")+
  theme(strip.background = element_blank(),
       strip.text.y = element_text(angle=0),
        legend.position='bottom',
        legend.direction='horizontal',
        axis.text.y = element_blank())+
  guides(color=F,fill=F)

ggsave('../../semfest-2015/figures/schematic_priors.png',width=10, height=10)

```

## Schematic prior simulations

### Truth conditions simulations
```{r schematic.tc}
tc.sims<- data.frame(prevlev = c(10,30,50,70,90),
              nzhikes=c(0.10, 0.299,0.5,0.70,0.9),
              # acc=c(0.25,0.56,0.75,0.875,0.964),
              #gendered=c(0.30, 0.63, 0.75, 0.87, 0.96),
              bio=c(0.180,0.458,0.663,0.82,0.94),
              gendered=c(0.25, 0.56, 0.75, 0.87, 0.96),
               rare=c(0.67,0.89,0.95,0.98,0.994))

tc.tidy<- gather(tc.sims, key, value, -prevlev)
        
tc.tidy$key<-factor(tc.tidy$key,
                   labels=c("typical","biological","gendered","rare"))

ggplot(tc.tidy, aes(x=prevlev,y=value,
                  colour=key, group=key))+
  geom_point(size=3, position=position_dodge(5))+
  geom_line(size=2,position=position_dodge(5))+
  scale_colour_brewer(type='qual',palette=8)+
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(10,30,50,70,90),limits=c(0,100))+
  theme_blackDisplay()+ 
  guides(color=guide_legend(title="Feature type"))+
  xlab("\n % of category C with feature F")+
  ylab('P("true" | generic)\n')+
  coord_fixed(100)+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)

ggsave('../../semfest-2015/figures/schematic_priors_TCdata.png',width=10, height=10)
```

### Asymmetry simulations
```{r schematic.asymm}
asym.sims<- data.frame(task=c("tc","ip"),
                       nzhikes = c(66,58.5),
                      # acc = c(41,29),
                       bio = c(65,92.6407),
                       gendered = c(60.2,50.5),
                       rare = c(50.3,10.4))

asym.tidy<- gather(asym.sims, key, value, -task)
asym.tidy$key<-factor(asym.tidy$key,
                   labels=c("typical","biological","gendered","rare"))

asym.tidy$task<-factor(asym.tidy$task,levels=c("tc","ip"),
                       labels=c("average Truth Conditions",
                                "Implied Prevalence"))

ggplot(asym.tidy, aes(x=task,y=value,fill=key,alpha=task))+
  geom_bar(stat='identity',position=position_dodge(0.5), 
           width=0.5,color='white')+
  theme_blackDisplay()+
  ylab("\n % of category with feature")+
  scale_fill_brewer(type='qual',palette=8)+
  scale_alpha_manual(values=c(0.4,1))+
  xlab("")+
  theme(legend.position='bottom',
        legend.direction='horizontal',
        legend.box = 'horizontal'
        #axis.text.x=element_blank()
        )+
  guides(fill = guide_legend(title = 'Feature type',order = 2), 
          alpha = F)#guide_legend(title='Task',order = 1,reverse=T))
 # coord_flip()

ggsave('../../semfest-2015/figures/schematic_priors_ASYMdata.png',width=15, height=12)
```

## Treeberad is tall priors


```{r tall.frodo}

s<-data.frame(hobbits=rnorm(10000,mean=3.6,sd=0.5),
              ents = rnorm(10000,mean=20,sd=1.5),
              creatures = rnorm(10000, mean = 10, sd = 5))
              
s.tidy<- s %>%
  gather(key,value)

#s.tidy$key<-factor(s.tidy$key,
#                   labels=c("typical","accidental","biological","rare"))


ggplot(s.tidy, aes(x=value,color=key,fill=key)) +
  geom_density(size=2,adjust=1.5,alpha=0.5)+
  scale_color_brewer(palette='Pastel2',type='qual')+
  scale_fill_brewer(palette="Pastel2",type='qual')+
 # facet_grid(key~.,scales='free')+
  theme_blackDisplay()+
  xlim(0,30)+
  xlab("\n height (ft)")+
  ylab("schematic prior probability \n")+
  theme(strip.background = element_blank(),
       strip.text.y = element_text(angle=0),
     #   legend.position='bottom',
    #    legend.direction='horizontal',
      legend.title = element_blank(),
        axis.text.y = element_blank())

ggsave('../../semfest-2015/figures/schematic_height.png',width=10, height=7)

```

## Post- Semfest

Mike Frank asked about the second hump in the elicited priors. It seems to be pretty robust. Could be a dependent measure thing, or could be interesting. 

After a discussion with Long, I came to conclusion that the fit prior can never be as good as the real prior. I tried to make a counter argument, and there was one: When the cost of research is very expensive, and you'd like to be able to make a lot of predictions to see what other things, which rely on the same prior knowledge, could be made. This could be particularly useful for developmental research.

+ Does this relate to Noah's human conceptome project?

It would be cool to make this and then to make open source various queestion and answer pairs (concept queries and resposes), ideally in different dependent measures and with docs, what these could be used for, etc.

### Concrete Prediction

The use of the experimental priors will lead to quantitative and qualitative better fit. I run the model called `lvRSA_emprior.church`. Returning truth conditions and implied prevalence and prevalence based on TC score. 

+ Note: I actually need to do the parameter fitting / FBT model, before making any strong judgments

```{r schematic.tc}
tc.sims<- data.frame(prevlev = c(10,30,50,70,90),
              distinct=c(0.10, 0.299,0.5,0.70,0.9),
              nondistinct=c(0.180,0.458,0.663,0.82,0.94),
              bare=c(0.25, 0.56, 0.75, 0.87, 0.96))

asym.sims<- data.frame(task=c("t.c.","i.p."),
                       distinct = c(66,58.5),
                       nondistinct = c(65,92.6407),
                       bare = c(60.2,50.5))


tc.tidy<- gather(tc.sims, key, value, -prevlev)
        
tc.tidy$key<-factor(tc.tidy$key,
                   labels=c("typical","biological","gendered","rare"))

ggplot(tc.tidy, aes(x=prevlev,y=value,
                  colour=key, group=key))+
  geom_point(size=3, position=position_dodge(5))+
  geom_line(size=2,position=position_dodge(5))+
  scale_colour_brewer(type='qual',palette=1)+
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_continuous(breaks=c(10,30,50,70,90),limits=c(0,100))+
  #theme_blackDisplay()+ 
  theme_bw()+
  guides(color=guide_legend(title="Feature type"))+
  xlab("\n % of category C with feature F")+
  ylab('P("true" | generic)\n')+
  coord_fixed(100)+
  theme(legend.key.size=unit(2, "lines"),
        legend.text.align=NULL)

```


