---
title: "generics of natural kinds"
author: "mht"
date: "May 16, 2015"
output: html_document
---

# Prior 1: Prevalence priors for 8 properties

n = 30. 80 responses per subject. [Experiment here](http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-1.html)

Subjects first see a list of 5 animals. They are asked to add 5 of their own to the list. Then, a column is revealed that asks them to estimate the % of each animal kind that has a property. Subjects fill out the column (rating prevalence for each animal). Upon hitting continue, the next column (hence, property) is revealed. There are 8 properties in total. They are:

1. Have wings
2. Have spots
3. Have pouches
4. Lay eggs
5. Carry malaria
6. Attack swimmers
7. Are male
8. Are female

Subjects are permitted to "go back" and change their prevalence estimate for properties presented earlier in the sequence. The "Animal list" cannot be changed, however.

Subjects are given 5 out of the following 6 animals to initialize the list.

1. Birds
2. Leopards
3. Ducks
4. Lions
5. Mosquitos
6. Sharks

```{r echo=F}
upperFirst <- function(name){
  return (paste(toupper(substr(name, 1, 1)), substr(name, 2, nchar(name)), sep=""))
}

removeS <- function(name){
  exceptions = c("Turtles", "Bees", "Horses", "Giraffes","Whales")
  last<-substr(name,nchar(name),nchar(name))
  last2<-substr(name,nchar(name)-1,nchar(name))
  if (name%in%exceptions){
    name.singular <- substr(name,1,nchar(name)-1)
  } else if (last2=='es') {
    name.singular <- substr(name,1,nchar(name)-2)
  } else if (last=='s') {
    name.singular <- substr(name,1,nchar(name)-1)
  } else  {
    name.singular <- name
  }
return(name.singular)
}


setwd(dir = 'generics/analysis/')
generics.of.interest <- data.frame(
  animal=c("Bird","Leopard","Duck","Lion","Mosquito","Shark"),
  property=c("lays eggs", "has spots","has wings","has manes","carries malaria",
                                             "attack swimmers"))

animals.given <- c("Bird","Leopard","Duck","Lion","Mosquito","Shark")



d<-read.csv(file = '~/Documents/research/generics/data/real-kinds/real-kinds-1-trials.csv')

d$animal.parsed<- factor(unlist(Map(removeS, upperFirst(as.character(d$animal)))))
d$property<-factor(d$property, 
                   levels=c("has spots", "has wings","has manes", "lays eggs",
                            "attack swimmers", "carries malaria",
                            "is male", "is female"))
```


# Response histogram

```{r}
ggplot(d, aes(x=prevalence))+geom_histogram(binwidth=5)+ggtitle('binwidth=5')
```

For each subject:

```{r}
ggplot(d, aes(x=prevalence))+
  geom_histogram(binwidth=5)+
  facet_wrap(~workerid)+
  scale_x_continuous(breaks=c(0, 50, 100))

```


# Animal production data

```{r exp1.newAnimals, fig.width=32}

# retrieve novel animals (and count only one instance per subject)
animals.produced<-filter(d,
                         (!(animal.parsed %in% animals.given)&
                            (property_index==0)))


ggplot(animals.produced, aes(x=animal.parsed))+
  geom_histogram()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

# Prevalence distributions


## Estimates for each animal.

Some of these animals have very few responses, owing to the fact that they were produced by just one or a few subjects. Ordering is alphabetical by animal name. Light blue bars indicate the category of interest for each property (for the generic).

```{r exp1.estimatesByAnimal, fig.height=15, fig.width=36}

d.tidy<- d %>%
  group_by(property,animal.parsed) %>%
  summarise(prev = mean(prevalence),
            sterr=sem(prevalence))

generics.of.interest$combined <- paste(generics.of.interest$property, 
                                       generics.of.interest$animal)
d.tidy$combined <- paste(d.tidy$property, d.tidy$animal.parsed)

d.tidy$interest<-d.tidy$combined %in% generics.of.interest$combined

ggplot(data=d.tidy, aes(x=animal.parsed, y=prev, fill=interest))+
  geom_bar(stat='identity',position=position_dodge())+
  facet_wrap(~property)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Reducing this plot to only the animals that were given to subjects (+ Dog and Cat, which over a third of subjects produced)

```{r exp1.estimatesByAnimal.reduced, fig.height=10, fig.width=20}

animals.with.at.least10.responses <- c(animals.given, c("Cat","Dog"))
animals.with.at.least5.responses <- c(animals.given, c("Cat","Dog","Chicken","Turtle","Tiger","Monkey","Frog",
                                                       "Bear"))


d.tidy.sub<- d.tidy %>% filter(animal.parsed %in%animals.with.at.least5.responses)

ggplot(data=d.tidy.sub, aes(x=animal.parsed, y=prev, fill=interest))+
  geom_bar(stat='identity',position=position_dodge())+
  geom_errorbar(aes(ymin=prev-2*sterr,ymax=prev+2*sterr),position=position_dodge(),width=0.5)+
  facet_wrap(~property)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Distribution by animal

Here, I plot the distribution of prevalence after summarizing an average prevalence for each animal. Hence, a sample from this distribution is an animal category (with an associated prevalence of the property). Again note:: many of these categories have very few responses.

Green line indicates prevalence for target category.
```{r}
ggplot(data=d.tidy, aes(x=prev))+
  geom_vline(data=filter(d.tidy,interest), aes(xintercept=prev),
             colour='#2ca25f',size=1.3)+
  geom_histogram(binwidth=5)+
  facet_wrap(~property)
```


## Distribution by response

Here, I don't include the intermediate step of summarising by animal kind. Instead, I just plot the density directly from subjects' responses. Again, green line indicates prevalence for target categogry.

```{r}

d.interest<-d.tidy %>% filter(interest)

ggplot(data = d, aes(x=prevalence))+
  #geom_histogram()+
  geom_density(adjust=0.5, fill='grey')+
  facet_wrap(~property,scales='free')+
  geom_vline(data=d.interest, aes(xintercept=prev), colour='#2ca25f',size=1.3)
```


Binned distributions (for model)

```{r}
d <- d %>% mutate(roundval=factor(round(prevalence/10)*10))

d.bin<- d %>%
  group_by(property, roundval) %>%
  summarise(count = length(roundval)) %>%
  ungroup() %>% group_by(property) %>%
  mutate(prob = count/sum(count),
         roundval = to.n(roundval))

ggplot(d.bin, aes(x=roundval, y=prob))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~property)+
  xlab("prevalence")+
  ylab("proportion of responses\n")+
  #scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_discrete(breaks=c(0,20,40,60,80,100))+#,limits=c(-5,105))+
 # theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
#  theme(legend.key.size=unit(2, "lines"),
#        legend.text.align=NULL)+
  guides(fill=F)

filter(d, property=='attack swimmers' & prevalence>90)$animal.parsed
```

Looks like "Mosquitos attack swimmers." is probably true.


```{r}
d.bin %>% select(-prob) %>% spread(roundval, count)

```


#### Markman's question: Is "lays eggs" affected by "are female"?

```{r}

d.femFirst<-d %>%
  filter((animal.parsed %in% c("Duck","Bird","Mosquito")) & 
           property %in% c("is female","lays eggs")) %>%
  select(workerid, animal.parsed, property, property_index) %>%
  mutate(property = factor(property, levels=c("is female","lays eggs"),
                           labels=c("female","eggs"))) %>%
  spread(property, property_index) %>%
  mutate(femFirst = female<eggs)



d.birds<- d %>%
  filter((animal.parsed %in% c("Duck","Bird","Mosquito")) & 
           property %in% c("is female","lays eggs")) 

d.birds<-left_join(d.birds, d.femFirst, by="workerid")

d.birds %>%
  group_by(property, animal.parsed.x, femFirst) %>%
  summarise(mean(prevalence))
  


```


### lvRSA simultation (with scraped Prasada data)

Doing TFBT with speaker optimality (at the S1 level) as a free parameter

```{r}
model.posteriorpred <-read.csv('~/Documents/research/generics/cbg2010-replication/models/model_predictions/generics_truthJudge_prasada1.csv',header=F,
                               col.names=c("generic","posteriorPred"))

prasada.data <-data.frame(generic = c("leopards have spots",
                                    	"birds have wings",
                                    	"lions have manes",
                                    	"ducks lay eggs",
                                    	"mosquitos carry malaria",
                                    	"sharks attack swimmers",
                                    	"lions are male",
                                    	"ducks are female",
                                    	"lions have wings"),
                          truth_judgment = c( 2.17,2.63,1.46,2.04,1.63,1.5,-0.04,
                                              -0.58,-2.5),
                          prevalence = c(93,92, 57, 78, 30, 31, 50, 50, 0)

)


combined.model.data<- left_join(model.posteriorpred, prasada.data)

with(combined.model.data, cor(posteriorPred, truth_judgment))
with(combined.model.data, cor(prevalence, truth_judgment))


qplot(data=combined.model.data,
      x=posteriorPred,y=truth_judgment,
      color=generic)+
  geom_point(size=3)

qplot(data=combined.model.data,
      x=prevalence,y=truth_judgment,
      color=generic)+
  geom_point(size=3)


```




# Prior 2: Prevalence priors for 16 properties


```{r echo=F}
upperFirst <- function(name){
  return (paste(toupper(substr(name, 1, 1)), substr(name, 2, nchar(name)), sep=""))
}

removeS <- function(name.in){
  exceptions = c("Turtles", "Bees", "Horses", "Giraffes","Whales","Beetles","Eagles","Snakes","Moles")
  bluejays =  c("Blue jay","Blue Jay","Bluejay")
  fleas = c("Flea", "Fly")
  name<-removeSpace(name.in)
  last<-substr(name,nchar(name),nchar(name))
  last2<-substr(name,nchar(name)-1,nchar(name))
  if (name%in%exceptions){
    name.singular <- substr(name,1,nchar(name)-1)
  } else if (name%in%bluejays){
    name.singular <- "Bluejay"
  } else if (name%in%fleas){
    name.singular <- "Flea"
  } else if (name=="Wolves") {
    name.singular <- "Wolf"
  } else if (name=='Dolpin') {
    name.singular <- "Dolphin"
  } else if (name=='Giraffs') {
    name.singular <- "Giraffe"
  }  else if (last2=='es') {
    name.singular <- substr(name,1,nchar(name)-2)
  } else if (last=='s') {
    name.singular <- substr(name,1,nchar(name)-1)
  } else {
    name.singular <- name
  }
  
return(name.singular)
}

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

removeSpace <- function(name){
  if (substrRight(name,1)==' ') {
    name.edit <- substr(name,1, nchar(name)-1)
  } else {
    name.edit <- name
  }
  return(name.edit)
}

setwd(dir = '~/Documents/research/generics/analysis/')
generics.of.interest <- data.frame(
  animal=c("Robin","Leopard","Duck","Lion","Mosquito","Shark","Cardinal","Kangaroo","Peacock","Tiger","Tick","Swan"),
  property=c("lay eggs", "have spots","have wings","have manes","carry malaria",
              "attacks swimmers","are red","have pouches","have beautiful feathers","eat people","carry Lyme disease","are white"))

d<-read.csv(file = '../experiments/turk/real-kinds-prior-2/real-kinds-2-trials.csv')
d0<-read.csv(file='../experiments/turk/real-kinds-prior-2/real-kinds-2pilot5/real-kinds-2-trials.csv')

d0$workerid = max(d$workerid) + d0$workerid+1
d<-bind_rows(d,d0)

d[d$property=='are juveline',]$property<-'are juvenile'

d$animal.parsed<- factor(unlist(Map(removeS, upperFirst(as.character(d$animal)))))

```


# Response histogram

```{r}
ggplot(d, aes(x=prevalence))+geom_histogram(binwidth=5)+ggtitle('binwidth=5')
```

For each subject:

```{r}
ggplot(d, aes(x=prevalence))+
  geom_histogram(binwidth=5)+
  facet_wrap(~workerid)+
  scale_x_continuous(breaks=c(0, 50, 100))

```


# Animal production data

```{r exp2.newAnimals, fig.height=25, fig.width=16}

# retrieve novel animals (and count only one instance per subject)
animals.produced<-filter(d,
                         (!(animal.parsed %in% generics.of.interest$animal)&
                            (property_index==0)|(property_index==8)))


animals.produced$animal_parsed<-with(animals.produced, 
                                     reorder(sentence, response, function(x) -x))

sort(table(animals.produced$animal.parsed))[sort(table(animals.produced$animal.parsed))>10]

# ggplot(animals.produced, aes(x=animal.parsed))+
#   geom_histogram()+
#   #theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   coord_flip()

```

# Prevalence distributions


## Estimates for each animal.

Some of these animals have very few responses, owing to the fact that they were produced by just one or a few subjects. Ordering is alphabetical by animal name. Light blue bars indicate the category of interest for each property (for the generic).

```{r exp2.estimatesByAnimal, fig.height=15, fig.width=36}

d.tidy<- d %>%
  group_by(property,animal.parsed) %>%
  summarise(prev = mean(prevalence),
            sterr=sem(prevalence)) %>%
  filter(!(is.na(sterr)))

generics.of.interest$combined <- paste(generics.of.interest$property, 
                                       generics.of.interest$animal)
d.tidy$combined <- paste(d.tidy$property, d.tidy$animal.parsed)

d.tidy$interest<-d.tidy$combined %in% generics.of.interest$combined

ggplot(data=d.tidy, aes(x=animal.parsed, y=prev, fill=interest))+
  geom_bar(stat='identity',position=position_dodge())+
  facet_wrap(~property)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Reducing this plot to only the animals that were given to subjects

```{r exp2.estimatesByAnimal.reduced, fig.height=10, fig.width=20}

d.tidy.sub <- d.tidy %>% 
  filter(animal.parsed %in% generics.of.interest$animal)
#   group_by(animal.parsed) %>%
#   mutate(count = length(animal.parsed)) %>%
#   filter(count > 10)

ggplot(data=d.tidy.sub, aes(x=animal.parsed, y=prev, fill=interest))+
  geom_bar(stat='identity',position=position_dodge())+
  geom_errorbar(aes(ymin=prev-2*sterr,ymax=prev+2*sterr),
                position=position_dodge(),width=0.5)+
  facet_wrap(~property)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

d.tidy.sub %>%
  filter(combined %in% generics.of.interest$combined)


```


## Distribution by animal

Here, I plot the distribution of prevalence after summarizing an average prevalence for each animal. Hence, a sample from this distribution is an animal category (with an associated prevalence of the property). Again note:: many of these categories have very few responses.

Green line indicates prevalence for target category.
```{r}
ggplot(data=d.tidy, aes(x=prev))+
  geom_vline(data=filter(d.tidy,interest), aes(xintercept=prev),
             colour='#2ca25f',size=1.3)+
  geom_histogram(binwidth=5)+
  facet_wrap(~property)
```

Binned distributions (for model)

```{r}
d.tidy<- d.tidy %>% mutate(roundval=round(prev/10)*10) 

d.anim.bin<- d.tidy %>%
  group_by(property, roundval) %>%
  summarise(count = length(roundval)) %>%
  ungroup() %>% group_by(property) %>%
  mutate(prob = count/sum(count),
         roundval = to.n(roundval))

ggplot(d.anim.bin, aes(x=roundval, y=prob))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~property)+
  xlab("prevalence")+
  ylab("proportion of responses\n")+
  #scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_discrete(breaks=c(0,20,40,60,80,100))+#,limits=c(-5,105))+
 # theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
#  theme(legend.key.size=unit(2, "lines"),
#        legend.text.align=NULL)+
  guides(fill=F)

d.anim.bin %>% select(-prob) %>% spread(roundval, count)



```



## Distribution by response

Here, I don't include the intermediate step of summarising by animal kind. Instead, I just plot the density directly from subjects' responses. Again, green line indicates prevalence for target categogry.

```{r}

d.interest<-d.tidy %>% filter(interest)

selection <-c("are female", "have wings", "have manes", "carry malaria")

ggplot(data = filter(d,property%in%selection), aes(x=prevalence))+
  #geom_histogram()+
  geom_density(adjust=0.5, fill='grey')+
  facet_wrap(~property,scales='free')+
  xlim(0,100)

+
 # geom_vline(data=d.interest, aes(xintercept=prev), colour='#2ca25f',size=1.3)
```


Binned distributions (for model)

```{r}
d <- d %>% mutate(roundval=factor(round(prevalence/10)*10))

d.bin<- d %>%
  group_by(property, roundval) %>%
  summarise(count = length(roundval)) %>%
  ungroup() %>% group_by(property) %>%
  mutate(prob = count/sum(count),
         roundval = to.n(roundval))


# Filter out given animals.


#filter(animal.parsed %in% generics.of.interest$animal)

ggplot(d.bin, aes(x=roundval, y=prob))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~property)+
  xlab("prevalence")+
  ylab("proportion of responses\n")+
  #scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_discrete(breaks=c(0,20,40,60,80,100))+#,limits=c(-5,105))+
 # theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
#  theme(legend.key.size=unit(2, "lines"),
#        legend.text.align=NULL)+
  guides(fill=F)

filter(d, property=='attack swimmers' & prevalence>90)$animal.parsed
```

Looks like "Mosquitos attack swimmers." is probably true.


```{r}
# d.out<-d.bin %>% select(-prob) %>% spread(roundval, count)
# d.out[is.na(d.out)] <- 1 # remove NAs (which are 0s); set to 1 so there is some probability mass...
# write.csv(d.out,file='../cbg2010-replication/models/prevalencePrior_16props.csv')
```

# Truth judgment: Experiment 1

Process for webppl
```{r}
# tj<-read.csv(file = '../experiments/turk/real-kinds-truth-1/real-kinds-truth-1-trials.csv')
# tj$response<-factor(tj$response,levels=c("disagree-key","agree-key"),
#        labels=c("mu","generic is true"))
# tj$sentence <- gsub('&quotechar','', tj$sentence)
# tj$sentence <- gsub('lyme','Lyme', tj$sentence)
# 
# tj.d<-tj%>% select(sentence, response, workerid) %>%
#   spread(workerid, response)
# 
# write.csv(tj.d,'real-kinds-truth-1-trials-n100-webpplfriendly.csv')
```

```{r tj1}

setwd(dir = '~/Documents/research/generics/analysis/')
tj<-read.csv(file = '../experiments/turk/real-kinds-truth-1/real-kinds-truth-1-trials.csv')
c <- read.csv(file = '../experiments/turk/real-kinds-truth-1/real-kinds-truth-1-catch_trials.csv')

### bootstrap CI
bootstrap.ci <- function(x){
  agr = aggregate(response ~ sentence, data=x, FUN=mean)
  agr$CILow = aggregate(response ~ sentence, data=x, FUN=ci.low)$response
  agr$CIHigh = aggregate(response ~ sentence, data=x, FUN=ci.high)$response
  agr$YMin = agr$response - agr$CILow
  agr$YMax = agr$response + agr$CIHigh
  return(agr)
}


tj.bs<-bootstrap.ci(tj %>% mutate(response = as.numeric(response=='agree-key')))

tj.bs$sentence <- gsub('&quotechar','', tj.bs$sentence)
tj.bs$sentence <- gsub('lyme','Lyme', tj.bs$sentence)

tj.bs$sentence<-with(tj.bs, reorder(sentence, response, function(x) x))


ggplot(data=tj.bs, aes(x=sentence, y=response-0.5))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8,
           fill='grey89')+
  geom_errorbar(aes(ymin=YMin-0.5,ymax=YMax-0.5), width=0.5, size = 1.5,
                color='white')+
  theme_blackDisplay()+
  #theme(axis.text.x = element_text(angle = 45, hjust = 1,
   #                                vjust=1))+
 # ylim(-.5,0.5)+
  xlab("")+
  ylab("\n proportion of subjects who agree")+
  scale_y_continuous(breaks=c(-0.5,0,0.5),labels=c("0","0.5","1"))+
  coord_flip()

ggsave(file='~/Box Sync/talks/esslli-2015-generics/truhtjudge_n100.pdf',
       width=24,height=20)

tj.tidy <- tj %>%
  group_by(sentence) %>%
  summarise(prop = sum(as.numeric(response=='agree-key'))/length(response),
            n = length(response)) %>%
  mutate(sterr = sqrt(prop*(1-prop)/n),
         endorse = prop-0.5)


tj.tidy$sentence <- gsub('&quotechar','', tj.tidy$sentence)
tj.tidy$sentence <- gsub('lyme','Lyme', tj.tidy$sentence)

tj.tidy$sentence<-with(tj.tidy, reorder(sentence, prop, function(x) -x))


ggplot(data=tj.tidy, aes(x=sentence, y=endorse))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=endorse-2*sterr,ymax=endorse+2*sterr), width=0.5)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(-.5,0.5)

```

Boring renaming of properties, and getting prior estimations for negations by subtracting positive form from 100

Scatterplot of raw prevalence vs. proportion of "agree" responses

```{r}

d.tidy.sub[d.tidy.sub$property == 'attacks swimmers',]$property <- 'attack swimmers'
d.tidy.sub$sentence <- with(d.tidy.sub, paste(paste(animal.parsed,'s',sep=''), paste(property,'.',sep='')))

m.tidy<-left_join(tj.bs,d.tidy.sub, by="sentence")

m.tidy[m.tidy$sentence=='Mosquitos dont carry malaria.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Mosquitos carry malaria.',]$prev

m.tidy[m.tidy$sentence=='Sharks dont attack swimmers.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Sharks attack swimmers.',]$prev

m.tidy[m.tidy$sentence=='Peacocks dont have beautiful feathers.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Peacocks have beautiful feathers.',]$prev

m.tidy[m.tidy$sentence=='Ticks dont carry Lyme disease.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Ticks carry Lyme disease.',]$prev

m.tidy[m.tidy$sentence=='Tigers dont eat people.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Tigers eat people.',]$prev

m.tidy<-m.tidy %>%
  filter(!is.na(prev))

ggplot(m.tidy,aes(x=prev,y=response))+
  geom_point()

with(m.tidy, cor(prev,response))

quantile(m.tidy$prev)

with(filter(m.tidy,(prev > quantile(m.tidy$prev)["25%"] & 
                      prev < quantile(m.tidy$prev)["75%"])), cor(prev,response))


```



## lvRSA model predictions

Doing TFBT with speaker optimality (at the S1 level) as a free parameter

```{r}
model.posteriorpred <-read.csv('../cbg2010-replication/models/model_predictions/generics_truthJudge_3_postpred_n100_mh1000.csv',header=F,
                               col.names=c("sentence","posteriorPred"))



combined.model.data<- left_join(model.posteriorpred, m.tidy, by='sentence')

with(combined.model.data, cor(posteriorPred, response))
with(filter(combined.model.data,
            (prev>25 & prev < 75)), cor(posteriorPred, response))

with(filter(combined.model.data,
            (prev > quantile(m.tidy$prev)["25%"] & 
            prev < quantile(m.tidy$prev)["75%"])), cor(posteriorPred,response))




with(combined.model.data, cor(posteriorPred, response, method='spearman'))


with(combined.model.data, cor(prev, response))
with(combined.model.data, cor(prev, response, method='spearman'))


combined.model.data$sentence<-with(combined.model.data, reorder(sentence, response, function(x) -x))



qplot(data=combined.model.data,
      x=posteriorPred,y=response,
      color=sentence)+
  geom_point(size=4)+
  geom_errorbar(aes(ymin=YMin, ymax=YMax),
                position=position_dodge(), size =2)+
  geom_abline(intercept=0,slope=1,linetype=2, size=2,color='white')+
  xlab("\n model posterior predictive")+
  ylab("proportion of agree's \n")+
  guides(color=F)+
  coord_fixed()+
  theme_blackDisplay()
  
ggsave(file='~/Box Sync/talks/esslli-2015-generics/scatter-lvrsa.pdf',
       width=13,height=13)

qplot(data=combined.model.data,
      x=prev,y=response,
      color=sentence)+
  geom_point(size=4)+
    geom_errorbar(aes(ymin=YMin, ymax=YMax),
                position=position_dodge(), size =2)+
  geom_abline(intercept=0,slope=0.01,linetype=2, size =2,color='white')+
  xlab("\n (raw) prevalence")+
  ylab("proportion of agree's \n")+
  guides(color=F)+
  coord_fixed(ratio=100)+
  theme_blackDisplay()

ggsave(file='~/Box Sync/talks/esslli-2015-generics/scatter-prevalence.pdf',
       width=13,height=13)

```



