---
title: "generics-esslli"
author: "mht"
date: "July 14, 2015"
output: html_document
---

Figures I'm using in my talk at ESSLLI. Probably also they will be used in my manuscript.


# Prior 2: Prevalence priors for 16 properties


```{r echo=F}
upperFirst <- function(name){
  return (paste(toupper(substr(name, 1, 1)), substr(name, 2, nchar(name)), sep=""))
}

removeS <- function(name.in){
  exceptions = c("Turtles", "Bees", "Horses", "Giraffes","Whales","Beetles","Eagles","Snakes","Moles")
  bluejays =  c("Blue jay","Blue Jay","Bluejay")
  fleas = c("Flea", "Fly")
  name<-removeSpace(name.in)
  last<-substr(name,nchar(name),nchar(name))
  last2<-substr(name,nchar(name)-1,nchar(name))
  if (name%in%exceptions){
    name.singular <- substr(name,1,nchar(name)-1)
  } else if (name%in%bluejays){
    name.singular <- "Bluejay"
  } else if (name%in%fleas){
    name.singular <- "Flea"
  } else if (name=="Wolves") {
    name.singular <- "Wolf"
  } else if (name=='Dolpin') {
    name.singular <- "Dolphin"
  } else if (name=='Giraffs') {
    name.singular <- "Giraffe"
  }  else if (last2=='es') {
    name.singular <- substr(name,1,nchar(name)-2)
  } else if (last=='s') {
    name.singular <- substr(name,1,nchar(name)-1)
  } else {
    name.singular <- name
  }
  
return(name.singular)
}

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

removeSpace <- function(name){
  if (substrRight(name,1)==' ') {
    name.edit <- substr(name,1, nchar(name)-1)
  } else {
    name.edit <- name
  }
  return(name.edit)
}

setwd(dir = '~/Documents/research/generics/analysis/')
generics.of.interest <- data.frame(
  animal=c("Robin","Leopard","Duck","Lion","Mosquito","Shark","Cardinal","Kangaroo","Peacock","Tiger","Tick","Swan"),
  property=c("lay eggs", "have spots","have wings","have manes","carry malaria",
              "attacks swimmers","are red","have pouches","have beautiful feathers","eat people","carry Lyme disease","are white"))

d<-read.csv(file = '../experiments/turk/real-kinds-prior-2/real-kinds-2-trials.csv')
d0<-read.csv(file='../experiments/turk/real-kinds-prior-2/real-kinds-2pilot5/real-kinds-2-trials.csv')

d0$workerid = max(d$workerid) + d0$workerid+1
d<-bind_rows(d,d0)

d[d$property=='are juveline',]$property<-'are juvenile'

d$animal.parsed<- factor(unlist(Map(removeS, upperFirst(as.character(d$animal)))))


# retrieve novel animals (and count only one instance per subject)
animals.produced<-filter(d,
                         (!(animal.parsed %in% generics.of.interest$animal)&
                            (property_index==0)|(property_index==8)))


```

### Prevalence distributions


#### Estimates for each animal.

Some of these animals have very few responses, owing to the fact that they were produced by just one or a few subjects. Ordering is alphabetical by animal name. Light blue bars indicate the category of interest for each property (for the generic).

```{r exp2.estimatesByAnimal, fig.height=15, fig.width=36}

d.tidy<- d %>%
  group_by(property,animal.parsed) %>%
  summarise(prev = mean(prevalence),
            sterr=sem(prevalence)) %>%
  filter(!(is.na(sterr)))

generics.of.interest$combined <- paste(generics.of.interest$property, 
                                       generics.of.interest$animal)
d.tidy$combined <- paste(d.tidy$property, d.tidy$animal.parsed)

d.tidy$interest<-d.tidy$combined %in% generics.of.interest$combined


d.tidy.sub <- d.tidy %>% 
  filter(animal.parsed %in% generics.of.interest$animal)

```


## Distribution by animal

Here, I plot the distribution of prevalence after summarizing an average prevalence for each animal. Hence, a sample from this distribution is an animal category (with an associated prevalence of the property). Again note:: many of these categories have very few responses.

Green line indicates prevalence for target category.
```{r}
ggplot(data=d.tidy, aes(x=prev))+
  geom_vline(data=filter(d.tidy,interest), aes(xintercept=prev),
             colour='#2ca25f',size=1.3)+
 # geom_histogram(binwidth=5)+
  geom_density()+
  facet_wrap(~property, scales='free')+
  xlim(0,100)
```

Binned distributions (for model)

```{r}
d.tidy<- d.tidy %>% mutate(roundval=round(prev/10)*10) 

d.anim.bin<- d.tidy %>%
  group_by(property, roundval) %>%
  summarise(count = length(roundval)) %>%
  ungroup() %>% group_by(property) %>%
  mutate(prob = count/sum(count),
         roundval = to.n(roundval))

ggplot(d.anim.bin, aes(x=roundval, y=prob))+
  geom_bar(stat='identity', position=position_dodge())+
  facet_wrap(~property)+
  xlab("prevalence")+
  ylab("proportion of responses\n")+
  #scale_fill_brewer(palette='Pastel1',type='qual')+
 # scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),limits=c(0,1))+
  scale_x_discrete(breaks=c(0,20,40,60,80,100))+#,limits=c(-5,105))+
 # theme_blackDisplay()+ 
  guides(fill=guide_legend(title="property"))+
#  theme(legend.key.size=unit(2, "lines"),
#        legend.text.align=NULL)+
  guides(fill=F)

d.anim.bin %>% select(-prob) %>% spread(roundval, count)



```



## Distribution by response

Here, I don't include the intermediate step of summarising by animal kind. Instead, I just plot the density directly from subjects' responses. Again, green line indicates prevalence for target categogry.

```{r}

d.interest<-d.tidy %>% filter(interest)

selection <-c("are female", "have wings", "have manes", "carry malaria")

ggplot(data = filter(d,property%in%selection), aes(x=prevalence,fill=property))+
  #geom_histogram()+
  geom_density(adjust=0.5, color='white')+
  facet_wrap(~property,scales='free')+
  xlim(0,100)+
  scale_fill_brewer(type='qual',palette='Pastel1')+
  theme_blackDisplay()+
  xlab("\n prevalence")+
  guides(fill=F)

ggsave(file='~/Box Sync/talks/esslli-2015-generics/naturalkinds-4priors.pdf')

,
       width=14,height=10)
 # geom_vline(data=d.interest, aes(xintercept=prev), colour='#2ca25f',size=1.3)
```


# Truth judgment: Experiment 1



```{r tj1}

setwd(dir = '~/Documents/research/generics/analysis/')
tj<-read.csv(file = '../experiments/turk/real-kinds-truth-1/real-kinds-truth-1-trials.csv')
c <- read.csv(file = '../experiments/turk/real-kinds-truth-1/real-kinds-truth-1-catch_trials.csv')

### bootstrap CI
bootstrap.ci <- function(x){
  agr = aggregate(response ~ sentence, data=x, FUN=mean)
  agr$CILow = aggregate(response ~ sentence, data=x, FUN=ci.low)$response
  agr$CIHigh = aggregate(response ~ sentence, data=x, FUN=ci.high)$response
  agr$YMin = agr$response - agr$CILow
  agr$YMax = agr$response + agr$CIHigh
  return(agr)
}


tj.bs<-bootstrap.ci(tj %>% mutate(response = as.numeric(response=='agree-key')))

tj.bs$sentence <- gsub('&quotechar','', tj.bs$sentence)
tj.bs$sentence <- gsub('lyme','Lyme', tj.bs$sentence)

tj.bs$sentence<-with(tj.bs, reorder(sentence, response, function(x) x))


ggplot(data=tj.bs, aes(x=sentence, y=response-0.5))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8,
           fill='grey89')+
  geom_errorbar(aes(ymin=YMin-0.5,ymax=YMax-0.5), width=0.5, size = 1.5,
                color='white')+
  theme_blackDisplay()+
  #theme(axis.text.x = element_text(angle = 45, hjust = 1,
   #                                vjust=1))+
 # ylim(-.5,0.5)+
  xlab("")+
  ylab("\n proportion of subjects who agree")+
  scale_y_continuous(breaks=c(-0.5,0,0.5),labels=c("0","0.5","1"))+
  coord_flip()

ggsave(file='~/Box Sync/talks/esslli-2015-generics/truhtjudge_n100.pdf',
       width=24,height=20)

tj.tidy <- tj %>%
  group_by(sentence) %>%
  summarise(prop = sum(as.numeric(response=='agree-key'))/length(response),
            n = length(response)) %>%
  mutate(sterr = sqrt(prop*(1-prop)/n),
         endorse = prop-0.5)


tj.tidy$sentence <- gsub('&quotechar','', tj.tidy$sentence)
tj.tidy$sentence <- gsub('lyme','Lyme', tj.tidy$sentence)

tj.tidy$sentence<-with(tj.tidy, reorder(sentence, prop, function(x) -x))


ggplot(data=tj.tidy, aes(x=sentence, y=endorse))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=endorse-2*sterr,ymax=endorse+2*sterr), width=0.5)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(-.5,0.5)

```

Boring renaming of properties, and getting prior estimations for negations by subtracting positive form from 100

Scatterplot of raw prevalence vs. proportion of "agree" responses

```{r}

d.tidy.sub[d.tidy.sub$property == 'attacks swimmers',]$property <- 'attack swimmers'
d.tidy.sub$sentence <- with(d.tidy.sub, paste(paste(animal.parsed,'s',sep=''), paste(property,'.',sep='')))

m.tidy<-left_join(tj.bs,d.tidy.sub, by="sentence")

m.tidy[m.tidy$sentence=='Mosquitos dont carry malaria.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Mosquitos carry malaria.',]$prev

m.tidy[m.tidy$sentence=='Sharks dont attack swimmers.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Sharks attack swimmers.',]$prev

m.tidy[m.tidy$sentence=='Peacocks dont have beautiful feathers.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Peacocks have beautiful feathers.',]$prev

m.tidy[m.tidy$sentence=='Ticks dont carry Lyme disease.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Ticks carry Lyme disease.',]$prev

m.tidy[m.tidy$sentence=='Tigers dont eat people.',]$prev<-100-
  m.tidy[m.tidy$sentence=='Tigers eat people.',]$prev

m.tidy<-m.tidy %>%
  filter(!is.na(prev))

ggplot(m.tidy,aes(x=prev,y=response))+
  geom_point()

with(m.tidy, cor(prev,response))

quantile(m.tidy$prev)

with(filter(m.tidy,(prev > quantile(m.tidy$prev)["25%"] & 
                      prev < quantile(m.tidy$prev)["75%"])), cor(prev,response))


```



## lvRSA model predictions

Doing TFBT with speaker optimality (at the S1 level) as a free parameter

```{r}
model.posteriorpred <-read.csv('../cbg2010-replication/models/model_predictions/generics_truthJudge_3_postpred_n100_mh1000.csv',header=F,
                               col.names=c("sentence","posteriorPred"))



combined.model.data<- left_join(model.posteriorpred, m.tidy, by='sentence')

with(combined.model.data, cor(posteriorPred, response))
with(filter(combined.model.data,
            (prev>25 & prev < 75)), cor(posteriorPred, response))

with(filter(combined.model.data,
            (prev > quantile(m.tidy$prev)["25%"] & 
            prev < quantile(m.tidy$prev)["75%"])), cor(posteriorPred,response))




  with(combined.model.data, cor(posteriorPred, response, method='spearman'))


with(combined.model.data, cor(prev, response))
with(combined.model.data, cor(prev, response, method='spearman'))


combined.model.data$sentence<-with(combined.model.data, reorder(sentence, response, function(x) -x))



qplot(data=combined.model.data,
      x=posteriorPred,y=response,
      color=sentence)+
  geom_point(size=4)+
  geom_errorbar(aes(ymin=YMin, ymax=YMax),
                position=position_dodge(), size =2)+
  geom_abline(intercept=0,slope=1,linetype=2, size=2,color='white')+
  xlab("\n model posterior predictive")+
  ylab("proportion of agree's \n")+
  guides(color=F)+
  coord_fixed()+
  theme_blackDisplay()
  
ggsave(file='~/Box Sync/talks/esslli-2015-generics/scatter-lvrsa.pdf',
       width=13,height=13)

qplot(data=combined.model.data,
      x=prev,y=response,
      color=sentence)+
  geom_point(size=4)+
    geom_errorbar(aes(ymin=YMin, ymax=YMax),
                position=position_dodge(), size =2)+
  geom_abline(intercept=0,slope=0.01,linetype=2, size =2,color='white')+
  xlab("\n (raw) prevalence")+
  ylab("proportion of agree's \n")+
  guides(color=F)+
  coord_fixed(ratio=100)+
  theme_blackDisplay()

ggsave(file='~/Box Sync/talks/esslli-2015-generics/scatter-prevalence.pdf',
       width=13,height=13)

```

