---
title: "generics-predictive"
author: "mht"
date: "May 23, 2016"
output: html_document
---


# Truth judgments (dobles / predictive task)

```{r truth.load}
project.path<- "~/Documents/research/generics/"
d <- read.csv(paste(project.path, 
                    "/data/predictive/predictive-1-trials.csv", sep=""))
```

Reaction time distributions

```{r}
d %>%
  ggplot(., aes(x=rt))+
  geom_histogram()+
  xlim(0,100)

d %>%
  ggplot(., aes(x=rt, fill=origins))+
  geom_histogram(position=position_dodge())

d %>%
  ggplot(., aes(x=rt, fill=event_outcome))+
  geom_histogram(position=position_dodge())

d %>%
  ggplot(., aes(x=rt))+
  geom_histogram()+
  facet_grid(origins~event_outcome)
```

Generic endorsement by origins and event outcomes

```{r}
d.stat<- d %>%
  group_by(origins,event_outcome) %>%
  multi_boot_standard(column="response")


ggplot(d.stat, aes(x=origins, y = mean, 
                   ymin=ci_lower, ymax=ci_upper, group=event_outcome,
                   fill=event_outcome))+
  geom_bar(stat='identity', 
           width = 0.8, position=position_dodge(0.8), 
           color='black')+
  geom_errorbar(position=position_dodge(0.8), width = 0.5)+
  theme_paper()+
  ylab("Generic endorsement")


```

Broken down by property type (color vs. part)

```{r}
d.stat2<- d %>%
  group_by(origins,event_outcome, stim_proptype) %>%
  multi_boot_standard(column="response")

d %>%
  group_by(stim_proptype,origins,event_outcome) %>%
  summarize(length(origins))

ggplot(d.stat2, aes(x=origins, y = mean, 
                   ymin=ci_lower, ymax=ci_upper, group=event_outcome,
                   fill=event_outcome))+
  geom_bar(stat='identity', 
           width = 0.8, position=position_dodge(0.8), 
           color='black')+
  geom_errorbar(position=position_dodge(0.8), width = 0.5)+
  theme_paper()+
  ylab("Generic endorsement")+
  facet_wrap(~stim_proptype)
```

Statistical models

```{r}

rs<-glmer(response ~ event_outcome * origins + (1 | workerid), 
          d, family='binomial')

rs<-glmer(response ~ event_outcome * origins * stim_proptype+ (1 | workerid), 
          d, family='binomial')


```

# Predictive elicitation

```{r predictive.load}
d2<- read.csv(paste(project.path,
                    "/data/predictive/predictive-elicitation-1-trials.csv",
                    sep=""))
```

Reaction time distributions
```{r}
d2 %>%
  ggplot(., aes(x=rt))+
  geom_histogram()+
  xlim(0,100)


# should probably log-transform and censor based on SDs...
```

Response distributions

```{r}
d2 %>%
  ggplot(., aes(x=response))+
  geom_histogram()+
  facet_grid(origins~event_outcome)
```


Average predictive prevalence

```{r}
d2.stat <- d2 %>%
  group_by(origins, event_outcome) %>%
  multi_boot_standard(column='response')

ggplot(d2.stat, aes(x=origins, y = mean, 
                   ymin=ci_lower, ymax=ci_upper, group=event_outcome,
                   fill=event_outcome))+
  geom_bar(stat='identity', 
           width = 0.8, position=position_dodge(0.8), 
           color='black')+
  geom_errorbar(position=position_dodge(0.8), width = 0.5)+
  ylab("Predictive prevalence")
```


Broken down by property type (color vs. part), for extrinsic-maintained and intrinsic-lost

```{r}
d2 %>%
  filter( (origins=='intrinsic' & event_outcome == 'lost') |
            (origins=='extrinsic' & event_outcome == 'maintained')) %>%
  ggplot(., aes(x=response))+
  geom_histogram()+
  facet_grid(stim_proptype~origins)
```

Averages, by origins, outcome, and type

```{r}
d2.stat.item <- d2 %>%
  group_by(origins, event_outcome, stim_proptype) %>%
  multi_boot_standard(column='response')

ggplot(d2.stat.item, aes(x=origins, y = mean, 
                   ymin=ci_lower, ymax=ci_upper, group=event_outcome,
                   fill=event_outcome))+
  geom_bar(stat='identity', 
           width = 0.8, position=position_dodge(0.8), 
           color='black')+
  geom_errorbar(position=position_dodge(0.8), width = 0.5)+
  ylab("Predictive prevalence")+
  facet_wrap(~stim_proptype)


```